### 2012-06-18 Weaklensing.tex
add Weaklensing.tex

%% LyX 2.0.3 created this file.  For more info, see http://www.lyx.org/.
%% Do not edit unless you really know what you are doing.
\documentclass[english]{article}
\usepackage[utf8]{luainputenc}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{babel}
\begin{document}

\part*{Weak Lensing Observables}

In weak lensing we can define complex ellipticity as $\epsilon=\frac{a-b}{a+b}e^{2i\phi}$
.a and b is long and short axis. While $\phi$is the orientation angle.

In analogy to the complex ellipticities we can also define complex
shear $\gamma=|\gamma|e^{2i\Phi}$as well as reduced shear $g=\frac{\gamma}{1-k}$.

The relation between unlensed and lensed ellipticity $\epsilon_{s}$
and $\epsilon$ is $\epsilon_{s}=\frac{\epsilon_{s}+g}{1+g*\epsilon}$.
In weak lensing limit,k$\ll1$and $\gamma\ll1$.Therefore $\epsilon\thickapprox\epsilon_{s}+\gamma$.

\part*{Method to obtain Shear $\gamma$}

Assume that we know the distribution of ellipticity P( \textbar{}$\epsilon_{s}|$)
in absence of lensing.

What we need to do is to find out the $\gamma$that leads to the \{$\epsilon_{s}\}$fits
P(\textbar{}$\epsilon_{s}|$) best.

We can use the $\chi^{2}$value to denote the deviation of \{$\epsilon_{s}$\}
from P(\textbar{}$\epsilon_{s}$\textbar{}).

Here $\chi^{2}=\underset{i}{\sum}\frac{(O_{i}-E_{i})^{2}}{E_{i}}$
$O_{i}$is the frequency of \{$|\epsilon_{s}|$\},while $E_{i}$is
the expected frequency obtained from P(\textbar{}$\epsilon_{s}|$).

Now that $\gamma-\chi^{2}$is a 2D function on complex plane. We can
use numerical methods like Simulated Anealing Method to calculate
the minimum point of this function.The $\gamma$ that leads to the
minimum $\chi^{2}$is the shear $\gamma$we want.
\end{document}

### 2012-06-19 K-S_test.tex
add K-S_test.tex

%% LyX 2.0.3 created this file.  For more info, see http://www.lyx.org/.
%% Do not edit unless you really know what you are doing.
\documentclass[english]{article}
\usepackage[T1]{fontenc}
\usepackage[latin9]{inputenc}
\usepackage{esint}
\usepackage{babel}
\begin{document}

\part*{Kolmogorov-Smirnov Test}

To test whether a set of data \{X\} satisfy probability distribution
P(X) ,we can use the K-S Test.

In K-S test $P=max(|F_{n}(x)-F(x)|)$ . $F_{n}(X)=($Observed values
NO. which is smaller than X in sample \{X\} )/N .N is the NO. of the
sample\{X\}.

F(X)=$\intop_{-\infty}^{x}P(X)$

The smaller P is ,the more likely \{X\} satisfies P(X).

In Weak Lensing for each $\gamma$ there's a set of ellipticity \{|$\epsilon_{s}|$\}.
We can use K-S Test to calculate the P value between \{|$\epsilon_{s}|$\}
and expected distribution P(|$\epsilon_{s}$|).

Then we can get a 2D $\gamma-P$ function. Find the minimum point
of this function, we obtain the shear $\gamma$.
\end{document}

### 2012-06-19 Weaklensing.tex

@@
 Here $\chi^{2}=\underset{i}{\sum}\frac{(O_{i}-E_{i})^{2}}{E_{i}}$
-$O_{i}$is the frequency of \{$|\epsilon_{s}|$\},while $E_{i}$is
-the expected frequency obtained from P(\textbar{}$\epsilon_{s}|$).
+$O_{i}$is the frequency of \{$|\epsilon_{s}|$\} for bin i ,while $E_{i}$is
+the expected frequency for bin i which can be obtained from P(\textbar{}$\epsilon_{s}|$).
 

### 2012-06-20 Likeilyhood.tex
add Likeilyhood.tex

%% LyX 2.0.3 created this file.  For more info, see http://www.lyx.org/.
%% Do not edit unless you really know what you are doing.
\documentclass[english]{article}
\usepackage[T1]{fontenc}
\usepackage[latin9]{inputenc}
\usepackage{amsmath}

\makeatletter

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% LyX specific LaTeX commands.
\DeclareRobustCommand{\greektext}{%
  \fontencoding{LGR}\selectfont\def\encodingdefault{LGR}}
\DeclareRobustCommand{\textgreek}[1]{\leavevmode{\greektext #1}}
\DeclareFontEncoding{LGR}{}{}
\DeclareTextSymbol{\~}{LGR}{126}

\makeatother

\usepackage{babel}
\begin{document}

\part*{Likeilyhood Function:}

Definition of likeilyhood function :

Let X be a random variable with a continuous probability distribution
with density function f depending on a parameter \textgreek{j}. Then
the function $L(\theta|x)=f_{\theta}(x)$ as a function of $\theta$is
the likeilyhood function of $\theta$,given the outcome x of X.

In a world ,the likelihood function of a set of parameter values given
some observed outcomes is equal to the probability of those observed
outcomes given those parameter values.

In the weak lensing case. We need to get the likeilyhood function
of shear $\gamma$,given a set of observed lensed ellipticity \{$\epsilon$\},and
we also know the distribution function of $|\epsilon_{s}$|,ellipticity
in absence of lensing P($|\epsilon_{s}|)$ .

Thus,the likeilyhood function of $\gamma$ should be $L(\gamma|\{\epsilon\})$=$\underset{i}{\prod}P($$|\epsilon_{s-n}|$).
Where $\epsilon_{s-n}=\epsilon_{-n}-\gamma$.

Or we can use the Log likeilyhood function $Log(L(\gamma|\{\epsilon\}))=\underset{i}{\sum}Log(P(|\epsilon_{s}|))$.
\end{document}

### 2012-06-27 lensing6_26.tex
git add lensing6_26.tex

%% LyX 2.0.3 created this file.  For more info, see http://www.lyx.org/.
%% Do not edit unless you really know what you are doing.
\documentclass[english]{article}
\usepackage[T1]{fontenc}
\usepackage[utf8]{luainputenc}
\usepackage{amsmath}
\usepackage{graphicx}

\makeatletter

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% LyX specific LaTeX commands.
%% Because html converters don't know tabularnewline
\providecommand{\tabularnewline}{\\}

\makeatother

\usepackage{babel}
\begin{document}

\part*{1.Likelihood Function}

L($\gamma$|Data)=P(Data|$\gamma$)=$\underset{n}{\prod}$p($\epsilon_{s-n}$){*}p($\phi_{s-n}$){*}$\frac{d\epsilon_{s}d\phi_{s}}{d\epsilon d\phi}$
.Since the universe is isotropic ,p($\phi_{s}$)=1,and p($\epsilon_{s}$)
is known. In the code I set the distribution of true ellipticity p($\epsilon_{s}$)
to be $\epsilon_{s}(1-\epsilon_{s})$ . It satisfies p(0)=p(1)=0.

\part*{2.Toy data production}

I use the function rand() in C language to produce random datas that
satisfy p($\epsilon_{s}$) and $p(\phi_{s})$. These data are used
as true ellipticity and orientation of galaxies in the code.

Then I use the formulor $\epsilon e^{2i\phi}=\epsilon_{s}e^{2i\phi_{s}}+\gamma.$
To shear the unlensed $\epsilon_{s}$,$\phi_{s}$ to lensed $\epsilon$and
$\phi$.

\part*{3.Likelihood function Calculation}

For any $\gamma$ on the complex plane we can recover unlensed $\epsilon_{s}$and
$\phi_{s}$,and calculate its likelihood.Since the likelihood is very
small when the number of data sample N is large,the code uses Log(likelihood).

the ($\gamma-\gamma_{true}$)-likelihood contour picture is showed
below with N=1000.

\includegraphics[scale=0.6]{gamma}

\part*{4.Result of $\gamma$ calculation}

To recover the true $\gamma$ we need to obtain the $\gamma$leads
to the largest likelihood.Since $\Delta\gamma=|\gamma-\gamma_{true}|$does
not depend on specific value of $\gamma_{true}$

only the value of $\Delta\gamma$ is recorded in the code.

The table below lists the mean value of |$\gamma-\gamma_{true}|$
for different Sample number N. The average is made over 6 tests.

\begin{tabular}{|c|c|c|c|}
\hline 
N & 200 & 1000 & 2000\tabularnewline
\hline 
\hline 
$\overline{|\Delta\gamma|}$ & 0.14 & 0.04 & 0.03\tabularnewline
\hline 
\end{tabular}
\end{document}

### 2013-02-13 write-up.tex
add write-up.tex

%% LyX 2.0.2 created this file.  For more info, see http://www.lyx.org/.
%% Do not edit unless you really know what you are doing.
\documentclass[english]{article}
\usepackage[T1]{fontenc}
\usepackage[latin9]{inputenc}
\usepackage{amssymb}
\usepackage{graphicx}

\makeatletter

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% LyX specific LaTeX commands.
%% Because html converters don't know tabularnewline
\providecommand{\tabularnewline}{\\}

\makeatother

\usepackage{babel}
\begin{document}

\title{Weak lensing Hierarchy Bayesian Inference }

\date{03/09/2013}
\maketitle
\begin{abstract}
We present a Hierarchy Bayesian method for shear inference in Weak
Lensing survey. With this method we are able to infer synchronously
cosmic shear at different sky patches as well as the intrinsic shape
distribution. We show that this Hierarchy Bayesian method is more
accurate than the traditional average method and (prove to a large
extent )it is an unbiased estimation of shear.

Key words:gravational lensing-methods;data analysis-methods;bayesian
inference
\end{abstract}

\section{Introduction}

$\ \ \ \ $Weak Lensing has become one of the most powerful method
in exploring the dark universe (Al- brecht et al. 2006; Peacock \&
Schneider 2006 )

As dark energy slows the growth of dark matter structures, these in
turn affect the appearance of distant galaxies, distorting them slightly
as gravitational fields deflect their light. This distortion is known
as cosmic shear.()

The measurement of cosmic shear is determined by the amount of distortion
caused to a forewground galaxy. Due to the isotropic universe the
expect value of a galaxy's intrinsic complex ellipticity is 0. Therefore
the comples ellipticity of a stretched galaxies is an unbiased estimation
of cosmic shear.However, the distortion induced by cosmic shear is
typically on the order of a few percent,which is significantly smaller
than the galaxies's intrinsic shape noise(\textasciitilde{}0.1 level).

Several beysian or likelihood approaches towards shear measurement
like lensfit(L. Miller,T. D. Kitching et al,2007;T.D. Kitching, L.
Miller et al 2008 ) im2shape(Bridle,) im3shape(Joe Zuntz, et al,arxive2013)
have bean make recently.{[}im3shape fitted different models on galaxies
image and used a max-likelihood method to determin the model parameters,and
then obtain the galaxy's ellipticity.{]}{[}lensfit proposed a modelfitting
approach in the galaxy shape measurement and evaluated how shear sensitivity
should be calculated based on posterior distribution of galaxies shape.{]}
However these methods mostly focus on the shape measurement of a single
galaxy.Given an telescope that has perfect measurement on galaxies'
shape their shear estimation method is no different thatn traditional
averaging method.

While in this paper what we want to focus is how to use a beysian
approach to infere cosmic shear independent from which way the galaxy
shape is measured with better accuracy than traditional averaging
method.Therefore in the toy model we used,we assume we have perfect
measurement on the galaxy shape.

One of the major problems for a bayesian inference of shear is that
even though a lot of measurement have bean made ,we still know little
about the intrinsic ellipticity distribution of galaxies of the whole
universe(Leauthaud\&Massey 2007;Joachimi\&Semboloni2012).However in
our Hierarchy Bayesian method we avoid to making any assumption on
intrinsic ellipticity distribution.We will show that using a free
model for intrinsic ellipticity distribution and infere its parameters
together with cosmic shear we will still out perform the traditional
averaging method.

The graphic model describe the hierarchy bayesian method in detail.
We assume in one sky patch there is a uniform

shear that applies on all the galaxies in that patch,and galaxies
in all patches have the same intrinsic ellipticity distribution.In
this way even if the number of galaxies in one patch is small,if we
have enough sky patches we can still get a good estimation of $\alpha$,which
is the key to have a good estimation of shear $g$ in each patch which
is the quantity we cares about.

\includegraphics[scale=0.5]{yike}

This report is orgnized as following: First we introduced the lensing
formula used in weak lensing region and how we simulated the lensed
ellpticity of galaxies.Then we introduced the likelihood function
$P(\epsilon_{\ell}|g,\alpha)$ which is the probability of having
lensed ellipticity $\epsilon_{\ell}$ given reduced shear $g$ in
each patch and intrinsic ellipticity $\epsilon_{0}$distribution parameter
$\alpha$ .Finally we show some results of the posterior distribution
sampling for two different models we selected for intrinsic shape
distrition function.Finally we estimate the level of possible systematic
bias of this HB inference.

\section{Method}

\subsection{Data Generation}

$\ \ \ \ $The definition of complex ellipticity of a galaxy is
\begin{equation}
\epsilon=\frac{1-q}{1+q}e^{2i\phi}
\end{equation}
 Here $q=\frac{b}{a}$ is the ratio of short and long axis. $\phi$
is the orientation angle of the galaxy.

First the unlensed complex ellipticity $\epsilon$ is generated according
to probability distribution:$P(|\epsilon|)=Beta(|\epsilon|,2.8,2.8)$
and $P(\phi)=\frac{1}{\pi}$. $\epsilon=|\epsilon|e^{2\phi i}$.

\includegraphics[scale=0.5]{sourceepsilon}

The simulated data is divided evenly into N patches.Galaxies in the
same patch are supposed to be sheared by the same shear map.The formula
of weaklensing is like:

\begin{equation}
\epsilon_{\ell}=\frac{\epsilon_{0}+g}{1+g^{*}\epsilon_{0}}
\end{equation}

$\epsilon_{\ell}$is the lensed ellipticity and $\epsilon_{0}$is
unlensed ellipticity.g is the reduced shear $g=\frac{\gamma}{1-k}$.k
denotes convergence and $\gamma$ denotes shear.In weak lensing region
$g\approx\mbox{\ensuremath{\gamma}}$
\begin{verse}
The inverse function is:
\begin{equation}
\epsilon_{0}=\frac{\epsilon_{\ell}-g}{1-g^{*}\epsilon_{\ell}}
\end{equation}

\end{verse}
Then we make N random samples from a selected distribution as the "true" reduced shear on each patch.

Finally we calculated the sheared shape of every galaxy on each patch.

Thus the simulated data we ar going to use is the lensed ellipticity
of $M\times N$ galaxies. N is the number of patches and M is the
number of galaxies in each patch.

Figure 2 shows the lensed ellipticity with M=8,N=64.The cross of blue
lines shows the true gamma used to shear the simulated.

\includegraphics[scale=0.3]{data}

\subsection{Likelihood Function}

If we know the ellipticity distribution of unlensed galaxies based
on some parasmeters $\alpha$,the likelihood of reduced shear $g$
and parameter $\alpha$ is like:

\begin{equation}
L(g,\alpha|\epsilon_{\ell})=P(\epsilon_{\ell}|g,\alpha)=P(\epsilon_{0}(g)|\alpha)*|\frac{\partial(|\epsilon_{0}|,\phi_{0})}{\partial(|\epsilon_{\ell}|,\phi_{\ell})}|
\end{equation}

$\epsilon_{0,}\epsilon_{\ell,}$ means the unlensed and lensed elliticity.
$\alpha$ the parameter of the distribution of unlensed ellipticity.

Due to the homogeneous universe,we can believe that all the galaxies
in different sky patches have the same intrinsic shape distribution.Therefore,in
order to get higher accuracy,what we do is to infere reduced shears
of a number of sky patches simultaneously with their common shape
parameter $\alpha$.
\begin{equation}
L(\vec{g},p,q|\epsilon_{\ell})=\prod_{i}\prod_{j}P(\epsilon_{0-j}(g_{i})|\alpha)|\frac{\partial(x_{0-j},y_{0-j})}{\partial(x_{\ell-j},y_{\ell-j})}|)
\end{equation}

i denotes ith patch and j denotes jth galaxies in a patch.

In this toy model,we choose two models for the distribution of unlensed
ellipticity :One is Beta distribution model.In this model we assume
the intrinsic ellipticity distribution is a beta distribution with
unknown parameter p and q.,The other one is step function model.Here
we devide 2D plane into a number of bins,and probability on each bin
is a free parameter.In later section we will show that we can get
similar results from these two models.

$|\frac{\partial(|\epsilon_{0}|,\phi_{0})}{\partial(|\epsilon|,\phi)}|$
is the Jacobi Determinant term.
\begin{equation}
|\frac{\partial(|\epsilon_{0}|,\phi_{0})}{\partial(|\epsilon_{\ell}|,\phi_{\ell})}|=|\frac{\partial(|\epsilon_{0}|,\phi_{0})}{\partial(x_{0},y_{0})}*\frac{\partial(x_{0},y_{0})}{\partial(x_{\ell},y_{\ell})}*\frac{\partial(x_{\ell},y_{\ell})}{\partial(|\epsilon_{\ell}|,\phi_{\ell})}|=\frac{|\epsilon_{\ell}|}{|\epsilon_{0}|}*|\frac{\partial(x_{0},y_{0})}{\partial(x_{\ell},y_{\ell})}|
\end{equation}

$(x_{0},y_{0})$ and $(x_{\ell},y_{\ell})$ are the Cartesian coordinates
of $\epsilon_{0}$ and $\epsilon_{\ell}$ on the complex plane.

When $|\epsilon_{0}|\longmapsto0$ ,$\epsilon\approx\epsilon_{0}+g$.Therefore,$|\frac{\partial(x_{0},y_{0)}}{\partial(x,y)}|\mapsto1$.Thus
when $|\epsilon_{0}|\mapsto0$ the Jacobi term $|\frac{\partial(|\epsilon_{0}|,\phi_{0})}{\partial(|\epsilon|,\phi)}|\mapsto\infty$.

In this paper 
\begin{equation}
P(\epsilon_{0}|\alpha)=|\epsilon_{0}|^{p-1}(1-|\epsilon_{0}|)^{q-1}/Beta(p,q)
\end{equation}

Thus

\begin{equation}
L(g,\alpha|\epsilon_{\ell})\propto|\epsilon_{0}|^{p-2}(1-|\epsilon_{0}|)^{q-1}|\frac{\partial(x_{0},y_{0})}{\partial(x_{\ell},y_{\ell})}|/Beta(p,q)
\end{equation}

We can see that when p<2 $L(g,\alpha|\epsilon_{\ell})$ will have
singular points at $g=\epsilon_{\ell}$.In this paper to avoid this
issue we restrict p always larger than 2.

The Jacobi term $|\frac{\partial(x_{0},y_{0})}{\partial(x_{\ell},y_{\ell})}|$
and Beta function $Beta(p,q)$ are calculated numerically.

\subsection{Gibbs Sampler}

While making the posterior samples we choose to use the classical
Gibbs sampler.

In Gibbs sampling ,samples of variable $x_{j}$ is made from the conditional
probability distribution:$p(x_{j}^{(i)}|x_{1}^{(i)},....,x_{j-1}^{(i)},x_{j+1}^{(i-1)}...)$

While the conditional distribution of one variable given all others
is just proportional to the joint distribution

\begin{equation}
p(x_{j}|x_{1},....,x_{j-1},x_{j+1}...,x_{n})\varpropto p(x_{1},.....,x_{n})
\end{equation}

While in paper the conditional distribution of reduced shear in one
patch only depends on the shape parameter $\alpha$ .Therefore sampling
reduced shear g from conditional distribution can be reduced to 2D
sampling problem,which can be done very quickly.

The total time needed to sample $g$ and $\alpha$ of 64 sky patches
with 8 galaxies in each patch will only be approximitly 25s on a 2
GHz CPU.

\subsection{Sample of Posterior Distribution }

\subsubsection{Beta function model}

in this section we assume the intrinsic shape distribution is a beta
function,and the two parameters p and q of Beta distribution are free
parameters to be sampled.The initial states comes from the result
of traditional average.The prior of $g$ is flat distribution on 2D
plane with constraint $|g|<1.$

Figure 2 shows the samples of g for 64 patches and 8 galaxies in each
patch.(Here for present reseaon we set the distribution of ``true''
g to be 2D Gaussian with sigma=0.1)

The red '+' sign denotes the mean value of lensed ellipticity.While
the blue '+' denotes the mean value of MCMC samples of gamma.The cross
the two blue lines is the possiition of true gamma.In some patches
the red '+' is not showed because it's out of the plane.

\includegraphics[scale=0.2]{uni/test}

Figure 3 shows the posterior samples of (p,q) ,the parameters of Beta
distribution.The two blues line show the possition of (p=2.8,q=2.8)
which is the true parameter used in Data generation part.

\includegraphics[scale=0.5]{uni/alpha_beta}

Since the value of |g| is usually supposed to be less than 0.1. While
comparing with traditional average method,in this paper the distribution
of ``true'' g is a uniform distribution within -0.1\textasciitilde{}0.1
for both g1 and g2.

To compare the accuracy with traditional averaging method we calculate
the value of $\sqrt{mean(\hat{g}}-g^{true})^{2}$

for HB method the typical value is \textasciitilde{}0.17 While for
traditional averaging method it's \textasciitilde{}0.18.

Though the value of mean square error depends on specific mock data
used,HB method consistantly out perform traditional averaging method
on a level of \textasciitilde{}0.01

\subsubsection{Step function model}

In this section we do not suppose the intrinsic distribution of ellipticity
to be Beta distribution any more.Instead we use a histogram to describe
the dtistribution of intrinsic ellipticity.We divide the 2-D space
r$\in$(0,1) into 10 bins .The probability of each bin is $p_{i}=e^{\alpha_{i}}$
.$\overrightarrow{\alpha}$ is a 10D parameter vector to be infered.

From practice we find that a prior smooth regularzation on $\alpha$
is needed to obtain a good estimation on shear g.

The prior distribution we used on $\alpha$ is :
\begin{equation}
Prior(\alpha)=exp(-\xi*\sum(\alpha_{i}-\alpha_{i-1})^{2})
\end{equation}

As in the Beta function model section,the data we used is 64{*}8 galaxies
seperated in 64 sky patches,and the prior of g is also the same.

$\xi$ is fixed at 2 .

Inital state is still the result of traditional average .

.Figure 8 shows the samples of g for 64 patches and 8 galaxies in
each patch and Figure 9 shows the infered $\vec{\alpha}$.The red
line in Figure 9 is Beta(2..8,2.8) the distribution used in data generation
part.

\includegraphics[scale=0.2]{step/test10}Figure 8

\includegraphics[scale=0.5]{step/stp10}

figure 9.The blue points are the infered $\alpha$ at the bin centers.Red
linr is true distribution Beta(2.8,2.8)

The accuracy we got from beta function model and step function model
are similar.They both out perform the traditional average method by
percentage level.

\section{Systematic Bias}

In this section,we measured the levels of possible systemmatic bias
led by this HB method.

Following Heymans et al. (2006), we quantify the systematic bias in
in terms of the multiplicative error m and additive error c on the
true shear $g^{true}$ 
\begin{equation}
\hat{g_{i}}-g_{i}^{true}=m_{i}g_{i}^{true}+c_{i}
\end{equation}

The accuracy in Weak Lensing measurement depends on both galaxies
shape measurement and shear inference period.In this paper our main
concern is how to infere shear in a HB method instead off traditional
averaging method and it does not involve the shape measurement part
.Therefore we assume we have perfect galaxies ellipticity measurement,and
all the possible inaccuracy is due to this HB shear inference method.

Using 10,000 data sets we are able to get the value of m and c for
both beta function and step function model.Each data set we use in
this section has 64 patches with 8 galaxies in eah patch.

The region for $g_{i}^{true}$ is -0.1\textasciitilde{}0.1 .

For beta function model :

\begin{tabular}{|c|c|c|}
\hline 
 & Expect Value & STD\tabularnewline
\hline 
\hline 
m1 & -0.00420 & 0.00304\tabularnewline
\hline 
c1 & 1.66$*10^{-4}$ & 1.73$*10^{-4}$\tabularnewline
\hline 
m2 & -0.00386 & 0.00290\tabularnewline
\hline 
c2 & 2.30$*10^{-4}$ & 1.81$*10^{-4}$\tabularnewline
\hline 
\end{tabular}

For step function model:

\begin{tabular}{|c|c|c|}
\hline 
 & Expect Value & STD\tabularnewline
\hline 
\hline 
m1 & 0.00502 & 0.00287\tabularnewline
\hline 
c1 & 2.05$*10^{-4}$ & 1.73$*10^{-4}$\tabularnewline
\hline 
m2 & 0.00156 & 0.00292\tabularnewline
\hline 
c2 & 2.14$*10^{-4}$ & 1.87{*}$10^{-4}$\tabularnewline
\hline 
\end{tabular}

\includegraphics[scale=0.5]{step_g1}

\includegraphics[scale=0.5]{g2_step}
\begin{quote}
Figure 9: Linear fit of $\delta g_{i}-g_{i}$ relationship for step
function model.
\end{quote}
As we can see from the data and graph no significant systematic bias
can be found using 10,000 data sets.With that amount of data we able
to narrow down m to $\sim10^{-3}$ and c to $\sim10^{-4}$.

In Table 1 we show the requirements on m, c for current, upcoming
and future cosmic shear surveys (Joe Zuntz ,axrive 2013)

\begin{tabular}{|c|c|c|}
\hline 
 & m & c\tabularnewline
\hline 
\hline 
current & 0.02 & 0.001\tabularnewline
\hline 
upcoming & 0.004 & 0.0006\tabularnewline
\hline 
future & 0.001 & 0.0003\tabularnewline
\hline 
\end{tabular}

Compared with our data,we can see that our method can at least support
upcoming cosmic shear surveys.Note that we only used 10,000 data sets
to quantify m,c due to limited computational time and the uncertainty
on $\hat{g}$ is large(\textasciitilde{}0.1),if much more data sets
were collected, these number will probabily be significantly lowered.

\section{Conclusion}

Here we present a Hierarchy Bayesian way in shear inference. Our method
successfully inferes the cosmic shears of different sky patches and
the intrinsic shape parameter synchronously.We showed that in the
area that galaxy density is low,our method can out perform traditional
averagemethod by \textasciitilde{}0.01 level. While in most cases
cosmic shear is just around this level. Also we quantify the level
of multiplicative and additive error,and shows this method has no
sign of a systematic bias down to (m\textasciitilde{}$10^{-3}$ c\textasciitilde{}$10^{-4}$
level ) and that this method can be aiming at support upcoming shear
surveys.

Eventhough the number of parameters used in this paper is up to 138
,using Gibbs sampler and starting from the result of simple average
we are able to make MCMC chain converged within 25s.

Further more ,by using the step function model, we showed that this
Hierarchy Bayesian method does not require correct knowledge on the
model of intrinsic shape dstribution.Simply using a step function
model and a prior regulazier we were able to get similar result as
when we assume we know the correct model of intrinsic shape distribution.

One intresting thing in shear survey is that the assumption that galaxy
pairs have no ellipticity correlation is not entirely accurate. There
are intrinsic alignments of nearby galaxies due to the alignment of
angular momentum produced by tidal shear correlations( Heymans C.,
Brown M., Heavens A., Meisenheimer K., Taylor A., Wolf C., 2004, MNRAS,
347, 895 ;B. Casaponsa, A. F. Heavens, T. D. Kitching, arxive,2013).Consider
the ellipticity the first assumption of traditional average method
$<\epsilon_{0}>=0$ does not stands any more,while for this Hierarchy
Bayesian method though we are also using the assumption that intrinsic
orientational angle distribution is a flat distribution, we can just
re-model it once more information on galaxy shape coorelation is uncovered.
\end{document}

### 2013-02-13 write-up.tex
a

@@
 $\ \ \ \ $Weak Lensing has become one of the most powerful method
-in exploring the dark universe (Al- brecht et al. 2006; Peacock \&
-Schneider 2006 )
+in exploring the distribution of matter in the Universe on large scales
+(Bartelmann \& Schneider 2001,Al- brecht et al. 2006; Peacock \& Schneider
+2006 ).This powerful method has a various astronomical applications.By
+detecting the weak lensing shear or magnification effect we are able
+to reconstruct the mass properties of galaxy clusters,as well as dark
+matter halos(Dahle et al. 2002; Gray et al. 2002; Clowe, Gonzalez
+\& Markevitch 2004;Sheldon et al. 2004)
 
-As dark energy slows the growth of dark matter structures, these in
-turn affect the appearance of distant galaxies, distorting them slightly
-as gravitational fields deflect their light. This distortion is known
-as cosmic shear.()
+General relativity predicts that the path of light from a distant
+galaxy is distorted by the gravitational potential fluctu- ations
+along the line of sight. As dark energy slows the growth of dark matter
+structures, these in turn affect the appearance of distant galaxies,
+distorting them slightly as gravitational fields deflect their light.
+This distortion is known as cosmic shear.()
 
@@
 the comples ellipticity of a stretched galaxies is an unbiased estimation
-of cosmic shear.However, the distortion induced by cosmic shear is
-typically on the order of a few percent,which is significantly smaller
-than the galaxies's intrinsic shape noise(\textasciitilde{}0.1 level).
+of cosmic shear(Bartelmann \& Schneider 2001).However, the distortion
+induced by cosmic shear is typically on the order of a few percent,which
+is significantly smaller than the galaxies's intrinsic shape noise(\textasciitilde{}0.1
+level).
 
@@
 \end{verse}
-Then we make N random samples from a selected distribution as the "true" reduced shear on each patch.
+Then we make N samples from the prior distriibution of g.In this paper
+we assume the prior distribution of g is gaussian with $\sigma=0.1$.
 
-Finally we calculated the sheared shape of every galaxy on each patch.
+Finally galaxies in N patches are sheared by N different gamma .
 
@@
 
-One intresting thing in shear survey is that the assumption that galaxy
+One intresting in shear survey is that the assumption that galaxy
 pairs have no ellipticity correlation is not entirely accurate. There

### 2013-02-13 write-up.tex
update write-up.tex

@@
 
-\date{03/09/2013}
+\date{02/13/2013}
 \maketitle
@@
 The measurement of cosmic shear is determined by the amount of distortion
-caused to a forewground galaxy. Due to the isotropic universe the
-expect value of a galaxy's intrinsic complex ellipticity is 0. Therefore
-the comples ellipticity of a stretched galaxies is an unbiased estimation
-of cosmic shear(Bartelmann \& Schneider 2001).However, the distortion
-induced by cosmic shear is typically on the order of a few percent,which
-is significantly smaller than the galaxies's intrinsic shape noise(\textasciitilde{}0.1
-level).
+caused to a foreground galaxy. Due to the isotropy of the Universe
+the expect value of a galaxy's intrinsic complex ellipticity $\epsilon$
+is 0. Therefore the comples ellipticity of a stretched galaxies is
+an unbiased estimation of cosmic shear(Bartelmann \& Schneider 2001).However,
+the distortion induced by cosmic shear is typically on the order of
+a few percent,which is significantly smaller than the galaxies's intrinsic
+shape noise(\textasciitilde{}0.1 level).
 
@@
 
-While in this paper what we want to focus is how to use a beysian
-approach to infere cosmic shear independent from which way the galaxy
+While in this paper what we want to focus is how a hierarchy beysian
+approach can infer cosmic shear independently from which way the galaxy
 shape is measured with better accuracy than traditional averaging
@@
 
-One of the major problems for a bayesian inference of shear is that
-even though a lot of measurement have bean made ,we still know little
-about the intrinsic ellipticity distribution of galaxies of the whole
-universe(Leauthaud\&Massey 2007;Joachimi\&Semboloni2012).However in
-our Hierarchy Bayesian method we avoid to making any assumption on
-intrinsic ellipticity distribution.We will show that using a free
-model for intrinsic ellipticity distribution and infere its parameters
-together with cosmic shear we will still out perform the traditional
-averaging method.
+One of the major problems of a bayesian inference of cosmic shear
+is that even though a lot of measurement have bean made ,we still
+know little about the intrinsic ellipticity distribution of galaxies
+of the whole universe(Leauthaud\&Massey 2007;Joachimi\&Semboloni2012).However
+in our Hierarchy Bayesian method we avoid to making up any empirical
+model for intrinsic ellipticity distribution.We will show that using
+a free form model for intrinsic ellipticity distribution and infer
+its parameters together with cosmic shear we can still out perform
+the traditional averaging method.
 

### 2013-02-13 write-up.tex
Update write-up.tex

@@
 General relativity predicts that the path of light from a distant
-galaxy is distorted by the gravitational potential fluctu- ations
+galaxy is distorted by the gravitational potential fluctuations
 along the line of sight. As dark energy slows the growth of dark matter

### 2013-02-13 write-up.tex
Update write-up.tex

@@
 galaxy.Given an telescope that has perfect measurement on galaxies'
-shape their shear estimation method is no different thatn traditional
-averaging method.
+shape their shear estimation method has no difference with traditional
+average method.
 

### 2013-02-14 code/step_gibbs.py
update step_gibbs.py

@@ -1,3 +1,4 @@
+#Gibbs sampler written iin the form of python class
 import random
 import cmath
 import math
@@ -34,7 +35,7 @@ def jacobian(e,e0,g):
 	J4=(reshear(e+delt,g).imag-y)/delt
 	return np.abs(J1*J2-J3*J4)
 def prior(x):
-	return -0.0*np.sum((x[1:]-x[:-1])**2)
+	return -2.0*np.sum((x[1:]-x[:-1])**2)
 def fep(x,alpha,beta):
 	if x<0 or x>1:
 		return 0
@@ -69,15 +70,55 @@ def postfunc(X,E):
 	result[0]=np.sum(result[1:])+prior(P)
 #	result[0]=np.sum(result[1:])
 	return result
-random.seed(93)
-np.random.seed(seed=89)
+class Gibbssampler(function,argus):
+	def __init__(self,function,argus,X0):
+		self.function=function
+		self.argus=argus
+	def run(self,X,prosig,nsteps,Seed=None):
+		np.random.seed(seed=Seed)
+		self.value=sel.function(X,*self.argus)
+		self.pos=1.0*X
+		X1=1.0*X
+		u=np.zeros(NP)
+		self.Chain=np.zeros((Nsteps,ndim))
+		accnum1=0.0
+		accnum2=0.0
+		for i in xrange(nsteps):
+			X1[Nbin:]=self.pos[Nbin:]
+			X1[:Nbin]=self.pos[:Nbin]+np.random.normal(loc=0.0,scale=prosig[:Nbin])
+			fvalue1=self.function(X1,*self.argus)
+			lnprob[0]=fvalue1[0]-self.value[0]
+			m=math.log(random.random())
+			if m<lnprob[0]:
+				accnum1+=1
+				self.pos[:Nbin]=X1[:Nbin]
+				self.value[:]=fvalue1[:]
+			X1[:Nbin]=self.pos[:Nbin]
+			X1[Nbin:]=self.pos[Nbin:]+np.random.normal(loc=0.0,scale=prosig[Nbin:])
+			fvalue1[:]=self.function(X1,*self.argus)
+			lnprob[1:]=fvalue1[1:]-self.value[1:]
+			u[:]=np.log(np.random.rand(NP))
[…]

### 2013-02-14 write-up.tex
update write-up

--- 2013-02-13 write-up.tex
@@
 \usepackage[latin9]{inputenc}
+\usepackage{amsmath}
 \usepackage{amssymb}
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% User specified LaTeX commands.
+\usepackage{babel}
+
 \makeatother
@@
 
-\title{Weak lensing Hierarchy Bayesian Inference }
+\title{Weak Lensing Shear Inference:A Hierarchy Bayesian Approach}
 
-\date{02/13/2013}
+\date{02/14/2013}
 \maketitle
@@
 The measurement of cosmic shear is determined by the amount of distortion
-caused to a foreground galaxy. Due to the isotropy of the Universe
-the expect value of a galaxy's intrinsic complex ellipticity $\epsilon$
-is 0. Therefore the comples ellipticity of a stretched galaxies is
-an unbiased estimation of cosmic shear(Bartelmann \& Schneider 2001).However,
-the distortion induced by cosmic shear is typically on the order of
-a few percent,which is significantly smaller than the galaxies's intrinsic
-shape noise(\textasciitilde{}0.1 level).
+caused to foreground galaxies. Due to the isotropy of the Universe
+the expect value of the intrinsic complex ellipticity $\epsilon$
+of a galaxy is 0. Therefore the complex ellipticity of a stretched
+galaxies is an unbiased estimation of cosmic shear(Bartelmann \& Schneider
+2001).However, the distortion induced by cosmic shear is typically
+on the order of a few percent,which is significantly smaller than
+the galaxies's intrinsic shape noise(\textasciitilde{}0.1 level).
 
@@
 galaxy.Given an telescope that has perfect measurement on galaxies'
-shape their shear estimation method is no different thatn traditional
+shape their shear estimation method has no difference from traditional
 averaging method.
@@
 its parameters together with cosmic shear we can still out perform
-the traditional averaging method.
+the traditional average method.
 
@@
 
-This report is orgnized as following: First we introduced the lensing
+This report is orgnized as following: First we introduce the lensing
 formula used in weak lensing region and how we simulated the lensed
@@
 First the unlensed complex ellipticity $\epsilon$ is generated according
-to probability distribution:$P(|\epsilon|)=Beta(|\epsilon|,2.8,2.8)$
-and $P(\phi)=\frac{1}{\pi}$. $\epsilon=|\epsilon|e^{2\phi i}$.
+to probability distribution:$f(|\epsilon|)=Beta(|\epsilon|,2.8,2.8)$
+and $f(\phi)=\frac{1}{\pi}$. $\epsilon=|\epsilon|e^{2\phi i}$.
 
@@
 In Gibbs sampling ,samples of variable $x_{j}$ is made from the conditional
-probability distribution:$p(x_{j}^{(i)}|x_{1}^{(i)},....,x_{j-1}^{(i)},x_{j+1}^{(i-1)}...)$
+probability distribution:$p(x_{j}^{(i)}|x_{1}^{(i)},....,x_{j-1}^{(i)},x_{j+1}^{(i-1)}...,x_{n}^{(i-1)})$
 
@@
 
-Compared with our data,we can see that our method can at least support
-upcoming cosmic shear surveys.Note that we only used 10,000 data sets
-to quantify m,c due to limited computational time and the uncertainty
-on $\hat{g}$ is large(\textasciitilde{}0.1),if much more data sets
-were collected, these number will probabily be significantly lowered.
+Compare this table with our data,we can see that our method can at
+least support upcoming cosmic shear surveys.Note that we only used
+10,000 data sets to quantify m,c due to limited computing time and
+the uncertainty on $\hat{g}$ is large(\textasciitilde{}0.1),if much
+more data sets were collected, these number will probably be significantly
+lowered.
 
@@
 
-Here we present a Hierarchy Bayesian way in shear inference. Our method
-successfully inferes the cosmic shears of different sky patches and
-the intrinsic shape parameter synchronously.We showed that in the
-area that galaxy density is low,our method can out perform traditional
+Here we present a Hierarchy Bayesian method of shear inference. Our
+method successfully infers the cosmic shears of different sky patches
+and the intrinsic shape parameter synchronously.We showed that in
+the area that galaxy density is low,our method can out perform traditional
 averagemethod by \textasciitilde{}0.01 level. While in most cases

### 2013-02-17 write-up.tex
update write-up  add ratleigh.py

@@
 
-\date{02/14/2013}
+\date{02/16/2013}
 \maketitle
@@
 and Beta function $Beta(p,q)$ are calculated numerically.
+
+One thing to note is that the likelihood of g in patch i only depends
+on the shape parameters but not dependent to g in other patch.Therefore,the
+marginalized likelihood of shape parameters has an equation like:
+
+\begin{equation}
+\ell(\alpha)=\prod_{i}\ell_{i}(\alpha|data_{i})
+\end{equation}
+
+$\ell_{i}(\alpha|data_{i})$ is the marginalized likelihood function
+calculated with data in the ith patch.From this formula we can see
+how better estimation of $\alpha$ will be obtained if we infer more
+sky patches simultaneously.
 

### 2013-02-17 code/rayleigh.py

@@ -1,0 +1,196 @@
+import random
+import cmath
+import math
+import numpy as np
+import matplotlib.pyplot as plt
+from scipy import special 
+from scipy import stats
+N=8
+#number per patch
+NP=64
+#number patches
+NIN=1
+sigma=0.000
+sig=0.05
+Nbin=10
+#number of bins
+ndim=2*NP+Nbin
+#nwalks=300
+index=np.array([i for i in range(NP) for j in range(N)])
+#t = (np.arange(Nbin)+0.5) / float(Nbin)
+inf=np.array([-np.inf for i in range(N*NP)])
+inf1=np.array([-np.inf for i in range(NP+1)])
+def shear(e0,g):
+	return (e0+g)/(1+g.conjugate()*e0)
+def reshear(e,g):
+	return (e-g)/(1-g.conjugate()*e)
+def jacobian(e,e0,g):
+	delt=0.000001
+	x=e0.real
+	y=e0.imag
+	J1=(reshear(e+delt,g).real-x)/delt
+	J2=(reshear(e+delt*1J,g).imag-y)/delt
+	J3=(reshear(e+delt*1J,g).real-x)/delt
+	J4=(reshear(e+delt,g).imag-y)/delt
+	return np.abs(J1*J2-J3*J4)
+def prior(x):
+	return -6.0*np.sum((x[1:]-x[:-1])**2)
+def fep(x,alpha,beta):
+	if x<0 or x>1:
+		return 0
+	return pow(x,alpha-1)*pow(1-x,beta-1)
+def lnfep(x,P):
+	x1=x[np.all([x>=0,x<1],axis=0)]
+	result=np.zeros(N*NP)
+#	result[np.all([x>=0,x<1],axis=0)]=(P[0]-2)*np.log(x1)+(P[1]-1)*np.log(1-x1)-math.log(special.beta(P[0],P[1]))
+	result[np.all([x>=0,x<1],axis=0)]=P[np.floor(x1/(1.0/Nbin)).astype(int)]
+	result[np.any([x<0,x>=1],axis=0)]=-np.inf
+	return result
+def initial(P,average):
+	a=np.zeros(2*NP+Nbin)
+	a[Nbin:]=average
+	a[:Nbin]=P
+	return a
+def lnlikelihood(e,gamma,P):
[…]

### 2013-02-18 write-up.tex
updte write-up.tex

@@
-%% LyX 2.0.2 created this file.  For more info, see http://www.lyx.org/.
+%% LyX 2.0.4 created this file.  For more info, see http://www.lyx.org/.
 %% Do not edit unless you really know what you are doing.
@@
 \usepackage[T1]{fontenc}
-\usepackage[latin9]{inputenc}
+\usepackage[utf8]{luainputenc}
 \usepackage{amsmath}
@@
 \usepackage{graphicx}
+\usepackage{esint}
 
@@
 
-The Jacobi term $|\frac{\partial(x_{0},y_{0})}{\partial(x_{\ell},y_{\ell})}|$
+The Jacobean term $|\frac{\partial(x_{0},y_{0})}{\partial(x_{\ell},y_{\ell})}|$
 and Beta function $Beta(p,q)$ are calculated numerically.
@@
 percentage level.
+
+Figure 10 shows how the mean square error of the Hierarchy Bayesian
+method varies with the number of sky patches used,in comparison with
+traditional average method and likelihood analysis with correct P($\epsilon$)
+hard-set.from this figure we can see that the mean square error of
+the Hierarchy Bayesian method decreases as the number of patches goes
+up,while this trend is less significant as number of patches becomes
+larger.Moreover,down to 8 patches this Hierarchy Bayesian method still
+out perform the traditional average method. Meanwhile the likelihood
+analysis with correct P($\epsilon$) shows higher accuracy than Hierarchy
+Bayesian method. That is consistent with our speculation. When the
+number of patches goes to infinity ,we will have correct estimation
+on P($\epsilon$) and Hierarchy Bayesian method converges to likelihood
+analysis with correct $P(\epsilon)$ hard-set,ignoring the difference
+between our step function model and real beta function,of course.
+
+\includegraphics[scale=0.5]{Np_step}
+
+\includegraphics[scale=0.5]{N16NP_vary}
+
+Figure 10:Mean square error VS Number of patches.In the upper graph
+number of galaxies per patch is 8 while in the lowwer it's 16.The
+Green line is mean square error of traditional average while the red
+line is that of likelihood analysis with correct $P(\epsilon)$ .
+
+\subsection{Shape Measurement Error}
+
+In this part we will discuss how the shape measurement error will
+affect the relative accuracy of this Hierarchy Bayesian method.As
+mentioned before ,we try to avoid any image process which is another
+important aspect of Weak Lensing survey ,so we simply assume a 2D
+Gaussian noise on ellipticity measurement.
+
+With that Gaussian noise the data we can obtain becomes the observed
+ellipticity $\epsilon_{ob}$,whoes probability distribution is 
+\begin{equation}
+f(\epsilon_{ob}|\epsilon_{\ell})\varpropto e^{-\frac{(\epsilon_{ob}-\epsilon_{\ell})^{2}}{2\sigma^{2}}}
+\end{equation}
+
+Therefore the likelihood of $g$ and $\alpha$ becomes
+\begin{equation}
+L(g,\alpha|\epsilon_{ob})=P(\epsilon_{ob}|g,\alpha)=\intop f(\epsilon_{ob}|\epsilon_{\ell})P(\epsilon_{\ell}|g,\alpha)d\epsilon_{\ell}
+\end{equation}
 

### 2013-02-19 prefactor.tex
add prefactor

%% LyX 2.0.4 created this file.  For more info, see http://www.lyx.org/.
%% Do not edit unless you really know what you are doing.
\documentclass[english]{article}
\usepackage[T1]{fontenc}
\usepackage[utf8]{luainputenc}
\usepackage{esint}
\usepackage{babel}
\begin{document}
One major limitation of the step function model is that a prior regulazier
$Prior(\alpha)=exp(-\xi\sum(\alpha_{i}-\alpha_{i-1})^{2})$ is needed
to infer the P($\epsilon$) and g correctly and the constant prefactor
$\xi$ needs to be tuned.In our test the true P($\epsilon$) is set
to be a smooth function ,which is a natural assumption for P($\epsilon$).The
effect of this prior regulazier is to keep the inferred P($\epsilon$)
smooth. if the constant $\xi$ is not big enough the inferred P($\epsilon$)
will have an oscilation noise and the accuracy of g inference will
also decreases. Thus an empirical formula for $\xi$ is helpful to
tune this prefactor by simulations. from several tests we find that
$\xi$ is proportional to the mean data density and can be approximated
by this empirical formula.
\begin{equation}
\xi=<\rho>/256
\end{equation}

Here $<\rho>=\int Nf^{2}(x)dx$ is the mean data density. With the
help of this empirical formula,$\xi$ can be tuned by doing some simulation
which has similar data distribution with the real data.
\end{document}

### 2013-02-19 prefactor.tex
Update prefactor.tex

@@
 \begin{document}
-One major limitation of the step function model is that a prior regulazier
+One limitation of the step function model is that a prior regulazier
 $Prior(\alpha)=exp(-\xi\sum(\alpha_{i}-\alpha_{i-1})^{2})$ is needed

### 2013-02-19 prefactor.tex
Update prefactor.tex

@@
 will have an oscilation noise and the accuracy of g inference will
-also decreases. Thus an empirical formula for $\xi$ is helpful to
-tune this prefactor by simulations. from several tests we find that
+also decrease. From several tests we find that
 $\xi$ is proportional to the mean data density and can be approximated
@@
 Here $<\rho>=\int Nf^{2}(x)dx$ is the mean data density. With the
-help of this empirical formula,$\xi$ can be tuned by doing some simulation
-which has similar data distribution with the real data.
+help of this empirical formula,we can tune this prefactor $\xi$ 
+by doing some simulation which has similar data distribution with the real data.
 \end{document}

### 2013-02-19 prefactor.tex
Added comments and rearrangements

@@
 \begin{document}
-One limitation of the step function model is that a prior regulazier
-$Prior(\alpha)=exp(-\xi\sum(\alpha_{i}-\alpha_{i-1})^{2})$ is needed
-to infer the P($\epsilon$) and g correctly and the constant prefactor
-$\xi$ needs to be tuned.In our test the true P($\epsilon$) is set
-to be a smooth function ,which is a natural assumption for P($\epsilon$).The
-effect of this prior regulazier is to keep the inferred P($\epsilon$)
-smooth. if the constant $\xi$ is not big enough the inferred P($\epsilon$)
-will have an oscilation noise and the accuracy of g inference will
-also decrease. From several tests we find that
+One limitation of the step function model is that it needs to be {\it regularized}; 
+this is achieved by assigning a prior PDF for the step heights $\alpha$.
+We use the form
+$Prior(\alpha)=exp(-\xi\sum(\alpha_{i}-\alpha_{i-1})^{2})$ 
+% alpha should be a vaector here, and you should write the prior as P(alpha|\xi) to show the dependence on the 
+% regularisation constant.
+when inferring the P($\epsilon$) and $g$.
+The choice of this functional form corresponds to the assumption
+that the true P($\epsilon$) is smooth, which seems fairly natural. This function has a hyperparameter, 
+$\xi$, that needs to be set somehow. If $\xi$ is too small, the inferred P($\epsilon$)
+will be too noisy, and the accuracy of the $g$ inference will
+decrease. Likewise, choosing an $\xi$ that is too large, the inferred P($\epsilon$) will be too smooth, and the 
+data will be under-fitted. In principle one could infer $\xi$ form the data at hand, but in practice we find...
+% What happened when you tried to infer \xi? Why does this not work?
+We find that
 $\xi$ is proportional to the mean data density and can be approximated
-by this empirical formula.
+by the following empirical formula:
 \begin{equation}
@@
 \end{equation}
-
+% What is the "data density" and why does it appear squared here?
 Here $<\rho>=\int Nf^{2}(x)dx$ is the mean data density. With the
-help of this empirical formula,we can tune this prefactor $\xi$ 
+help of this empirical formula, we can tune this prefactor $\xi$ 
 by doing some simulation which has similar data distribution with the real data.
+% This needs better wording: justifying your choices is very important!
 \end{document}

### 2013-02-21 write-up.tex
update write-up

@@
 
-\date{02/16/2013}
+\date{02/19/2013}
 \maketitle
@@
 $|\frac{\partial(|\epsilon_{0}|,\phi_{0})}{\partial(|\epsilon|,\phi)}|$
-is the Jacobi Determinant term. 
+is the Jacobean Determinant term. 
 \begin{equation}
@@
 $(x_{0},y_{0})$ and $(x_{\ell},y_{\ell})$ are the Cartesian coordinates
-of $\epsilon_{0}$ and $\epsilon_{\ell}$ on the complex plane.
-
-When $|\epsilon_{0}|\longmapsto0$ ,$\epsilon\approx\epsilon_{0}+g$.Therefore,$|\frac{\partial(x_{0},y_{0)}}{\partial(x,y)}|\mapsto1$.Thus
-when $|\epsilon_{0}|\mapsto0$ the Jacobi term $|\frac{\partial(|\epsilon_{0}|,\phi_{0})}{\partial(|\epsilon|,\phi)}|\mapsto\infty$.
-
-In this paper 
-\begin{equation}
-P(\epsilon_{0}|\alpha)=|\epsilon_{0}|^{p-1}(1-|\epsilon_{0}|)^{q-1}/Beta(p,q)
-\end{equation}
-
-Thus
-
-\begin{equation}
-L(g,\alpha|\epsilon_{\ell})\propto|\epsilon_{0}|^{p-2}(1-|\epsilon_{0}|)^{q-1}|\frac{\partial(x_{0},y_{0})}{\partial(x_{\ell},y_{\ell})}|/Beta(p,q)
-\end{equation}
-
-We can see that when p<2 $L(g,\alpha|\epsilon_{\ell})$ will have
-singular points at $g=\epsilon_{\ell}$.In this paper to avoid this
-issue we restrict p always larger than 2.
-
-The Jacobean term $|\frac{\partial(x_{0},y_{0})}{\partial(x_{\ell},y_{\ell})}|$
-and Beta function $Beta(p,q)$ are calculated numerically.
+of $\epsilon_{0}$ and $\epsilon_{\ell}$ on the complex plane.This
+Jacobean term is numerically computaed.
 
@@
 
+When $|\epsilon_{0}|\longmapsto0$ ,$\epsilon\approx\epsilon_{0}+g$.Therefore,$|\frac{\partial(x_{0},y_{0)}}{\partial(x,y)}|\mapsto1$.Thus
+when $|\epsilon_{0}|\mapsto0$ the Jacobi term $|\frac{\partial(|\epsilon_{0}|,\phi_{0})}{\partial(|\epsilon|,\phi)}|\mapsto\infty$.
+
+In this section 
+\begin{equation}
+P(\epsilon_{0}|\alpha)=|\epsilon_{0}|^{p-1}(1-|\epsilon_{0}|)^{q-1}/Beta(p,q)
+\end{equation}
+
+Thus
+
+\begin{equation}
+L(g,\alpha|\epsilon_{\ell})\propto|\epsilon_{0}|^{p-2}(1-|\epsilon_{0}|)^{q-1}|\frac{\partial(x_{0},y_{0})}{\partial(x_{\ell},y_{\ell})}|/Beta(p,q)
+\end{equation}
+
+We can see that when p<2 $L(g,\alpha|\epsilon_{\ell})$ will have
+singular points at $g=\epsilon_{\ell}$.In this section to avoid this
+issue we restrict p always larger than 2.
+
+The Jacobean term $|\frac{\partial(x_{0},y_{0})}{\partial(x_{\ell},y_{\ell})}|$
+and Beta function $Beta(p,q)$ are calculated numerically.
+
 Figure 2 shows the samples of g for 64 patches and 8 galaxies in each
@@
 \begin{equation}
-Prior(\alpha)=exp(-\xi*\sum(\alpha_{i}-\alpha_{i-1})^{2})
+Prior(\vec{\alpha}|\xi)=exp(-\xi\sum(\alpha_{i}-\alpha_{i-1})^{2})
 \end{equation}
@@
 
-Figure 10 shows how the mean square error of the Hierarchy Bayesian
+Figur 10 shows the distribution of $g_{estimation}-g_{true}$.From
+the figure we can see that it's a gaussian like distribution centrered
+at 0.
+
+\includegraphics[scale=0.5]{dg2}
+
+Figure 11 shows how the mean square error of the Hierarchy Bayesian
 method varies with the number of sky patches used,in comparison with
@@
 
-Figure 10:Mean square error VS Number of patches.In the upper graph
+Figure 11:Mean square error VS Number of patches.In the upper graph
 number of galaxies per patch is 8 while in the lowwer it's 16.The
@@
 line is that of likelihood analysis with correct $P(\epsilon)$ .
+
+One limitation of the step function model is that it needs to be \textit{regularized};
+this is achieved by assigning a prior PDF for the step heights $\vec{\alpha}$.
+We use the form $Prior(\vec{\alpha}|\xi)=exp(-\xi\sum(\alpha_{i}-\alpha_{i-1})^{2})$
+when inferring the P($\epsilon$) and $g$. The choice of this functional
+form corresponds to the assumption that the true P($\epsilon$) is
+smooth, which seems fairly natural. This function has a hyperparameter,
+$\xi$, that needs to be set somehow. If $\xi$ is too small, the
+inferred P($\epsilon$) will be too noisy, and the accuracy of the
+$g$ inference will decrease. Likewise, choosing an $\xi$ that is
+too large, the inferred P($\epsilon$) will be too smooth, and the
+data will be under-fitted. In principle one could infer $\xi$ form
+the data at hand, but in practice we find that .
+
+a flat prior PDF for $\xi$ will make the inferred $P(\epsilon)$
+too noisy.Therefore to make the inferred $P(\epsilon)$ smooth enough
+we still need to assign some prior PDF on $\xi$ that pushes $\xi$
+to a larger region,and this prior PDF also need to be tuned. We find
+that $\xi$ is proportional to the mean data number density and can
+be approximated by the following empirical formula: 
+\begin{equation}
+\xi=N<\rho(|\epsilon|)>/256*\frac{Nbin}{10}
+\end{equation}
+Here $<\rho|\epsilon|>=\int\rho(|\epsilon|)^{2}d(|\epsilon|)$ corresponds
+to the average of data number density weighted with number density,and
+Nbin is the number of bins used in step function model. With the help
+of this empirical formula, we can tune this prefactor $\xi$ by doing
+some simulation which has similar data distribution with the real
+data.
 
@@
 
-\section{Systematic Bias}
+\section{Systematical Bias}
 
-In this section,we measured the levels of possible systemmatic bias
-led by this HB method.
+$\ \ \ \ $In this section,we measured the levels of possible systemmatical
+bias led by this HB method.
 
@@
 
-The accuracy in Weak Lensing measurement depends on both galaxies
-shape measurement and shear inference period.In this paper our main
-concern is how to infere shear in a HB method instead off traditional
-averaging method and it does not involve the shape measurement part
-.Therefore we assume we have perfect galaxies ellipticity measurement,and
-all the possible inaccuracy is due to this HB shear inference method.
+The accuracy of Weak Lensing survey depends on both galaxy shape measurement
+and shear inference .In this paper our main concern is how to infere
+shear in a HB method instead off traditional averaging method and
+it does not involve the shape measurement part .Therefore we assume
+we have perfect galaxies ellipticity measurement,and all the possible
+inaccuracy is due to this HB shear inference method.
 
-Using 10,000 data sets we are able to get the value of m and c for
-both beta function and step function model.Each data set we use in
-this section has 64 patches with 8 galaxies in eah patch.
+We calculated the average of $g^{estimated}-g^{true}$ of 10,000 data
+sets as described above.Each data set has 64 patches and 8{*}64 galaxies,and
+the true P($\epsilon$) is Beta(2.8,2.8) .For both Beta function model
+and step funtion model we then determin the best fitted parameters
+m and c of fomula (15).Figure 9 shows an example of step funtion model
+with prior prefator $\xi=3$.The results of the systematical bias
+analysis are tabulated in table 1.
 
-The region for $g_{i}^{true}$ is -0.1\textasciitilde{}0.1 .
+\includegraphics[scale=0.5]{g1bias}
 
-For beta function model :
+\includegraphics[scale=0.5]{g2bias}
+\begin{quote}
+Figure 9: Linear fit of $\delta g_{i}-g_{i}$ relationship for step
+function model.
 
-\begin{tabular}{|c|c|c|}
+\begin{tabular}{|c|c|c|c|}
 \hline 
- & Expect Value  & STD\tabularnewline
+Beta Model & Expect Value  & $\sigma$ & S/N\tabularnewline
 \hline 
 \hline 
-m1  & -0.00420  & 0.00304\tabularnewline
+m1  & -0.00420  & 0.00304 & 1.38\tabularnewline
 \hline 
-c1  & 1.66$*10^{-4}$  & 1.73$*10^{-4}$\tabularnewline
+c1  & 1.66$*10^{-4}$  & 1.73$*10^{-4}$ & 0.96\tabularnewline
 \hline 
-m2  & -0.00386  & 0.00290\tabularnewline
+m2  & -0.00386  & 0.00290 & 1.31\tabularnewline
 \hline 
-c2  & 2.30$*10^{-4}$  & 1.81$*10^{-4}$\tabularnewline
+c2  & 2.30$*10^{-4}$  & 1.81$*10^{-4}$ & 1.27\tabularnewline
 \hline 
@@
 
-For step function model:
-
-\begin{tabular}{|c|c|c|}
+\begin{tabular}{|c|c|c|c|}
 \hline 
- & Expect Value  & STD\tabularnewline
+Step Model & Expect Value  & $\sigma$ & S/N\tabularnewline
 \hline 
 \hline 
-m1  & 0.00502  & 0.00287\tabularnewline
+m1  & -6.09{*}$10^{-4}$ & 0.00239 & 0.25\tabularnewline
 \hline 
-c1  & 2.05$*10^{-4}$  & 1.73$*10^{-4}$\tabularnewline
+c1  & 1.82$*10^{-4}$  & 1.44$*10^{-4}$ & 1.26\tabularnewline
 \hline 
-m2  & 0.00156  & 0.00292\tabularnewline
+m2  & 0.00178  & 0.00281 & 0.63\tabularnewline
 \hline 
-c2  & 2.14$*10^{-4}$  & 1.87{*}$10^{-4}$\tabularnewline
+c2  & 2.978$*10^{-4}$  & 1.71{*}$10^{-4}$ & 1.74\tabularnewline
 \hline 
@@
 
-\includegraphics[scale=0.5]{step_g1}
-
-\includegraphics[scale=0.5]{g2_step} 
-\begin{quote}
-Figure 9: Linear fit of $\delta g_{i}-g_{i}$ relationship for step
-function model. 
+Table 1:Tabulated measures of multiplicative error <$m_{i}>$ and
+additive error $<c_{i}>$and their standard deviations ,along with
+their S/N ratio. 
 \end{quote}
-As we can see from the data and graph no significant systematic bias
-can be found using 10,000 data sets.With that amount of data we able
-to narrow down m to $\sim10^{-3}$ and c to $\sim10^{-4}$.
-
 In Table 1 we show the requirements on m, c for current, upcoming

### 2013-03-11 docs/introduction.tex
Started MNRAS paper, with sections to be designed by Yike

%% LyX 2.0.4 created this file.  For more info, see http://www.lyx.org/.
%% Do not edit unless you really know what you are doing.
\documentclass[english]{article}
\usepackage[T1]{fontenc}
\usepackage[latin9]{inputenc}
\usepackage{textcomp}
\usepackage{babel}
\begin{document}

\part*{Introduction}

\section{Bias}

This bias on the shear is usually quantifi{}ed in terms of multiplicative
and additive errors This bias on the shear is usually quantifi{}ed
in terms of multiplicative and additive errors $m_{i}$ and $c_{i}$.
\begin{equation}
\hat{\gamma_{i}}=(1+m_{i})\gamma_{i}^{t}+c_{i}
\end{equation}

The requirements on the level of systematic errors for current and
future galaxy surveys are expressed in terms of mi, ci in Amara \&
R\textasciiacute{}efr\textasciiacute{}egier (2008).

For the simple average method,the systematic error of a shear measurement
method can be tested on a fi{}nite number of images in the absence
of shape noise by performing a \textquoteleft{}ring-test\textquoteright{}
(Nakajima \& Bernstein 2007).

For the traditional average method the bias of sear measurement comes
from the convolution with the PSF,pixelisation of the image , pixel
noise on the image due to the fi{}nite number of photons from the
source and atmosphere,and all the other effects that may cause error
in the galaxy ellipticity measurement.

(Tomasz Kacprzak\&Joe Zuntz 2012) present a method to effectively
remove this noise bias for realistic galaxy images. Using a forward
model fi{}tting, Maximum Likelihood approach for parameter estimation.
They create a model of the bias as a function of galaxy and PSF parameters
by determining their bias from various simulations that sample parameter
space. They demonstrate that this procedure successfully removes the
noise bias to the accuracy required by upcoming galaxy surveys.

\section{P(e) Intrinsic ellipticity distribution}

A number of studies have been made of the distribution of galaxy ellipticities
(e.g. ). These studies find a wide variation in distribution of |e|
, which appears strongly dependent on apparent magnitude.

(Leauthaud\&Massey 2007) undertake a measurement of the intrinsic
shape noise, $\sigma_{int}$, as a function of magnitude, size and
redshift,by derive an empirical estimation of the shape measurement
error, $\sigma_{measure}$.Then subtract it from $\sigma_{\gamma}^{2}$.
(The uncertanty of shear measurement in simple average is$\sigma_{\gamma}^{2}=\sigma_{int}^{2}+\sigma_{measure}^{2}$)

(http://arxiv.org/pdf/astro-ph/0702359v1.pdf)

(Joachimi\&Semboloni2012) study both the polarisation dispersion and
distribution of galaxy ellipticity using COSMOS data.

Their results shows a clear tendency towards lower $\sigma_{e}$ for
luminous galaxies with MV< \textminus{}22 in a broad redshift range
0.5 < z < 1.8.

They also plot P(|e|) for the full LRG sample and non-LRG galaxies
in the magnitude range \textminus{}19 < MV < \textminus{}17 ,based
on both COSMOS data and results from the simulation-based models.

\section{lensfit}

(Miller\& T. D. Kitchicung2007 ) proposed a modelfitting approach
in the galaxy shape measurement and evaluated how shear sensitivity
should be calculae based on posterior distribution of galaxies shape.

(Gamma estimaion:$\hat{g}=\frac{\sum w_{i}<e>_{i}}{\sum\partial<e>_{i}/\partial g}$
when the shape measurement is perfect thismeasurement goes back to
simple average)

It convolves the galaxy models with the PSF to calculate the posterior
probability of the model given the data then marginalize over galaxy
size, centroid and bulge fraction.The shear is then estimated in a
Bayesian way from this posterior probability surface.

To calculate the ellipticity prior which isrequired by the lensfit
method,(Miller\&T. D. Kitching2008) proposed an iterative mehod .(In
their model P(|e|) depends on 3 parameters and has a form cos{*}exp).They
proposed a model forP(|e|) and iteratively adjust three parameters
until the summed posterior and prior distributions agree.(? It looks
like they do not cares about the shear while calculating the ellipticity
posterior,then they use it in the shear estimator.?)

CFHTLenS is the fi{}rst weak lensing survey to apply the lensfi{}t
model fi{}tting method. 
\end{document}

### 2013-03-11 docs/ms.tex
Started MNRAS paper, with sections to be designed by Yike

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Hierarchical Inference in Weak Lensing: Inferring Pr(e)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[useAMS,usenatbib]{mn2e}
%% letterpaper
%% a4paper

% \voffset=-0.8in

% Packages:
\input psfig.sty
\usepackage{xspace}
\usepackage{graphicx}

% Macros:
\input{macros.tex}
\input{addresses.tex}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\title[Hierarchical Inference in Weak Lensing]
{Hierarchical Inference of the Intrinsic Ellipticity
Distribution of Galaxies during Weak Lensing Analysis}

\author[Tang et al]{%
  Yike~Tang$^{1}$,
  David W. Hogg,$^{1}$
  Philip~J.~Marshall$^{2}$
  \medskip\\
  $^1$\nyu\\
  $^2$\oxford
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

\date{to be submitted to MNRAS}

\pagerange{\pageref{firstpage}--\pageref{lastpage}}\pubyear{2010}

\maketitle

\label{firstpage}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{abstract}

\noindent\flag{Hogg}{Do you want to try and write an abstract?}

\end{abstract}

% Full list of options at http://www.journals.uchicago.edu/ApJ/instruct.key.html

\begin{keywords}
  gravitational lensing
\end{keywords}

\setcounter{footnote}{1}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%  SECTION 1: INTRODUCTION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Introduction}
\label{sec:intro}

\flag{Yike}{Plan the sections of your paper, and write very brief notes on
what you want to say in each of them. You will find it helpful to divide
them into sub-sections, and even paragraphs. You may also want to put in
placeholder figures and tables; if you do, make sure to write the captions of
them. The itemized conclusions should be partial answers to a corresponding
list of questions in the introduction. You can write these now, as incomplete
statements: when you know what your findings are, you can complete them.}

% WL as cosmological and astrophysical probe.

% Information is scarce. 
% Expensive, high precision future. Motivation.

% This paper: toy problem, exploring one aspect of analysis.

% History of shear estimation, and treatment of Pr(e).

This paper is organized as follows...

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%  SECTION N: XXX
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{XXX}
\label{sec:XXX}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%  SECTION N: XXX
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{XXX}
\label{sec:XXX}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%  SECTION N: XXX
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{XXX}
\label{sec:XXX}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%  SECTION X: DISCUSSION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Discussion}
\label{sec:discuss}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%  SECTION X: CONCLUSIONS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Conclusions}
\label{sec:conclusions}

In summary, ...

\begin{itemize}

\item We ...

\item The ...

\item The ...

\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%  ACKNOWLEDGMENTS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section*{Acknowledgments}

We thank XXX for useful discussions and suggestions.

\input{acknowledgments.tex}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%  APPENDICES
% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% 
% \appendix
% 
% \section{}
% \label{sec:appendix}
% 
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%  REFERENCES
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% MNRAS does not use bibtex, input .bbl file instead. 
% Generate this in the makefile using bubble script in scriptutils:

%   bubble -f PS1QLS-survey.tex references.bib

\bibliographystyle{apj}
\bibliography{references}
%\input{PS1QLS-survey.bbl}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\label{lastpage}
\bsp

\end{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2013-03-12 docs/ms.tex
an abstract for Yike and Phil, as requested

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% in this abstract, below, check the use of -, --, and ---.  Understand?
 
 \begin{abstract}
-
-\noindent\flag{Hogg}{Do you want to try and write an abstract?}
-
+Weak-lensing projects---to measure galaxy--galaxy lensing or the shear--shear
+correlation function---often make use of estimators that involve simple or weighted
+means of measured galaxy ellipticities.  Here we propose moving to a probabilistic inference
+framework for weak-lensing projects, in which the both the distribution of unlensed
+(intrinsic) galaxy ellipticities and the distribution of ellipticity measurement noise contributions
+are both treated as priors.  We perform hierarchical inference to \emph{infer} the
+unlensed ellipticity distribution simultaneously with the shear map.  The best
+shear-field estimators (point estimates), in this context, become
+maximum-\emph{marginalized}-likelihood estimates, in which uncertainty about the
+inferred unlensed distribution has been marginalized out.  We show that our proposed
+estimators perform better than simple mean-ellipticity estimators both in terms of
+bias and variance.  We also show that as the number of observed galaxies becomes
+large, the performance of our proposed estimators approaches the performance of a
+magical maximum-likelihood estimator that could be constructed if the true unlensed
+ellipticity distribution were known \textit{a priori}.  Importantly, this work only
+considers the \emph{catalog-level} problem of how to combine galaxy ellipticity
+measurements; it does not consider the problem of making those measurements in the
+first place.  In the end we argue that weak lensing projects ought to move beyond
+point estimates and instead propagate full likelihood-function information about
+the shear field forward into scientific analyses.  Only this could properly
+propagate uncertainty without introducing additional catalog-generated variance.
 \end{abstract}

### 2013-03-12 docs/formula.tex
add formula.tex

%% LyX 2.0.4 created this file.  For more info, see http://www.lyx.org/.
%% Do not edit unless you really know what you are doing.
\documentclass[english]{article}
\usepackage[T1]{fontenc}
\usepackage[utf8]{luainputenc}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{esint}

\makeatletter
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% User specified LaTeX commands.
\usepackage{babel}

\makeatother

\usepackage{babel}
\begin{document}
Likelihood:

p($\epsilon_{\ell}|\vec{g},\alpha)=P(\epsilon_{0}(\epsilon_{\ell},\vec{g})|\alpha)*|\frac{\epsilon_{0}(\epsilon_{\ell},\vec{g})}{\epsilon_{\ell}}|$

Prior:

Prior($\vec{g})=1$ $|\vec{g}|<1$ else Prior(g)=0

Prior($\alpha)=exp(-\underset{i}{\xi\sum}(\alpha_{i}-\alpha_{i-1})^{2})$

Marginalized likelihood:

p($\epsilon_{\ell}|\vec{g})=\int p(\epsilon_{\ell}|\vec{g},\alpha)p(\alpha|\vec{g})d\alpha$

with $p(\alpha|\vec{g})=Prior(\alpha)$

$p(\epsilon_{l}|\vec{g})=\int p(\epsilon_{\ell}|\vec{g},\alpha)*Prior(\alpha)d\alpha$

$p(\epsilon_{\ell}|g_{1})=\underset{|g|<1}{\int}p(\epsilon_{\ell}|\vec{g})dg_{2}$
\end{document}

### 2013-03-12 docs/write-up.tex
add formulas

--- 2013-02-21 write-up.tex
@@
 
-\title{Weak Lensing Shear Inference:A Hierarchy Bayesian Approach}
+\title{Weak Lensing Shear Inference:A Hierarchical Bayesian Approach}
 
-\date{02/19/2013}
+\date{02/27/2013}
 \maketitle
 \begin{abstract}
-We present a Hierarchy Bayesian method for shear inference in Weak
-Lensing survey. With this method we are able to infer synchronously
-cosmic shear at different sky patches as well as the intrinsic shape
-distribution. We show that this Hierarchy Bayesian method is more
-accurate than the traditional average method and (prove to a large
-extent )it is an unbiased estimation of shear.
+We present an Hierarchical Bayesian approach to infer the shear map
+caused by Weak Lensing effect,by solving a toy weak lensing problem,in
+which we set a uniform shear on each sky patch and we have galaxies'
+ellipticity data either with no measurement error or a simple 2-D
+Gaussian noise. This hierarchical inference involves learning the
+parameters of an exceedingly flexible model for the distribution of
+unlensed galaxies' ellipticity, subject to a constraint that this
+unlensed distribution is isotropical on ellipticity orientaion.It
+is showed that using this flexible model P($\epsilon$|$\alpha$),we
+are able to infer shears of different sky patches and their common
+unlensed ellipticity distribution simultaneously.Though the average
+of galaxies' ellipticity gives a simple estimation of cosmological
+shear,we show that this hierarchical Bayesian method is more accurate
+and precise.
 
-Key words:gravational lensing-methods;data analysis-methods;bayesian
-inference 
+Key words:gravational lensing-methods;data analysis-methods;hierarchical
+bayesian inference 
 \end{abstract}
@@
 \begin{equation}
-L(g,\alpha|\epsilon_{\ell})=P(\epsilon_{\ell}|g,\alpha)=P(\epsilon_{0}(g)|\alpha)*|\frac{\partial(|\epsilon_{0}|,\phi_{0})}{\partial(|\epsilon_{\ell}|,\phi_{\ell})}|
+L(\vec{g},\alpha|\epsilon_{\ell})=p(\epsilon_{\ell}|\vec{g},\alpha)=P(\epsilon_{0}(\vec{g})|\alpha)*|\frac{\partial\epsilon_{0}}{\partial\epsilon_{\ell}}|
 \end{equation}
 
-$\epsilon_{0,}\epsilon_{\ell,}$ means the unlensed and lensed elliticity.
-$\alpha$ the parameter of the distribution of unlensed ellipticity.
+Note that both $\epsilon_{0}$ and $\epsilon_{\ell}$are complex numbers.So
+$|\frac{\partial\epsilon_{0}}{\partial\epsilon_{\ell}}|$ is the Jacobian
+determinant term.Here the prior distribtuion we use for $\vec{g}$
+is a 2Dflat distribution in the region $|g|<1$.Therefore $prior(\vec{g)}=\begin{cases}
+1 & |\vec{g}|<1\\
+0 & |\vec{g}|>1
+\end{cases}$
 
-Due to the homogeneous universe,we can believe that all the galaxies
-in different sky patches have the same intrinsic shape distribution.Therefore,in
-order to get higher accuracy,what we do is to infere reduced shears
-of a number of sky patches simultaneously with their common shape
-parameter $\alpha$. 
+The prior of $\alpha$ some how depends on the model we choose for
+intrinsic ellipticity distribution .When we use the step function
+model for P($\epsilon_{0}$),we find that we need to use a prior on
+$\alpha$ .
 \begin{equation}
-L(\vec{g},p,q|\epsilon_{\ell})=\prod_{i}\prod_{j}P(\epsilon_{0-j}(g_{i})|\alpha)|\frac{\partial(x_{0-j},y_{0-j})}{\partial(x_{\ell-j},y_{\ell-j})}|)
+Prior(\vec{\alpha}|\xi)=exp(-\xi\sum(\alpha_{i}-\alpha_{i-1})^{2})
 \end{equation}
 
-i denotes ith patch and j denotes jth galaxies in a patch.
-
-In this toy model,we choose two models for the distribution of unlensed
-ellipticity :One is Beta distribution model.In this model we assume
-the intrinsic ellipticity distribution is a beta distribution with
-unknown parameter p and q.,The other one is step function model.Here
-we devide 2D plane into a number of bins,and probability on each bin
-is a free parameter.In later section we will show that we can get
-similar results from these two models.
-
-$|\frac{\partial(|\epsilon_{0}|,\phi_{0})}{\partial(|\epsilon|,\phi)}|$
-is the Jacobean Determinant term. 
+Given the likehood functions and priors we can also calculated the
+marginalized likelihood function.
 \begin{equation}
-|\frac{\partial(|\epsilon_{0}|,\phi_{0})}{\partial(|\epsilon_{\ell}|,\phi_{\ell})}|=|\frac{\partial(|\epsilon_{0}|,\phi_{0})}{\partial(x_{0},y_{0})}*\frac{\partial(x_{0},y_{0})}{\partial(x_{\ell},y_{\ell})}*\frac{\partial(x_{\ell},y_{\ell})}{\partial(|\epsilon_{\ell}|,\phi_{\ell})}|=\frac{|\epsilon_{\ell}|}{|\epsilon_{0}|}*|\frac{\partial(x_{0},y_{0})}{\partial(x_{\ell},y_{\ell})}|
+p(\epsilon_{\ell}|\vec{g})=\int p(\epsilon_{\ell}|\vec{g},\alpha)p(\alpha|\vec{g})d\alpha
 \end{equation}
 
-$(x_{0},y_{0})$ and $(x_{\ell},y_{\ell})$ are the Cartesian coordinates
-of $\epsilon_{0}$ and $\epsilon_{\ell}$ on the complex plane.This
-Jacobean term is numerically computaed.
+Since $p(\alpha)$ does not explicitly depends on $\vec{g}$ .$p(\alpha|\vec{g})$is
+just $Prior(\vec{\alpha}|\xi)$.Therefore,we have marginalized likehood
+\begin{equation}
+p(\epsilon_{\ell}|\vec{g})=\int p(\epsilon_{\ell}|\vec{g},\alpha)Prior(\vec{\alpha}|\xi)d\alpha
+\end{equation}
 
@@
 When $|\epsilon_{0}|\longmapsto0$ ,$\epsilon\approx\epsilon_{0}+g$.Therefore,$|\frac{\partial(x_{0},y_{0)}}{\partial(x,y)}|\mapsto1$.Thus
-when $|\epsilon_{0}|\mapsto0$ the Jacobi term $|\frac{\partial(|\epsilon_{0}|,\phi_{0})}{\partial(|\epsilon|,\phi)}|\mapsto\infty$.
+when $|\epsilon_{0}|\mapsto0$ the Jacobean term $|\frac{\partial(|\epsilon_{0}|,\phi_{0})}{\partial(|\epsilon|,\phi)}|\mapsto\infty$.
 
@@
 the value of $\sqrt{mean(\hat{g}}-g^{true})^{2}$
-
-for HB method the typical value is \textasciitilde{}0.17 While for
-traditional averaging method it's \textasciitilde{}0.18.
 
@@
 \includegraphics[scale=0.5]{N16NP_vary}
+
+\includegraphics[scale=0.5]{errorN8}
 
@@
 \hline 
-m2  & 0.00178  & 0.00281 & 0.63\tabularnewline
+m2  & -3.48{*}$10^{-4}$ & 0.00214 & 0.16\tabularnewline
 \hline 
-c2  & 2.978$*10^{-4}$  & 1.71{*}$10^{-4}$ & 1.74\tabularnewline
+c2  & 2.01$*10^{-4}$  & 1.29{*}$10^{-4}$ & 1.56\tabularnewline
 \hline 

### 2013-03-12 docs/formula.tex
formulas

@@
 \begin{document}
-Likelihood:
+If we know the ellipticity distribution of unlensed galaxies based
+on some parasmeters $\alpha$,the likelihood of reduced shear $g$
+and parameter $\alpha$ is like:
 
-p($\epsilon_{\ell}|\vec{g},\alpha)=P(\epsilon_{0}(\epsilon_{\ell},\vec{g})|\alpha)*|\frac{\epsilon_{0}(\epsilon_{\ell},\vec{g})}{\epsilon_{\ell}}|$
+\begin{equation}
+L(\vec{g},\alpha|\epsilon_{\ell})=p(\epsilon_{\ell}|\vec{g},\alpha)=P(\epsilon_{0}(\vec{g})|\alpha)*|\frac{\partial\epsilon_{0}}{\partial\epsilon_{\ell}}|
+\end{equation}
 
-Prior:
+Note that both $\epsilon_{0}$ and $\epsilon_{\ell}$are complex numbers.So
+$|\frac{\partial\epsilon_{0}}{\partial\epsilon_{\ell}}|$ is the Jacobian
+determinant term.Here the prior distribtuion we use for $\vec{g}$
+is a 2Dflat distribution in the region $|g|<1$.Therefore $prior(\vec{g)}=\begin{cases}
+1 & |\vec{g}|<1\\
+0 & |\vec{g}|>1
+\end{cases}$
 
-Prior($\vec{g})=1$ $|\vec{g}|<1$ else Prior(g)=0
+The prior of $\alpha$ some how depends on the model we choose for
+intrinsic ellipticity distribution .When we use the step function
+model for P($\epsilon_{0}$),we find that we need to use a prior on
+$\alpha$ .
+\begin{equation}
+Prior(\vec{\alpha}|\xi)=exp(-\xi\sum(\alpha_{i}-\alpha_{i-1})^{2})
+\end{equation}
 
-Prior($\alpha)=exp(-\underset{i}{\xi\sum}(\alpha_{i}-\alpha_{i-1})^{2})$
+Given the likehood functions and priors we can also calculated the
+marginalized likelihood function.
+\begin{equation}
+p(\epsilon_{\ell}|\vec{g})=\int p(\epsilon_{\ell}|\vec{g},\alpha)p(\alpha|\vec{g})d\alpha
+\end{equation}
 
-Marginalized likelihood:
+Since $p(\alpha)$ does not explicitly depends on $\vec{g}$ .$p(\alpha|\vec{g})$is
+just $Prior(\vec{\alpha}|\xi)$.Therefore,we have marginalized likehood
+\begin{equation}
+p(\epsilon_{\ell}|\vec{g})=\int p(\epsilon_{\ell}|\vec{g},\alpha)Prior(\vec{\alpha}|\xi)d\alpha
+\end{equation}
 
-p($\epsilon_{\ell}|\vec{g})=\int p(\epsilon_{\ell}|\vec{g},\alpha)p(\alpha|\vec{g})d\alpha$
-
-with $p(\alpha|\vec{g})=Prior(\alpha)$
-
-$p(\epsilon_{l}|\vec{g})=\int p(\epsilon_{\ell}|\vec{g},\alpha)*Prior(\alpha)d\alpha$
-
-$p(\epsilon_{\ell}|g_{1})=\underset{|g|<1}{\int}p(\epsilon_{\ell}|\vec{g})dg_{2}$
 \end{document}

### 2013-03-13 docs/ms.tex
no psfig
Update ms.tex

@@
 % Packages:
-\input psfig.sty
+% \input psfig.sty
 \usepackage{xspace}
@@
 
-\section{XXX}
+\section{method}
 \label{sec:XXX}
+
+\subsection{Likelihood Functions}
+If we know the ellipticity distribution of unlensed galaxies based
+on some parasmeters $\alpha$,the likelihood of reduced shear $g$
+and parameter $\alpha$ is like:
+
+\begin{equation}
+L(\vec{g},\alpha|\epsilon_{\ell})=p(\epsilon_{\ell}|\vec{g},\alpha)=P(\epsilon_{0}(\vec{g})|\alpha)*|\frac{\partial\epsilon_{0}}{\partial\epsilon_{\ell}}|
+\end{equation}
+
+Note that both $\epsilon_{0}$ and $\epsilon_{\ell}$are complex numbers.So
+$|\frac{\partial\epsilon_{0}}{\partial\epsilon_{\ell}}|$ is the Jacobian
+determinant term.Here the prior distribtuion we use for $\vec{g}$
+is a 2Dflat distribution in the region $|g|<1$.Therefore $prior(\vec{g)}=\begin{cases}
+1 & |\vec{g}|<1\\
+0 & |\vec{g}|>1
+\end{cases}$
+
+The prior of $\alpha$ some how depends on the model we choose for
+intrinsic ellipticity distribution .When we use the step function
+model for P($\epsilon_{0}$),we find that we need to use a prior on
+$\alpha$ .
+\begin{equation}
+Prior(\vec{\alpha}|\xi)=exp(-\xi\sum(\alpha_{i}-\alpha_{i-1})^{2})
+\end{equation}
+
+Given the likehood functions and priors we can also calculated the
+marginalized likelihood function.
+\begin{equation}
+p(\epsilon_{\ell}|\vec{g})=\int p(\epsilon_{\ell}|\vec{g},\alpha)p(\alpha|\vec{g})d\alpha
+\end{equation}
+
+Since $p(\alpha)$ does not explicitly depends on $\vec{g}$ .$p(\alpha|\vec{g})$is
+just $Prior(\vec{\alpha}|\xi)$.Therefore,we have marginalized likehood
+\begin{equation}
+p(\epsilon_{\ell}|\vec{g})=\int p(\epsilon_{\ell}|\vec{g},\alpha)Prior(\vec{\alpha}|\xi)d\alpha
+\end{equation}
+
+\subsection{model for P($\epsilon_{0}$)}
+Two flexible models are tested for P($\epsilon_{0}$)
+One is Beta function model and one is step function model.
+While using step function model we use a prior regularzation on $\alpha$ 
+\begin{equation}
+Prior(\vec{\alpha}|\xi)=exp(-\xi\sum(\alpha_{i}-\alpha_{i-1})^{2})
+\end{equation}
+
+\subsection{MCMC Sampler}
+
+While making the posterior samples we choose to use the classical Gibbs sampler.
 
@@
 
-\section{XXX}
+\section{Result}
 \label{sec:XXX}
+
+\subsection{Posterior samples}
+We show the posterior samples of both g and $\alpha$ ,for both beta function and step function model.
+\subsection{Bias Test}
+We test the systematical bias of our estimator.
+We plot $g_{1}-g_{1}^{true}$ VS $g_{1}^{true}$ ,and put on an error bar which equals standard deviation of 
+marginalized likehood functon $p(Data|g_{1})$ ,and use a linear fit to determin the m,c value and their standard 
+deviations.
+
+\subsection{Accuracy Test}
+We compare the mean square error of our estimator with average and the estimator that could be constructed if the true unlensed
+ellipticity distribution were known.
+We show how the mean square error varies with number of galaxies ,number of patches and so on.
+
+\subsection{Accuracy Test}
+We show some example how our method works when there is an Gaussian noise added on the observed $\epsilon$
+
+\subsection{prefactor $\xi$}
+Discuss about how $\xi$ is tuned ,the danger if $\xi$ is set to be too large or too small.
 
@@
 
-\section{XXX}
+\section{Discussion}
 \label{sec:XXX}

### 2013-03-13 docs/ms.tex
Update ms.tex

@@
 \subsection{Bias Test}
-We test the systematical bias of our estimator.
+We test the systematical bias of our estimator.(Here the estimator is the max-marginalized likelihood estimator?)
 We plot $g_{1}-g_{1}^{true}$ VS $g_{1}^{true}$ ,and put on an error bar which equals standard deviation of 
@@
 
-\subsection{Accuracy Test}
+\subsection{Measurement Error}
 We show some example how our method works when there is an Gaussian noise added on the observed $\epsilon$

### 2013-03-14 docs/ms.tex
Update ms.tex

@@
 
-\subsection{Likelihood Functions}
-If we know the ellipticity distribution of unlensed galaxies based
-on some parasmeters $\alpha$,the likelihood of reduced shear $g$
-and parameter $\alpha$ is like:
+\subsection{Likelihood Function}
+
+We assume Lensed galaxy ellipticity $\epsilon_{\ell}$ is related
+to the intrinsic galaxy ellipticity $\epsilon_{0}$ in the weak lensing
+regime via
+\begin{equation}
+\epsilon_{\ell}=\frac{\epsilon_{0}+g}{1+g^{*}\epsilon_{0}}
+\end{equation}
+
+and it's inverse formula 
+\begin{equation}
+\epsilon_{0}=\frac{\epsilon_{\ell}-g}{1-g^{*}\epsilon_{\ell}}
+\end{equation}
+from Schramm \& Kayser (1995), Seitz \& Schneider (1997), where $\epsilon$
+is represented as a complex variable and g, $g^{*}$ are the reduced
+shear and its complex conjugate, respectively. $\epsilon$ is defined
+in terms of the major and minor axes and orientation a, b, $\phi$,
+respectively, as e = (a − b)/(a + b) exp(2i$\phi$). Due to the isotropic
+of Universe ,we expect $\phi$has a uniform distribution from 0 to
+$\pi$.Then we can expect 
+\begin{equation}
+<\epsilon_{\ell}>=g
+\end{equation}
+
+So $<\epsilon_{\ell}>$ can be adopted as an estimator of g.
+
+However in our hierachical Bayesian approach we are able to obtain
+the posterior distribution of g ,starting from the same formulas.
+
+Suppose we know the ellipticity distribution of unlensed galaxies
+based on some parasmeters $\alpha$,the likelihood of reduced shear
+$g$ and parameter $\alpha$ is like:
 
@@
 $|\frac{\partial\epsilon_{0}}{\partial\epsilon_{\ell}}|$ is the Jacobian
-determinant term.Here the prior distribtuion we use for $\vec{g}$
-is a 2Dflat distribution in the region $|g|<1$.Therefore $prior(\vec{g)}=\begin{cases}
+determinant term,which can be calculated numerically from formula
+(5).
+
+If there is measurement error on $\epsilon_{ob}$,we will have 
+\begin{equation}
+L(\vec{g},\alpha|\epsilon_{ob})=p(\epsilon_{ob}|\vec{g},\alpha)=\int f(\epsilon_{ob}|\epsilon_{\ell})p(\epsilon_{\ell}|\vec{g},\alpha)
+\end{equation}
+Here the prior distribtuion we use for $\vec{g}$ is a 2Dflat distribution
+in the region $|g|<1$.Therefore $prior(\vec{g)}=\begin{cases}
 1 & |\vec{g}|<1\\
@@
 
-\subsection{model for P($\epsilon_{0}$)}
-Two flexible models are tested for P($\epsilon_{0}$)
-One is Beta function model and one is step function model.
-While using step function model we use a prior regularzation on $\alpha$ 
+One thing to note is that the likelihood of g in patch i only depends
+on the shape parameters but not dependent to g in other patch.Therefore,the
+marginalized likelihood of shape parameters has an equation like:
+
+\begin{equation}
+\ell(\alpha|data)=\prod_{i}\ell_{i}(\alpha|data_{i})
+\end{equation}
+
+$\ell_{i}(\alpha|data_{i})$ is the marginalized likelihood function
+calculated with data in the ith patch.From this formula we can see
+how better estimation of $\alpha$ will be obtained if we infer more
+sky patches simultaneously.
+
+\subsection{Model for Prior($\epsilon_{0}$)}
+
+The correctness of posterior distribution of g depends on the intrinsic
+ellipticity distribution P($\epsilon_{0}|\alpha$). Due to the limitation
+of human's knowledge we are not able to give an analytical form of
+$P(\epsilon_{0}|\alpha)$.Therefore we proposed an exceedingly flexible
+model for $P(\epsilon_{0}|\alpha)$,which does not requires further
+assumption on $P(\epsilon_{0}|\alpha)$.
+
+We divide the 2-D space r$\in$(0,1) into N bins .The probability
+of each bin is $p_{i}=e^{\alpha_{i}}$ .$\overrightarrow{\alpha}$
+is a N-D parameter vector to be infered,simultaneously with g.
+
+From practice we find that a prior smooth regularzation on $\alpha$
+is needed to obtain a good estimation on shear g.
+
+The prior distribution we used on $\alpha$ is : 
 \begin{equation}
@@
 
-\subsection{MCMC Sampler}
+Here $\xi$ is a prefactor need to be tuned .
 
-While making the posterior samples we choose to use the classical Gibbs sampler.
+Meanwhile,in order to show the correctness of our method ,we also
+set up a simulation in which we know the true $P(|\epsilon_{0}||\alpha)$
+is a Beta distribution ,and thus $\alpha$ is the 2-D parameter (p,q)
+of the Beta distribution.We will show the posterior samples using
+both of these two methods in next section. Note that for either model
+we assume P($\epsilon_{0}$) is isotropic.
+
+\subsection{Gibbs Sampler}
+
+While making the posterior samples we choose to use the classical
+Gibbs sampler.
+
+In Gibbs sampling ,samples of variable $x_{j}$ is made from the conditional
+probability distribution:$p(x_{j}^{(i)}|x_{1}^{(i)},....,x_{j-1}^{(i)},x_{j+1}^{(i-1)}...,x_{n}^{(i-1)})$
+
+While the conditional distribution of one variable given all others
+is just proportional to the joint distribution
+
+\begin{equation}
+p(x_{j}|x_{1},....,x_{j-1},x_{j+1}...,x_{n})\varpropto p(x_{1},.....,x_{n})
+\end{equation}
+
+One thing to note is that the conditional probability of g in ith
+patch only explicitly depends on $\alpha$ ,but not g in other patches.Therefore
+with $\alpha$ fixed ,the posterior distribution of reduced shear
+in ith patch are independent from each other .
+\begin{equation}
+p(\vec{g}_{1}....\vec{g}_{n}|\alpha,Data)=p(\vec{g}_{1}|\alpha,Data_{1})....p(\vec{g}_{n}|\alpha,Data_{n})
+\end{equation}
+Therefore sampling reduced shear g from conditional distribution can
+be reduced to 2D sampling problem,which can be done very quickly.
+
+The total time needed to sample $g$ and $\alpha$ of 64 sky patches
+with 8 galaxies in each patch will only be approximitly 25s on a 2
+GHz CPU.
+
+\subsection{Simulations}
+
+The procedure of our simulation is that ,first we generated N{*}NP
+unlensed galaxies' elliprticity from the ``true'' $P(\epsilon_{0})$,and
+asign these galaxies into NP patches equally.So each patch has N galaxies.Second
+we generate NP true reduced shears ,and asign them to each patch,and
+then shear the unlensed galaxies using formula (4) .
+
+Finally we can put on some noise on $\epsilon_{\ell}$ to get the
+observed ellipticity $\epsilon_{ob}$. For simplicity we've only considered
+the situation when P($\epsilon_{ob}|\epsilon_{\ell})$ is a 2D Gaussian.
+
+Use Gibbs sampler and $P(\epsilon_{0}|\alpha)$ mentioned previously,we
+are to sample the posterior distribution of g and $\alpha$ simultaneously
+and effectively.
 

### 2013-03-14 docs/ms.tex
Update ms.tex

@@
 in terms of the major and minor axes and orientation a, b, $\phi$,
-respectively, as e = (a − b)/(a + b) exp(2i$\phi$). Due to the isotropic
-of Universe ,we expect $\phi$has a uniform distribution from 0 to
+respectively, as $\epsilon$ = (a − b)/(a + b) exp(2i$\phi$). Due to the isotropic
+of Universe ,we expect $\phi$ has a uniform distribution from 0 to
 $\pi$.Then we can expect 
@@
 
-So $<\epsilon_{\ell}>$ can be adopted as an estimator of g.
+Therefore $<\epsilon_{\ell}>$ can be adopted as an estimator of g.
 
 However in our hierachical Bayesian approach we are able to obtain
-the posterior distribution of g ,starting from the same formulas.
+the posterior distribution of g ,based on the assumption  $\phi$ has a uniform distribution and galaxies in different
+sky patches have the same intrinsic shape distribution.
 
 Suppose we know the ellipticity distribution of unlensed galaxies
-based on some parasmeters $\alpha$,the likelihood of reduced shear
-$g$ and parameter $\alpha$ is like:
+based on some parasmeters $\alpha$,then we can write the likelihood of reduced shear and $\alpha$:
 
@@
 how better estimation of $\alpha$ will be obtained if we infer more
-sky patches simultaneously.
+sky patches simultaneously. With better knowledge on $\alpha$ we can in turn have better estimates on reduced shear g.
 

### 2013-03-14 docs/ms.tex
Update ms.tex

@@
 
-\subsection{Likelihood Function}
+\subsection{Likelihood Functions}
 
@@
 in terms of the major and minor axes and orientation a, b, $\phi$,
-respectively, as $\epsilon$ = (a − b)/(a + b) exp(2i$\phi$). Due to the isotropic
+respectively, as $\epsilon$ = (a − b)/(a + b) exp(2i$\phi$). Due to the isotropicity
 of Universe ,we expect $\phi$ has a uniform distribution from 0 to
@@
 \end{equation}
-Here the prior distribtuion we use for $\vec{g}$ is a 2Dflat distribution
+Here the prior distribtuion we use for $\vec{g}$ is a 2D flat distribution
 in the region $|g|<1$.Therefore $prior(\vec{g)}=\begin{cases}
@@
 intrinsic ellipticity distribution .When we use the step function
-model for P($\epsilon_{0}$),we find that we need to use a prior on
-$\alpha$ .
+model for P($\epsilon_{0}$),which we'll decribe latter.We find that
+we need to use a prior on $\alpha$ .
 \begin{equation}
@@
 how better estimation of $\alpha$ will be obtained if we infer more
-sky patches simultaneously. With better knowledge on $\alpha$ we can in turn have better estimates on reduced shear g.
+sky patches simultaneously. With better knowledge on $\alpha$ we can
+in turn have better estimates on reduced shear g.
 
@@
 
-While making the posterior samples we choose to use the classical
+While making the posterior samples $p(\g,\alpha|Data) we choose to use the classical
 Gibbs sampler.

### 2013-03-16 docs/ms.tex
Update ms.tex

@@
 % History of shear estimation, and treatment of Pr(e).
+
+why is weak lensing important?
+Weak gravitational lensing has become the most potential tool for constraining the cosmological parameters that describe the dark universe (Albrecht et al. 2006; Peacock & Schneider 2006). 
+One application of Weak gravitational lensing is that it can be used to measure the mass profile of single galaxy,galaxy groups and clusters or large scales.
+
+Cosmic shear is the mild distortion of distant galaxy images due to the
+bending of light by intervening matter.
+
+Cosmic shear provides one of the most promising methods for constraining the nature of
+dark energy (Albrecht et al. 2006; Peacock&Schneider 2006).
+
+What is the big problems of weak lensing analysis:
+The magnitude of shear in Weak lensing is typically ~0.01 it's usually 10 times smaller than the intrinsic shape 
+noise,it's also smaller than the distortion caused be PSF effect which usually has ~0.05 level.
+We have little information about the intrinsic shape distribution futher than it's istropic,the direct observation we can make is mere the distribution
+of lensed ellipticity.And there is an analytical fine model to describe intrinsic shape distribution.
+
+how do we break it down to e measurement, and g inference, and cosmological parameter estimation?
+
+The measurement of galaxy shapes from images is first step  of weak gravitational lensing analysis , since the observed ellipticities of distant galaxies are
+Used to infer the shear map , which quantify how shape of galaxies are distorted.
+The second step is to infer 
+Finally,we can recover the projected mass profile of galaxies or dark energy by it’s shear map.
+
+what are we studying in this paper (ie, not the whole thing, just going from es to gs).
+In this paper we merely consider the inference of shear map from galaxies shape.
+We set up an simple toy model in which we have the observed ellipticity as data,and the only measurement error we consider 
+is a Gaussian noise add on the true lensed ellipticity.We suppose there is a uniform shear acting on one sky patch,
+
+What approach will we take and WHY.
+
+Our approach is to use an exceedingly model for intrinsic shape distribution,and use MCMC sampling to 
+gives out the whole likelihood function of shear in many sky patches and their common shape parameters simultaneously.
+
+We can use the credit interval of posterior samples as the uncertainty of estimate
+, which can be used as statistical weights.It tells us how much information about shear can we obtain from observed data.
+
+By doing this we use the information that galaxies in different sky patch should have the same intrinsic shape distribution.
 
@@
 
-While making the posterior samples $p(\g,\alpha|Data) we choose to use the classical
+While making the posterior samples $p(\g,\alpha|Data)$ we choose to use the classical
 Gibbs sampler.

### 2013-03-16 docs/ms.tex
Update ms.tex

@@
 \begin{equation}
-L(\vec{g},\alpha|\epsilon_{\ell})=p(\epsilon_{\ell}|\vec{g},\alpha)=P(\epsilon_{0}(\vec{g})|\alpha)*|\frac{\partial\epsilon_{0}}{\partial\epsilon_{\ell}}|
+p(\epsilon_{\ell}|\vec{g},\alpha)=p(\epsilon_{0}(\vec{g})|\alpha)*|\frac{\partial\epsilon_{0}}\,{\partial\epsilon_{\ell}}|
 \end{equation}
@@
 \begin{equation}
-L(\vec{g},\alpha|\epsilon_{ob})=p(\epsilon_{ob}|\vec{g},\alpha)=\int f(\epsilon_{ob}|\epsilon_{\ell})p(\epsilon_{\ell}|\vec{g},\alpha)
+p(\epsilon_{ob}|\vec{g},\alpha)=\int f(\epsilon_{ob}|\epsilon_{\ell})\,p(\epsilon_{\ell}|\vec{g},\alpha)
 \end{equation}
 Here the prior distribtuion we use for $\vec{g}$ is a 2D flat distribution
-in the region $|g|<1$.Therefore $prior(\vec{g)}=\begin{cases}
+in the region $|g|<1$.Therefore $p(\vec{g)}=\begin{cases}
 1 & |\vec{g}|<1\\
@@
 \begin{equation}
-Prior(\vec{\alpha}|\xi)=exp(-\xi\sum(\alpha_{i}-\alpha_{i-1})^{2})
+p(\vec{\alpha}|\xi)=exp(-\xi\sum(\alpha_{i}-\alpha_{i-1})^{2})
 \end{equation}
@@
 Since $p(\alpha)$ does not explicitly depends on $\vec{g}$ .$p(\alpha|\vec{g})$is
-just $Prior(\vec{\alpha}|\xi)$.Therefore,we have marginalized likehood
+just the pror distribution $p(\vec{\alpha}|\xi)$.Therefore,we have marginalized likehood
 \begin{equation}
-p(\epsilon_{\ell}|\vec{g})=\int p(\epsilon_{\ell}|\vec{g},\alpha)Prior(\vec{\alpha}|\xi)d\alpha
+p(\epsilon_{\ell}|\vec{g})=\int p(\epsilon_{\ell}|\vec{g},\alpha)\,p(\vec{\alpha}|\xi)d\alpha
 \end{equation}
+Given that marginalized likelihood function ,in principle we could optimize it  and gives out a max-likelihood estimator 
+for \vec{g} in different patches simultaneously.
 

### 2013-03-16 docs/ms.tex
Update ms.tex

@@
 Used to infer the shear map , which quantify how shape of galaxies are distorted.
-The second step is to infer 
+The second step is to infer the shear map from galaxies ellipticity.Usually the estimate of g  involve simple or weighted
+means of measured galaxy ellipticities.
 Finally,we can recover the projected mass profile of galaxies or dark energy by it’s shear map.

### 2013-03-19 docs/ms.tex
Update ms.tex

@@
 
+How it's related to galaxy -galaxy lensing
+In galaxy - galaxy lensing what people usually do is stack many lensing signals together and get the "average"
+shear map,and then infers the mean mass profile of galaxy or galaxy cluster.
+However with HB method we can calculate the posterior distribution of mass profile of each lens and propagate all the uncertainty
+from to the posterior distributions.
 This paper is organized as follows...

### 2013-03-29 docs/ms.tex
Update ms.tex

--- 2013-03-16 docs/ms.tex
@@
 
-why is weak lensing important?
 Weak gravitational lensing has become the most potential tool for constraining the cosmological parameters that describe the dark universe (Albrecht et al. 2006; Peacock & Schneider 2006). 
 One application of Weak gravitational lensing is that it can be used to measure the mass profile of single galaxy,galaxy groups and clusters or large scales.
+Cosmic shear is the mild distortion of distant galaxy images due to the bending of light by intervening matter.
+Cosmic shear provides one of the most promising methods for constraining the nature of dark energy (Albrecht et al. 2006; Peacock&Schneider 2006). 
+In galaxy--galaxy weaklensing  ,tangential shear distortions of background galaxies around foreground
+galaxies, allows direct measurement of the galaxy–DM correlation
 
-Cosmic shear is the mild distortion of distant galaxy images due to the
-bending of light by intervening matter.
+The distortion in Weak lensing is typically ~ 0.01,or ~0.001 for galaxy-galaxy lensing  it's usually 10 times smaller than the intrinsic shape 
+noise,it's also smaller than the distortion caused be PSF effect which usually has ~0.05 level.
+The main source of uncertainty of tangential shear comes from the intrinsic shape "noise" . We know little knowledge about 
+the distribution of intrinsic ellipticity,exception the assumption that the orientational angle should be isotropic.
+With this assumption,we can use the average of galaxies' ellipticity as an estimator of tangential shear.--However by 
+doing this we loose some information about how the ellipticity are distributed. Simple average point estimator can't 
+use the other reasonable assumption about intrinsic shape distribution --galaxies in different sky patches should have 
+the same shape distibution--which is the result of homogeneous Universe.
 
-Cosmic shear provides one of the most promising methods for constraining the nature of
-dark energy (Albrecht et al. 2006; Peacock&Schneider 2006).
+The typical procedure of weak lensing analysis usually include ellipticity measurement,shear inference,mass profile reconstruction.
+The measurement of galaxy shapes  is  the first step  of weak gravitational lensing analysis,since it's the direct observable
+that relates with tangential shear.However in this paper we only concern about how to infere shear from galaxy ellipticity
+in a hierachical way.Therefore in our simulation we set up an simple toy model in which we have the observed ellipticity as data,and the only measurement error we consider 
+is a Gaussian noise add on the true lensed ellipticity.We suppose there is a uniform shear acting on one all the galaxies in sky patch,
 
-What is the big problems of weak lensing analysis:
-The magnitude of shear in Weak lensing is typically ~0.01 it's usually 10 times smaller than the intrinsic shape 
-noise,it's also smaller than the distortion caused be PSF effect which usually has ~0.05 level.
-We have little information about the intrinsic shape distribution futher than it's istropic,the direct observation we can make is mere the distribution
-of lensed ellipticity.And there is an analytical fine model to describe intrinsic shape distribution.
+Our approach is to use an exceedingly flexiable model for intrinsic shape distribution,and assumes all the galaxies in different
+patches abeys such an distribution.Then we can calculate the joint likelihood of both shpape distribution parameters and shear in differ
+With a classical Gibbs MCMC sampler we are able to sample their posteior distriibution.After marginalizing the shape parameters, we can
+obtain the posterior distribution of shear,which we are interested in.
 
-how do we break it down to e measurement, and g inference, and cosmological parameter estimation?
+In galaxy--galaxy lensing ,since the distortion is so weak,what people usually do is stack many lensing signals together and get the "average"
+shear map,and then infers the mean mass profile of galaxy or galaxy cluster.
+However with HB method we can avoid this brute averaging ,instead we can get the posterior distribution of mass profile for 
+each lensing system - even though it has very arge uncertainty- we can calculate the statistical property like galaxy-mass
+correlation function via this posterior distribution.
 
-The measurement of galaxy shapes from images is first step  of weak gravitational lensing analysis , since the observed ellipticities of distant galaxies are
-Used to infer the shear map , which quantify how shape of galaxies are distorted.
-The second step is to infer 
-Finally,we can recover the projected mass profile of galaxies or dark energy by it’s shear map.
-
-what are we studying in this paper (ie, not the whole thing, just going from es to gs).
-In this paper we merely consider the inference of shear map from galaxies shape.
-We set up an simple toy model in which we have the observed ellipticity as data,and the only measurement error we consider 
-is a Gaussian noise add on the true lensed ellipticity.We suppose there is a uniform shear acting on one sky patch,
-
-What approach will we take and WHY.
-
-Our approach is to use an exceedingly model for intrinsic shape distribution,and use MCMC sampling to 
-gives out the whole likelihood function of shear in many sky patches and their common shape parameters simultaneously.
-
-We can use the credit interval of posterior samples as the uncertainty of estimate
-, which can be used as statistical weights.It tells us how much information about shear can we obtain from observed data.
-
-By doing this we use the information that galaxies in different sky patch should have the same intrinsic shape distribution.
-
-This paper is organized as follows...
+This paper is orgnized as following: In section 2 we introduce the weak lensing formulas and the likelihood function .Then we 
+describe two flexible models for the intrinsic shape distribution. In section 3 we show the result of the MCMC sampling
+,and check the bias and variance of sample mean and compare with that of the simple average method.In Section 4 we discussed
 

### 2013-03-29 docs/ms.tex
Update ms.tex

@@
 that relates with tangential shear.However in this paper we only concern about how to infere shear from galaxy ellipticity
-in a hierachical way.Therefore in our simulation we set up an simple toy model in which we have the observed ellipticity as data,and the only measurement error we consider 
+in a hierachical way.Therefore in our simulation we set up a simple toy model in which we have the observed ellipticity as data,and the only measurement error we consider 
 is a Gaussian noise add on the true lensed ellipticity.We suppose there is a uniform shear acting on one all the galaxies in sky patch,

### 2013-03-29 docs/ms.tex
Update ms.tex

@@
 
-Our approach is to use an exceedingly flexiable model for intrinsic shape distribution,and assumes all the galaxies in different
-patches abeys such an distribution.Then we can calculate the joint likelihood of both shpape distribution parameters and shear in differ
+Our approach is to use an exceedingly flexible model for intrinsic shape distribution,and assumes all the galaxies in different
+patches abeys such a distribution.Then we can calculate the joint likelihood of  shpape distribution parameters and shear in differ
 With a classical Gibbs MCMC sampler we are able to sample their posteior distriibution.After marginalizing the shape parameters, we can

### 2013-03-29 docs/ms.tex
Update ms.tex

@@
 With this assumption,we can use the average of galaxies' ellipticity as an estimator of tangential shear.--However by 
-doing this we loose some information about how the ellipticity are distributed. Simple average point estimator can't 
+doing this we lose some information about how the ellipticity are distributed. Simple average point estimator can't 
 use the other reasonable assumption about intrinsic shape distribution --galaxies in different sky patches should have 

### 2013-03-29 docs/ms.tex
Update ms.tex

@@
 
-Weak gravitational lensing has become the most potential tool for constraining the cosmological parameters that describe the dark universe (Albrecht et al. 2006; Peacock & Schneider 2006). 
+Weak gravitational lensing has become the most potential tool to explore the dark universe. 
 One application of Weak gravitational lensing is that it can be used to measure the mass profile of single galaxy,galaxy groups and clusters or large scales.
-Cosmic shear is the mild distortion of distant galaxy images due to the bending of light by intervening matter.
-Cosmic shear provides one of the most promising methods for constraining the nature of dark energy (Albrecht et al. 2006; Peacock&Schneider 2006). 
-In galaxy--galaxy weaklensing  ,tangential shear distortions of background galaxies around foreground
-galaxies, allows direct measurement of the galaxy–DM correlation
+Cosmic shear is the mild distortion of distant galaxy images due to the bending of light by intervening matter.It provides one of the most promising methods for constraining the nature of dark energy (Albrecht et al.
+2006; Peacock&Schneider 2006).
+While in galaxy--galaxy weaklensing ,tangential shear distortions of background galaxies around foreground galaxies, allows direct measurement of the galaxy–DM correlation
 

### 2013-03-29 docs/ms.tex
Update ms.tex

@@
 
-The distortion in Weak lensing is typically ~ 0.01,or ~0.001 for galaxy-galaxy lensing  it's usually 10 times smaller than the intrinsic shape 
+The distortion in Weak lensing is typically ~ 0.01,or ~0.001 for galaxy-galaxy lensing  it's usually more than 10 times smaller than the intrinsic shape 
 noise,it's also smaller than the distortion caused be PSF effect which usually has ~0.05 level.

### 2013-03-29 docs/ms.tex
Update ms.tex

@@
 However with HB method we can avoid this brute averaging ,instead we can get the posterior distribution of mass profile for 
-each lensing system - even though it has very arge uncertainty- we can calculate the statistical property like galaxy-mass
+each lensing system - even though it has very large uncertainty- we can calculate the statistical property like galaxy-mass
 correlation function via this posterior distribution.

### 2013-03-30 docs/ms.tex
Update ms.tex

@@
 patches abeys such a distribution.Then we can calculate the joint likelihood of  shpape distribution parameters and shear in differ
-With a classical Gibbs MCMC sampler we are able to sample their posteior distriibution.After marginalizing the shape parameters, we can
-obtain the posterior distribution of shear,which we are interested in.
+shy patches.With a classical Gibbs MCMC sampler we are able to sample their posteior distriibution.After marginalizing the shape parameters, we can
+obtain the posterior distribution of shear,which we are interested in.This approach allows us use the information maximumly
+without introducing in any wrong assumptions on intrinsic shape distribution.
 

### 2013-03-30 docs/ms.tex
Update ms.tex

@@
 
-In summary, ...
+In summary,We have presented a conceptually simple method for estimating tangential shear ,
+with carefully calculated uncertainty estimates. This method is intrinsically cope with high noise levels on the input data and naturally
+allows bad fit to be identified from the residuals map.
+We have proposed an exceeding flexible model for intrinsic shape distribution allows us to obtain the correct posterior distributions,
+while avoiding making unsupported assumptions.
 

### 2013-03-30 docs/ms.tex
Update ms.tex

@@
 We have proposed an exceeding flexible model for intrinsic shape distribution allows us to obtain the correct posterior distributions,
-while avoiding making unsupported assumptions.
+while avoiding making unsupported assumptions.The Gibbs sampler allows us to sample the posterior distribution of shear in 
+large number of sky patches simultaneously and efficiently.
 

### 2013-03-30 docs/ms.tex
Update ms.tex

@@
 \label{sec:XXX}
+In weak lensing survey,one way to btain high S/N ratio is to stack large number of lensing signal together,and 
+calculate the mean shear map of all these lensing systems.However simply to stack allthe lensing signals would not be the
+optimal way because of the amount of information we can obtain from each lensing system can be very different.
+The Bayesian inference approach we proposed allows a natural way to optimally include all the data.What we need to do
+is to propogate the whole likelihood of each lensing system while calculating the statistical properties of various lensing
+systems.
 

### 2013-03-30 docs/ms.tex
Update ms.tex

@@
 optimal way because of the amount of information we can obtain from each lensing system can be very different.
-The Bayesian inference approach we proposed allows a natural way to optimally include all the data.What we need to do
-is to propogate the whole likelihood of each lensing system while calculating the statistical properties of various lensing
-systems.
+The Bayesian inference approach we proposed allows a natural way to optimally include all the data.In stead of stacking what we need to do
+is to propogate the likelihood of the shear map of each lensing system. The statistical property of all the lensing systems can be 
+calculated from these likelihoods.
 

### 2013-03-30 docs/ms.tex
Update ms.tex

--- 2013-03-30 docs/ms.tex
@@
 \label{sec:XXX}
+In weak lensing survey,one way to obtain high S/N ratio is to stack large number of lensing signal together,and 
+calculate the mean shear map of all these lensing systems.However simply to stack allthe lensing signals would not be the
+optimal way because of the amount of information we can obtain from each lensing system can be very different.
+The Bayesian inference approach we proposed allows a natural way to optimally include all the data.In stead of stacking what we need to do
+is to propogate the likelihood of the shear map of each lensing system. The statistical property of all the lensing systems
+like the galaxy-mass ,shear-shar correlation function ,in principle can be calculated from these likelihood functions.
 

### 2013-03-31 docs/ms.tex
Update ms.tex

@@
 In weak lensing survey,one way to obtain high S/N ratio is to stack large number of lensing signal together,and 
-calculate the mean shear map of all these lensing systems.However simply to stack allthe lensing signals would not be the
+calculate the mean shear map of all these lensing systems.However simply to stack all the lensing signals would not be the
 optimal way because of the amount of information we can obtain from each lensing system can be very different.

### 2013-04-02 docs/ms.tex
Update ms.tex

@@
 \section{Introduction}
+
 \label{sec:intro}
 
-\flag{Yike}{Plan the sections of your paper, and write very brief notes on
-what you want to say in each of them. You will find it helpful to divide
-them into sub-sections, and even paragraphs. You may also want to put in
-placeholder figures and tables; if you do, make sure to write the captions of
-them. The itemized conclusions should be partial answers to a corresponding
-list of questions in the introduction. You can write these now, as incomplete
-statements: when you know what your findings are, you can complete them.}
+\flag{Yike}{Plan the sections of your paper, and write very brief
+notes on what you want to say in each of them. You will find it helpful
+to divide them into sub-sections, and even paragraphs. You may also
+want to put in placeholder figures and tables; if you do, make sure
+to write the captions of them. The itemized conclusions should be
+partial answers to a corresponding list of questions in the introduction.
+You can write these now, as incomplete statements: when you know what
+your findings are, you can complete them.}
 
@@
 
-Weak gravitational lensing has become the most potential tool to explore the dark universe. 
-One application of Weak gravitational lensing is that it can be used to measure the mass profile of single galaxy,galaxy groups and clusters or large scales.
-Cosmic shear is the mild distortion of distant galaxy images due to the bending of light by intervening matter.It provides one of the most promising methods for constraining the nature of dark energy (Albrecht et al.
-2006; Peacock&Schneider 2006).
-While in galaxy--galaxy weaklensing ,tangential shear distortions of background galaxies around foreground galaxies, allows direct measurement of the galaxy–DM correlation
+Weak gravitational lensing has become the most potential tool to explore
+the dark universe. One application of Weak gravitational lensing is
+that it can be used to measure the mass profile of single galaxy,galaxy
+groups and clusters or large scales. Cosmic shear is the mild distortion
+of distant galaxy images due to the bending of light by intervening
+matter.It provides one of the most promising methods for constraining
+the nature of dark energy (Albrecht et al. 2006; Peacock\&Schneider
+2006). While in galaxy--galaxy weaklensing ,tangential shear distortions
+of background galaxies around foreground galaxies, allows direct measurement
+of the galaxy-DM correlation
 
-The distortion in Weak lensing is typically ~ 0.01,or ~0.001 for galaxy-galaxy lensing  it's usually more than 10 times smaller than the intrinsic shape 
-noise,it's also smaller than the distortion caused be PSF effect which usually has ~0.05 level.
-The main source of uncertainty of tangential shear comes from the intrinsic shape "noise" . We know little knowledge about 
-the distribution of intrinsic ellipticity,exception the assumption that the orientational angle should be isotropic.
-With this assumption,we can use the average of galaxies' ellipticity as an estimator of tangential shear.--However by 
-doing this we lose some information about how the ellipticity are distributed. Simple average point estimator can't 
-use the other reasonable assumption about intrinsic shape distribution --galaxies in different sky patches should have 
+The distortion in Weak lensing is typically ~ 0.01,or ~0.001 for
+galaxy-galaxy lensing it's usually more than 10 times smaller than
+the intrinsic shape noise,it's also smaller than the distortion caused
+be PSF effect which usually has ~0.05 level. For shear measurement
+the main source of uncertainty comes from the intrinsic shape noise
+. We know little knowledge about the distribution of intrinsic ellipticity,exception
+the assumption that the orientational angle should be isotropic. With
+this assumption,we can use the average of galaxies' ellipticity as
+an estimator of tangential shear.--However by doing this we lose some
+information about how the ellipticity are distributed. Simple average
+point estimator can't use the other reasonable assumption about intrinsic
+shape distribution --galaxies in different sky patches should have
 the same shape distibution--which is the result of homogeneous Universe.
 
-The typical procedure of weak lensing analysis usually include ellipticity measurement,shear inference,mass profile reconstruction.
-The measurement of galaxy shapes  is  the first step  of weak gravitational lensing analysis,since it's the direct observable
-that relates with tangential shear.However in this paper we only concern about how to infere shear from galaxy ellipticity
-in a hierachical way.Therefore in our simulation we set up a simple toy model in which we have the observed ellipticity as data,and the only measurement error we consider 
-is a Gaussian noise add on the true lensed ellipticity.We suppose there is a uniform shear acting on one all the galaxies in sky patch,
+The typical procedure of weak lensing analysis usually include ellipticity
+measurement,shear inference,mass profile reconstruction. The measurement
+of galaxy shapes is the first step of weak gravitational lensing analysis,since
+it's the direct observable that relates with tangential shear.However
+in this paper we only concern about how to infere shear from galaxy
+ellipticity in a hierachical way.Therefore in our simulation we set
+up a simple toy model in which we have the observed ellipticity as
+data,and the only measurement error we consider is a Gaussian noise
+add on the true lensed ellipticity.We suppose there is a uniform shear
+acting on one all the galaxies in sky patch,
 
-Our approach is to use an exceedingly flexible model for intrinsic shape distribution,and assumes all the galaxies in different
-patches abeys such a distribution.Then we can calculate the joint likelihood of  shpape distribution parameters and shear in differ
-shy patches.With a classical Gibbs MCMC sampler we are able to sample their posteior distriibution.After marginalizing the shape parameters, we can
-obtain the posterior distribution of shear,which we are interested in.This approach allows us use the information maximumly
-without introducing in any wrong assumptions on intrinsic shape distribution.
+Our approach is to use an exceedingly flexible model for intrinsic
+shape distribution,and assumes all the galaxies in different patches
+abeys such a distribution.Then we can calculate the joint likelihood
+of shpape distribution parameters and shear in differ shy patches.With
+a classical Gibbs MCMC sampler we are able to sample their posteior
+distriibution.After marginalizing the shape parameters, we can obtain
+the posterior distribution of shear,which we are interested in.This
+approach allows us use the information maximumly without introducing
+in any wrong assumptions on intrinsic shape distribution.
 
-In galaxy--galaxy lensing ,since the distortion is so weak,what people usually do is stack many lensing signals together and get the "average"
-shear map,and then infers the mean mass profile of galaxy or galaxy cluster.
-However with HB method we can avoid this brute averaging ,instead we can get the posterior distribution of mass profile for 
-each lensing system - even though it has very large uncertainty- we can calculate the statistical property like galaxy-mass
-correlation function via this posterior distribution.
+In galaxy--galaxy lensing ,since the distortion is so weak,what people
+usually do is stack many lensing signals together and get the mean
+shear map,and then infers the mean mass profile of galaxy or galaxy
+cluster. However with HB method we can avoid this brute averaging
+,instead we can get the posterior distribution of mass profile for
+each lensing system - even though it has very large uncertainty- we
+can calculate the statistical property like galaxy-mass correlation
+function via this posterior distribution.
 
-This paper is orgnized as following: In section 2 we introduce the weak lensing formulas and the likelihood function .Then we 
-describe two flexible models for the intrinsic shape distribution. In section 3 we show the result of the MCMC sampling
-,and check the bias and variance of sample mean and compare with that of the simple average method.In Section 4 we discussed
+This paper is orgnized as following: In section 2 we introduce the
+weak lensing formulas and the likelihood function .Then we describe
+two flexible models for the intrinsic shape distribution. In section
+3 we show the result of the MCMC sampling ,and check the bias and
+variance of sample mean and compare with that of the simple average
+method.In Section 4 we discussed
 
@@
 \section{method}
+
 \label{sec:XXX}
@@
 in terms of the major and minor axes and orientation a, b, $\phi$,
-respectively, as $\epsilon$ = (a − b)/(a + b) exp(2i$\phi$). Due to the isotropicity
-of Universe ,we expect $\phi$ has a uniform distribution from 0 to
-$\pi$.Then we can expect 
+respectively, as $\epsilon$ = (a - b)/(a + b) exp(2i$\phi$). Due
+to the isotropicity of Universe ,we expect $\phi$ has a uniform distribution
+from 0 to $\pi$.Then we can expect 
 \begin{equation}
@@
 However in our hierachical Bayesian approach we are able to obtain
-the posterior distribution of g ,based on the assumption  $\phi$ has a uniform distribution and galaxies in different
-sky patches have the same intrinsic shape distribution.
+the posterior distribution of g ,based on the assumption $\phi$ has
+a uniform distribution and galaxies in different sky patches have
+the same intrinsic shape distribution.
 
 Suppose we know the ellipticity distribution of unlensed galaxies
-based on some parasmeters $\alpha$,then we can write the likelihood of reduced shear and $\alpha$:
+based on some parasmeters $\alpha$,then we can write the likelihood
+of reduced shear and $\alpha$:
 
 \begin{equation}
-p(\epsilon_{\ell}|\vec{g},\alpha)=p(\epsilon_{0}(\vec{g})|\alpha)*|\frac{\partial\epsilon_{0}}\,{\partial\epsilon_{\ell}}|
+p(\epsilon_{\ell}|\vec{g},\alpha)=p(\epsilon_{0}(\vec{g})|\alpha)*|\frac{\partial\epsilon_{0}}{\,}{\partial\epsilon_{\ell}}|
 \end{equation}
@@
 \begin{equation}
-p(\epsilon_{ob}|\vec{g},\alpha)=\int f(\epsilon_{ob}|\epsilon_{\ell})\,p(\epsilon_{\ell}|\vec{g},\alpha)
+p(\epsilon_{ob}|\vec{g},\alpha)=\int f(\epsilon_{ob}|\epsilon_{\ell})\, p(\epsilon_{\ell}|\vec{g},\alpha)
 \end{equation}
@@
 Since $p(\alpha)$ does not explicitly depends on $\vec{g}$ .$p(\alpha|\vec{g})$is
-just the pror distribution $p(\vec{\alpha}|\xi)$.Therefore,we have marginalized likehood
+just the pror distribution $p(\vec{\alpha}|\xi)$.Therefore,we have
+marginalized likehood 
 \begin{equation}
-p(\epsilon_{\ell}|\vec{g})=\int p(\epsilon_{\ell}|\vec{g},\alpha)\,p(\vec{\alpha}|\xi)d\alpha
+p(\epsilon_{\ell}|\vec{g})=\int p(\epsilon_{\ell}|\vec{g},\alpha)\, p(\vec{\alpha}|\xi)d\alpha
 \end{equation}
-Given that marginalized likelihood function ,in principle we could optimize it  and gives out a max-likelihood estimator 
-for \vec{g} in different patches simultaneously.
+Given that marginalized likelihood function ,in principle we could
+optimize it and gives out a max-likelihood estimator for $\vec{g}$
+in different patches simultaneously.
 
@@
 how better estimation of $\alpha$ will be obtained if we infer more
-sky patches simultaneously. With better knowledge on $\alpha$ we can
-in turn have better estimates on reduced shear g.
+sky patches simultaneously. With better knowledge on $\alpha$ we
+can in turn have better estimates on reduced shear g.
 
@@
 
-While making the posterior samples $p(\g,\alpha|Data)$ we choose to use the classical
-Gibbs sampler.
+While making the posterior samples $p(g,\alpha|Data)$ we choose to
+use the classical Gibbs sampler.
 
@@
 \section{Result}
+
 \label{sec:XXX}
@@
 \subsection{Posterior samples}
-We show the posterior samples of both g and $\alpha$ ,for both beta function and step function model.
+
+We show the posterior samples of both g and $\alpha$ ,for both beta
+function and step function model.
+
 \subsection{Bias Test}
-We test the systematical bias of our estimator.(Here the estimator is the max-marginalized likelihood estimator?)
-We plot $g_{1}-g_{1}^{true}$ VS $g_{1}^{true}$ ,and put on an error bar which equals standard deviation of 
-marginalized likehood functon $p(Data|g_{1})$ ,and use a linear fit to determin the m,c value and their standard 
-deviations.
+
+We test the systematical bias of our estimator.(Here the estimator
+is the max-marginalized likelihood estimator?) We plot $g_{1}-g_{1}^{true}$
+VS $g_{1}^{true}$ ,and put on an error bar which equals standard
+deviation of marginalized likehood functon $p(Data|g_{1})$ ,and use
+a linear fit to determin the m,c value and their standard deviations.
 
 \subsection{Accuracy Test}
-We compare the mean square error of our estimator with average and the estimator that could be constructed if the true unlensed
-ellipticity distribution were known.
-We show how the mean square error varies with number of galaxies ,number of patches and so on.
+
+We compare the mean square error of our estimator with average and
+the estimator that could be constructed if the true unlensed ellipticity
+distribution were known. We show how the mean square error varies
+with number of galaxies ,number of patches and so on.
 
 \subsection{Measurement Error}
-We show some example how our method works when there is an Gaussian noise added on the observed $\epsilon$
+
+We show some example how our method works when there is an Gaussian
+noise added on the observed $\epsilon$
 
 \subsection{prefactor $\xi$}
-Discuss about how $\xi$ is tuned ,the danger if $\xi$ is set to be too large or too small.
+
+Discuss about how $\xi$ is tuned ,the danger if $\xi$ is set to
+be too large or too small.
 
@@
 \section{Discussion}
-\label{sec:XXX}
-In weak lensing survey,one way to obtain high S/N ratio is to stack large number of lensing signal together,and 
-calculate the mean shear map of all these lensing systems.However simply to stack all the lensing signals would not be the
-optimal way because of the amount of information we can obtain from each lensing system can be very different.
-The Bayesian inference approach we proposed allows a natural way to optimally include all the data.In stead of stacking what we need to do
-is to propogate the likelihood of the shear map of each lensing system. The statistical property of all the lensing systems
-like the galaxy-mass ,shear-shar correlation function ,in principle can be calculated from these likelihood functions.
+
+\label{sec:XXX} In weak lensing survey,one way to obtain high S/N
+ratio is to stack large number of lensing signal together,and calculate
+the mean shear map of all these lensing systems.However simply to
+stack all the lensing signals would not be the optimal way because
+of the amount of information we can obtain from each lensing system
+can be very different. The Bayesian inference approach we proposed
+allows a natural way to optimally include all the data.In stead of
+stacking what we need to do is to propogate the likelihood of the
+shear map of each lensing system. The statistical property of all
+the lensing systems like the galaxy-mass ,shear-shar correlation function
+,in principle can be calculated from these likelihood functions.
 
@@
 \section{Discussion}
+
 \label{sec:discuss}
@@
 \section{Conclusions}
+
 \label{sec:conclusions}
 
-In summary,We have presented a conceptually simple method for estimating tangential shear ,
-with carefully calculated uncertainty estimates. This method is intrinsically cope with high noise levels on the input data and naturally
-allows bad fit to be identified from the residuals map.
-We have proposed an exceeding flexible model for intrinsic shape distribution allows us to obtain the correct posterior distributions,
-while avoiding making unsupported assumptions.The Gibbs sampler allows us to sample the posterior distribution of shear in 
-large number of sky patches simultaneously and efficiently.
-
+In summary,We have presented a conceptually simple method for estimating
+tangential shear , with carefully calculated uncertainty estimates.
+This method is intrinsically cope with high noise levels on the input
+data and naturally allows bad fit to be identified from the residuals
+map. We have proposed an exceeding flexible model for intrinsic shape
+distribution allows us to obtain the correct posterior distributions,
+while avoiding making unsupported assumptions.The Gibbs sampler allows
+us to sample the posterior distribution of shear in large number of
+sky patches simultaneously and efficiently.
 \begin{itemize}
-
 \item We ...
-
 \item The ...
-
 \item The ...
-
 \end{itemize}
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-\label{lastpage}
-\bsp
+\label{lastpage} \bsp
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\end{document}

### 2013-04-02 docs/ms.tex
Update ms.tex

@@
 ,instead we can get the posterior distribution of mass profile for
-each lensing system - even though it has very large uncertainty- we
-can calculate the statistical property like galaxy-mass correlation
+each lensing system - even though it may have very large uncertainty- we
+can calculate their statistical property like galaxy-mass correlation
 function via this posterior distribution.

### 2013-04-02 docs/ms.tex
Update ms.tex

@@
 data,and the only measurement error we consider is a Gaussian noise
-add on the true lensed ellipticity.We suppose there is a uniform shear
+added on the lensed galaxy ellipticity.We also suppose there is a uniform shear
 acting on one all the galaxies in sky patch,

### 2013-04-03 docs/ms.tex
Update ms.tex

@@
 The distortion in Weak lensing is typically ~ 0.01,or ~0.001 for
-galaxy-galaxy lensing it's usually more than 10 times smaller than
+galaxy-galaxy lensing. It's usually more than 10 times smaller than
 the intrinsic shape noise,it's also smaller than the distortion caused
-be PSF effect which usually has ~0.05 level. For shear measurement
+be PSF effect which is usually around ~0.05 level. For shear measurement
 the main source of uncertainty comes from the intrinsic shape noise
-. We know little knowledge about the distribution of intrinsic ellipticity,exception
-the assumption that the orientational angle should be isotropic. With
-this assumption,we can use the average of galaxies' ellipticity as
-an estimator of tangential shear.--However by doing this we lose some
+.Since the unlensed galaxy shape can not be observed directly the information
+we have about the intrinsic ellipticity is scarce,other than  the assumption that 
+the orientational angle should be isotropic. With
+this assumption,an estimator can be made by simply averaging galaxies' complex
+ellipticity.However by doing this we will not be able to utilize the
 information about how the ellipticity are distributed. Simple average
@@
 shape distribution --galaxies in different sky patches should have
-the same shape distibution--which is the result of homogeneous Universe.
+the same shape distibution--which is the natural result of the homogeneous Universe.
 
-The typical procedure of weak lensing analysis usually include ellipticity
-measurement,shear inference,mass profile reconstruction. The measurement
+A typical procedure of weak lensing analysis  includes ellipticity
+measurement,shear inference and mass profile reconstruction. The measurement
 of galaxy shapes is the first step of weak gravitational lensing analysis,since

### 2013-04-03 docs/ms.tex
Update ms.tex

@@
 it's the direct observable that relates with tangential shear.However
-in this paper we only concern about how to infere shear from galaxy
-ellipticity in a hierachical way.Therefore in our simulation we set
-up a simple toy model in which we have the observed ellipticity as
+in this paper we only concern about how to infer shear from galaxy
+ellipticity in a hierachical way.Therefore in our simulation we merely
+set up a simple toy model in which we have the observed ellipticity as
 data,and the only measurement error we consider is a Gaussian noise
@@
 abeys such a distribution.Then we can calculate the joint likelihood
-of shpape distribution parameters and shear in differ shy patches.With
+of shpape distribution parameters and shears in different sky patches.With
 a classical Gibbs MCMC sampler we are able to sample their posteior
@@
 approach allows us use the information maximumly without introducing
-in any wrong assumptions on intrinsic shape distribution.
+in any wrong assumption on intrinsic shape distribution.
 

### 2013-04-03 docs/ms.tex
Update ms.tex

@@
 
-We assume Lensed galaxy ellipticity $\epsilon_{\ell}$ is related
+We assume the lensed galaxy ellipticity $\epsilon_{\ell}$ is related
 to the intrinsic galaxy ellipticity $\epsilon_{0}$ in the weak lensing
@@
 is represented as a complex variable and g, $g^{*}$ are the reduced
-shear and its complex conjugate, respectively. $\epsilon$ is defined
-in terms of the major and minor axes and orientation a, b, $\phi$,
-respectively, as $\epsilon$ = (a - b)/(a + b) exp(2i$\phi$). Due
-to the isotropicity of Universe ,we expect $\phi$ has a uniform distribution
+shear and its complex conjugate, respectively. In weak lensing region we have 
+\begin{equation}
+g=\frac{\gamma}{1-k}\approx\gamma
+\end{equation}
+$\gamma$ is the shear .This is the assumption we use through out
+the paper.$\epsilon$ is defined in terms of the major and minor axes and orientation a, b, $\phi$,
+respectively, as
+\begin{equation}
+\epsilon=\frac{a-b}{a+b}e^{2i\phi}
+\end{equation}
+Due to the isotropicity of Universe ,for the unlensed ellipticity $\epsilon_{0}$ 
+we expect $\phi$ has a uniform distribution
 from 0 to $\pi$.Then we can expect 
@@
 \end{equation}
-
 Therefore $<\epsilon_{\ell}>$ can be adopted as an estimator of g.

### 2013-04-03 docs/ms.tex
Update ms.tex

@@
 intrinsic ellipticity distribution .When we use the step function
-model for P($\epsilon_{0}$),which we'll decribe latter.We find that
+model for P($\epsilon_{0}$),which we'll describe latter.We find that
 we need to use a prior on $\alpha$ . 

### 2013-04-03 docs/ms.tex
Update ms.tex

@@
 
-In summary,We have presented a conceptually simple method for estimating
-tangential shear , with carefully calculated uncertainty estimates.
-This method is intrinsically cope with high noise levels on the input
-data and naturally allows bad fit to be identified from the residuals
-map. We have proposed an exceeding flexible model for intrinsic shape
-distribution allows us to obtain the correct posterior distributions,
-while avoiding making unsupported assumptions.The Gibbs sampler allows
-us to sample the posterior distribution of shear in large number of
+In summary,We have presented a conceptually hierachical inference
+approach for weak lensing shear estimation, with carefully calculated 
+uncertainty estimates.This method is intrinsically cope with high noise
+levels on the input data and naturally allows bad fit to be identified 
+from the residuals map. We have proposed an exceeding flexible model for 
+intrinsic shape distribution allows us to obtain the correct posterior 
+distributions, while avoiding making unsupported assumptions.The Gibbs
+sampler allows us to sample the posterior distribution of shear in large number of
 sky patches simultaneously and efficiently.

### 2013-04-03 docs/ms.tex
Update ms.tex

@@
 levels on the input data and naturally allows bad fit to be identified 
-from the residuals map. We have proposed an exceeding flexible model for 
-intrinsic shape distribution allows us to obtain the correct posterior 
+from the residuals map. We also have proposed a flexible non-parametric model 
+for intrinsic shape distribution allows us to obtain the correct posterior 
 distributions, while avoiding making unsupported assumptions.The Gibbs

### 2013-04-03 docs/ms.tex
Update ms.tex

--- 2013-04-03 docs/ms.tex
@@
 levels on the input data and naturally allows bad fit to be identified 
-from the residuals map. We have proposed an exceeding flexible model for 
-intrinsic shape distribution allows us to obtain the correct posterior 
-distributions, while avoiding making unsupported assumptions.The Gibbs
+from the residuals map. We also have proposed a flexible non-parametric model 
+for intrinsic shape distribution allows us to obtain the correct posterior 
+distributions, while avoiding making any unsupported assumptions.The Gibbs
 sampler allows us to sample the posterior distribution of shear in large number of

### 2013-04-04 docs/ms.tex
Update ms.tex

@@
 
+The probability distribution can be visualised by plotting points at each sample
+position. An example in the x, y plane is shown for the posterior distribution of
+$\vec{g}$ of 64 sky patches in Fig. .8 galaxy shape profiles in each patch is used as the data.
+The number density of samples is proportional to the probability density.The figure shows that the two parameters of $\vec{g}$
+do not have strong correlation,since the shape of smaples is close to a circle.
+We also shows the histogram of g1 in a single sky patch.Not surprisingly it is close to a Gaussian distribution.
+If the probability distribution of parameters are perfect Gaussian,their most probable estimates and uncertainty 
+is just the mean and standard deviation of the Gaussian distribution.
+
 \subsection{Bias Test}
@@
 sky patches simultaneously and efficiently.
+
+Several  model fitting galaxy shape measurent method have been proposed in recent years.
+Unlike the average method which merely request a point estimator of galaxy ellipcity,our hierachical bayesian
+utilizes the whole likelihood of the galaxy ellipticity.
 \begin{itemize}

### 2013-04-04 docs/ms.tex
Update ms.tex

@@
 If the probability distribution of parameters are perfect Gaussian,their most probable estimates and uncertainty 
-is just the mean and standard deviation of the Gaussian distribution.
+is just the mean and standard deviation of the Gaussian distribution.However,in pratical,we find that the distribution 
+of reduced shear $\vec{g}$ will be getting closer to Gaussian,with larger number of galaxies used.When we have more than
+8 galaxies in each sky patch,we found it's eligible to make such an approximation that to use sample mean and standard 
+deviation as most probable estimates and uncertainty.
 

### 2013-04-04 docs/ms.tex
Update ms.tex

--- 2013-04-04 docs/ms.tex
@@
 If the probability distribution of parameters are perfect Gaussian,their most probable estimates and uncertainty 
-is just the mean and standard deviation of the Gaussian distribution.
+is just the mean and standard deviation of the Gaussian distribution.However,in pratical,we find that the distribution 
+of reduced shear $\vec{g}$ will be getting closer to Gaussian,with larger number of galaxies used.When we have more than
+8 galaxies in each sky patch,we found it's eligible to make such an approximation that to use sample mean and standard 
+deviation as most probable estimates and uncertainty.We will justify this approximation witha bias test in the following
+sub section.
 

### 2013-04-04 docs/ms.tex
Update ms.tex

--- 2013-04-04 docs/ms.tex
@@
 If the probability distribution of parameters are perfect Gaussian,their most probable estimates and uncertainty 
-is just the mean and standard deviation of the Gaussian distribution.
+is just the mean and standard deviation of the Gaussian distribution.However,in pratical,we find that the distribution 
+of reduced shear $\vec{g}$ will be getting closer to Gaussian,with larger number of galaxies used.When we have more than
+8 galaxies in each sky patch,we found it's eligible to make such an approximation that to use sample mean and standard 
+deviation as most probable estimates and uncertainty.We will justify this approximation with a bias test in the following
+sub section.
 

### 2013-04-04 docs/ms.tex
Update ms.tex

@@
 \subsection{Bias Test}
+In this section,we measured the levels of possible systemmatical
+bias of this Hierachical inference method.
+Following Heymans et al. (2006), we quantify the systematic bias in
+in terms of the multiplicative error m and additive error c on the
+true shear $g^{true}$ 
+\begin{equation}
+\hat{g_{i}}-g_{i}^{true}=m_{i}g_{i}^{true}+c_{i}
+\end{equation}
 
-We test the systematical bias of our estimator.(Here the estimator
-is the max-marginalized likelihood estimator?) We plot $g_{1}-g_{1}^{true}$
-VS $g_{1}^{true}$ ,and put on an error bar which equals standard
-deviation of marginalized likehood functon $p(Data|g_{1})$ ,and use
-a linear fit to determin the m,c value and their standard deviations.
+The accuracy of Weak Lensing survey depends on both galaxy shape measurement
+and shear inference .In this paper our main concern is how to infere
+shear in a HB method instead off traditional averaging method and
+it does not involve the shape measurement part .Therefore we assume
+we have perfect galaxies ellipticity measurement,and all the possible
+inaccuracy is due to this HB shear inference method.
+
+We calculated the average of $g^{estimated}-g^{true}$ of 10,000 data
+sets as described above.Each data set has 64 patches and 8{*}64 galaxies,and
+the true P($\epsilon$) is Beta(2.8,2.8) .For both Beta function model
+and step funtion model we then determin the best fitted parameters
+m and c of fomula (15).Figure 9 shows an example of step funtion model
+with prior prefator $\xi=3$.The results of the systematical bias
+analysis are tabulated in table 1.
 

### 2013-04-04 docs/ms.tex
Update ms.tex

@@
 In this section,we measured the levels of possible systemmatical
-bias of this Hierachical inference method.
+bias of this Hierachical inference method.In principle given the correct model and prior ,
+the hierchical Bayesian inference method would have no bias,if propagate the whole likelihood function.
+However,in practical,the bias may be introduced by the model we use for the intrinsic shape distribution,
+and the prior regularizer of the prefactor $\xi$ as well as the Gaussian approximation we did for the likelihood
+function of $\vec{g}$ .Therefore a bias test is necessary to identify how much bias there is. 
 Following Heymans et al. (2006), we quantify the systematic bias in

### 2013-04-04 docs/ms.tex
Update ms.tex

@@
 
-The accuracy of Weak Lensing survey depends on both galaxy shape measurement
-and shear inference .In this paper our main concern is how to infere
-shear in a HB method instead off traditional averaging method and
-it does not involve the shape measurement part .Therefore we assume
-we have perfect galaxies ellipticity measurement,and all the possible
-inaccuracy is due to this HB shear inference method.
+To isolate out the source of the bias in this section,we assume we have perfect measurement on galaxy shape.
+We will discuss more on the influence of measurement error section 4.4 .
 
 We calculated the average of $g^{estimated}-g^{true}$ of 10,000 data
-sets as described above.Each data set has 64 patches and 8{*}64 galaxies,and
-the true P($\epsilon$) is Beta(2.8,2.8) .For both Beta function model
-and step funtion model we then determin the best fitted parameters
-m and c of fomula (15).Figure 9 shows an example of step funtion model
+sets as described in section 4.1 .Each data set has 64 patches and 8$\times$64 galaxies,and
+the true P($\epsilon$) is Beta(2.8,2.8).The input true values of $\vec{g}_{1}$ and $\vec{g}_{2}$ of the 
+64$\times$10,000 sky patches are generated randomly from a uniform distribution from -0.1 to 0.1 . 
 with prior prefator $\xi=3$.The results of the systematical bias

### 2013-04-04 docs/ms.tex
Update ms.tex

@@
 sets as described in section 4.1 .Each data set has 64 patches and 8$\times$64 galaxies,and
-the true P($\epsilon$) is Beta(2.8,2.8).The input true values of $\vec{g}_{1}$ and $\vec{g}_{2}$ of the 
-64$\times$10,000 sky patches are generated randomly from a uniform distribution from -0.1 to 0.1 . 
-with prior prefator $\xi=3$.The results of the systematical bias
-analysis are tabulated in table 1.
+the true P($\epsilon$) is Beta(2.8,2.8).The step function model is used with the prior prefator $\xi=3$.
+The input true values of $\vec{g}_{1}$ and $\vec{g}_{2}$ of the 64$\times$10,000 sky patches are generated randomly from a uniform distribution from -0.1 to 0.1 . 
+The results of the systematical bias analysis are tabulated in table 1.
 

### 2013-04-04 docs/ms.tex
Update ms.tex

@@
 The input true values of $\vec{g}_{1}$ and $\vec{g}_{2}$ of the 64$\times$10,000 sky patches are generated randomly from a uniform distribution from -0.1 to 0.1 .
-The results of the systematical bias analysis are tabulated in table 1.
+
+As described in the previous subsection we use the sample mean as the most probable $g_{i}$ and 
+the standard deviation as the uncertainty.A standard weighted minimum $\chi^{2}$ linear fit is performed to get the
+most-likely value and uncertainty of m and c.
 

### 2013-04-04 docs/ms.tex
Update ms.tex

@@
 
+Due to the limitation of galaxy number we are not able to get an exact value for m and c.However in our result 
+both the most-like and uncertainty of m are around $10^{-3}$ and for c they are around $10^{-4}$ . Due to the
+relatively large uncertainty,it is only an rough estimate of bias level.
+
 \subsection{Accuracy Test}
@@
 
-Discuss about how $\xi$ is tuned ,the danger if $\xi$ is set to
-be too large or too small.
+One limitation of the step function model is that it needs to be \textit{regularized};
+this is achieved by assigning a prior PDF for the step heights $\vec{\alpha}$.
+We use the form $Prior(\vec{\alpha}|\xi)=exp(-\xi\sum(\alpha_{i}-\alpha_{i-1})^{2})$
+when inferring the P($\epsilon$) and $g$. The choice of this functional
+form corresponds to the assumption that the true P($\epsilon$) is
+smooth, which seems fairly natural. This function has a hyperparameter,
+$\xi$, that needs to be set somehow. If $\xi$ is too small, the
+inferred P($\epsilon$) will be too noisy, and the accuracy of the
+$g$ inference will decrease. Likewise, choosing an $\xi$ that is
+too large, the inferred P($\epsilon$) will be too smooth, and the
+data will be under-fitted. In principle one could infer $\xi$ form
+the data at hand, but in practice we find that we further more need some
+prior regularizer on $\xi$ to obtain correct inference.Therefore in this paper 
+we just tuned $\xi$ empirically .From various trials, We find
+that $\xi$ should be proportional to the mean data number density and can
+be approximated by the following empirical formula: 
+\begin{equation}
+\xi=N<\rho(|\epsilon|)>/256*\frac{Nbin}{10}
+\end{equation}
+Here $<\rho|\epsilon|>=\int\rho(|\epsilon|)^{2}d(|\epsilon|)$ corresponds
+to the average of data number density,and Nbin is the number of bins used 
+in step function model.
 

### 2013-04-04 docs/ms.tex
Update ms.tex

@@
 \subsection{Measurement Error}
+In this section we  discuss how the shape measurement error will
+affect the variance and bias of this Hierarchy Bayesian method.As
+mentioned before ,we only considers the catalog-level problem of how to combine galaxy ellipticity
+measurements.Therefore we assume the likelihood of true lensed ellipticity $p(\epsilon_{ob}|\epsilon_{\ell})
+is a 2D Gaussian with sigma equals 0.05 and mean equals true lensed ellipticity.
 
-We show some example how our method works when there is an Gaussian
-noise added on the observed $\epsilon$
+Therefore the likelihood of $g$ and $\alpha$ becomes
+\begin{equation}
+L(g,\alpha|\epsilon_{ob})=P(\epsilon_{ob}|g,\alpha)=\intop f(\epsilon_{ob}|\epsilon_{\ell})P(\epsilon_{\ell}|g,\alpha)d\epsilon_{\ell}
+\end{equation}
 

### 2013-04-04 docs/ms.tex
Update ms.tex

--- 2013-04-04 docs/ms.tex
@@
 \subsection{Measurement Error}
-
-We show some example how our method works when there is an Gaussian
-noise added on the observed $\epsilon$
+In this section we  discuss how the shape measurement error will
+affect the variance and bias of this Hierarchy Bayesian method.
+In principle,if the likelihood of true lensed ellipticity $p(\epsilon_{ob}|\epsilon_{\ell})$
+is known the likelihood $p(\epsilon_{ob}|g,\alpha)$ can be calculated using the convolution as equation ().
+However,due to the limitation of computational time we avoid to do this convolution but use $\epsilon_{ob}$
+as an estimator of $\epsilon_{\ell}$ .
+The likelihood of true lensed ellipticity $p(\epsilon_{ob}|\epsilon_{\ell})$ we use in the simulation is a 2D
+Gaussian with mean equals $\epsilon_{\ell}$ and $\sigma$ equals 0.05 .
+The result of bias test and mean square error test is shown in...
 

### 2013-04-04 docs/ms.tex
Update ms.tex

@@
 %
-% Hierarchical Inference in Weak Lensing: Inferring Pr(e)
+% hierarchical Inference in Weak Lensing: Inferring Pr(e)
 %
@@
 in this paper we only concern about how to infer shear from galaxy
-ellipticity in a hierachical way.Therefore in our simulation we merely
+ellipticity in a hierarchical way.Therefore in our simulation we merely
 set up a simple toy model in which we have the observed ellipticity as
@@
 
-However in our hierachical Bayesian approach we are able to obtain
+However in our hierarchical Bayesian approach we are able to obtain
 the posterior distribution of g ,based on the assumption $\phi$ has
@@
 In this section,we measured the levels of possible systemmatical
-bias of this Hierachical inference method.In principle given the correct model and prior ,
+bias of this Hierarchical inference method.In principle given the correct model and prior ,
 the hierchical Bayesian inference method would have no bias,if propagate the whole likelihood function.
@@
 In this section we  discuss how the shape measurement error will
-affect the variance and bias of this Hierarchy Bayesian method.
+affect the variance and bias of this Hierarchical Bayesian method.
 In principle,if the likelihood of true lensed ellipticity $p(\epsilon_{ob}|\epsilon_{\ell})$

### 2013-04-04 docs/ms.tex
Update ms.tex

@@
 the nature of dark energy (Albrecht et al. 2006; Peacock\&Schneider
-2006). While in galaxy--galaxy weaklensing ,tangential shear distortions
+2006). While in galaxy--galaxy weaklensing, tangential shear distortions
 of background galaxies around foreground galaxies, allows direct measurement
@@
 galaxy-galaxy lensing. It's usually more than 10 times smaller than
-the intrinsic shape noise,it's also smaller than the distortion caused
+the intrinsic shape noise, it's also smaller than the distortion caused
 be PSF effect which is usually around ~0.05 level. For shear measurement
@@
 of galaxy shapes is the first step of weak gravitational lensing analysis,since
-it's the direct observable that relates with tangential shear.However
+it's the direct observable that relates with tangential shear. However
 in this paper we only concern about how to infer shear from galaxy
-ellipticity in a hierarchical way.Therefore in our simulation we merely
+ellipticity in a hierarchical way. Therefore in our simulation we merely
 set up a simple toy model in which we have the observed ellipticity as
@@
 added on the lensed galaxy ellipticity.We also suppose there is a uniform shear
-acting on one all the galaxies in sky patch,
+acting on one all the galaxies in sky patch.
 
 Our approach is to use an exceedingly flexible model for intrinsic
-shape distribution,and assumes all the galaxies in different patches
-abeys such a distribution.Then we can calculate the joint likelihood
+shape distribution, and assumes all the galaxies in different patches
+abeys such a distribution. Then we can calculate the joint likelihood
 of shpape distribution parameters and shears in different sky patches.With
@@
 distriibution.After marginalizing the shape parameters, we can obtain
-the posterior distribution of shear,which we are interested in.This
+the posterior distribution of shear,which we are interested in. This
 approach allows us use the information maximumly without introducing
@@
 cluster. However with HB method we can avoid this brute averaging
-,instead we can get the posterior distribution of mass profile for
+, instead we can get the posterior distribution of mass profile for
 each lensing system - even though it may have very large uncertainty- we
@@
 \end{equation}
-$\gamma$ is the shear .This is the assumption we use through out
+$\gamma$ is the shear. This is the assumption we use through out
 the paper.$\epsilon$ is defined in terms of the major and minor axes and orientation a, b, $\phi$,
@@
 \end{equation}
-Due to the isotropicity of Universe ,for the unlensed ellipticity $\epsilon_{0}$ 
+Due to the isotropicity of Universe, for the unlensed ellipticity $\epsilon_{0}$ 
 we expect $\phi$ has a uniform distribution
@@
 However in our hierarchical Bayesian approach we are able to obtain
-the posterior distribution of g ,based on the assumption $\phi$ has
+the posterior distribution of g, based on the assumption $\phi$ has
 a uniform distribution and galaxies in different sky patches have
@@
 Suppose we know the ellipticity distribution of unlensed galaxies
-based on some parasmeters $\alpha$,then we can write the likelihood
+based on some parasmeters $\alpha$, then we can write the likelihood
 of reduced shear and $\alpha$:
@@
 The prior of $\alpha$ some how depends on the model we choose for
-intrinsic ellipticity distribution .When we use the step function
-model for P($\epsilon_{0}$),which we'll describe latter.We find that
-we need to use a prior on $\alpha$ . 
+intrinsic ellipticity distribution. When we use the step function
+model for P($\epsilon_{0}$), which we'll describe latter.We find that
+we need to use a prior on $\alpha$. 
 \begin{equation}
@@
 Since $p(\alpha)$ does not explicitly depends on $\vec{g}$ .$p(\alpha|\vec{g})$is
-just the pror distribution $p(\vec{\alpha}|\xi)$.Therefore,we have
+just the pror distribution $p(\vec{\alpha}|\xi)$.Therefore, we have
 marginalized likehood 
@@
 \end{equation}
-Given that marginalized likelihood function ,in principle we could
+Given that marginalized likelihood function, in principle we could
 optimize it and gives out a max-likelihood estimator for $\vec{g}$
@@
 $P(\epsilon_{0}|\alpha)$.Therefore we proposed an exceedingly flexible
-model for $P(\epsilon_{0}|\alpha)$,which does not requires further
+model for $P(\epsilon_{0}|\alpha)$, which does not requires further
 assumption on $P(\epsilon_{0}|\alpha)$.
@@
 We divide the 2-D space r$\in$(0,1) into N bins .The probability
-of each bin is $p_{i}=e^{\alpha_{i}}$ .$\overrightarrow{\alpha}$
-is a N-D parameter vector to be infered,simultaneously with g.
+of each bin is $p_{i}=e^{\alpha_{i}}$. $\overrightarrow{\alpha}$
+is a N-D parameter vector to be infered, simultaneously with g.
 
@@
 
-Meanwhile,in order to show the correctness of our method ,we also
+Meanwhile,in order to show the correctness of our method, we also
 set up a simulation in which we know the true $P(|\epsilon_{0}||\alpha)$
-is a Beta distribution ,and thus $\alpha$ is the 2-D parameter (p,q)
+is a Beta distribution, and thus $\alpha$ is the 2-D parameter (p,q)
 of the Beta distribution.We will show the posterior samples using
@@
 One thing to note is that the conditional probability of g in ith
-patch only explicitly depends on $\alpha$ ,but not g in other patches.Therefore
+patch only explicitly depends on $\alpha$, but not g in other patches. Therefore
 with $\alpha$ fixed ,the posterior distribution of reduced shear
-in ith patch are independent from each other . 
+in ith patch are independent from each other. 
 \begin{equation}
@@
 do not have strong correlation,since the shape of smaples is close to a circle.
-We also shows the histogram of g1 in a single sky patch.Not surprisingly it is close to a Gaussian distribution.
+We also shows the histogram of g1 in a single sky patch. Not surprisingly it is close to a Gaussian distribution.
 If the probability distribution of parameters are perfect Gaussian,their most probable estimates and uncertainty 
@@
 8 galaxies in each sky patch,we found it's eligible to make such an approximation that to use sample mean and standard 
-deviation as most probable estimates and uncertainty.We will justify this approximation with a bias test in the following
+deviation as most probable estimates and uncertainty. We will justify this approximation with a bias test in the following
 sub section.
@@
 bias of this Hierarchical inference method.In principle given the correct model and prior ,
-the hierchical Bayesian inference method would have no bias,if propagate the whole likelihood function.
-However,in practical,the bias may be introduced by the model we use for the intrinsic shape distribution,
+the hierchical Bayesian inference method would have no bias, if propagate the whole likelihood function.
+However,in practical, the bias may be introduced by the model we use for the intrinsic shape distribution,
 and the prior regularizer of the prefactor $\xi$ as well as the Gaussian approximation we did for the likelihood
-function of $\vec{g}$ .Therefore a bias test is necessary to identify how much bias there is. 
+function of $\vec{g}$. Therefore a bias test is necessary to identify how much bias there is. 
 Following Heymans et al. (2006), we quantify the systematic bias in
@@
 As described in the previous subsection we use the sample mean as the most probable $g_{i}$ and 
-the standard deviation as the uncertainty.A standard weighted minimum $\chi^{2}$ linear fit is performed to get the
+the standard deviation as the uncertainty. A standard weighted minimum $\chi^{2}$ linear fit is performed to get the
 most-likely value and uncertainty of m and c.
@@
 both the most-like and uncertainty of m are around $10^{-3}$ and for c they are around $10^{-4}$ . Due to the
-relatively large uncertainty,it is only an rough estimate of bias level.
+relatively large uncertainty, it is only an rough estimate of bias level.
 
@@
 However,due to the limitation of computational time we avoid to do this convolution but use $\epsilon_{ob}$
-as an estimator of $\epsilon_{\ell}$ .
+as an estimator of $\epsilon_{\ell}$.
 The likelihood of true lensed ellipticity $p(\epsilon_{ob}|\epsilon_{\ell})$ we use in the simulation is a 2D
@@
 
-In summary,We have presented a conceptually hierachical inference
+In summary, we have presented a conceptually hierachical inference
 approach for weak lensing shear estimation, with carefully calculated 

### 2013-04-04 docs/ms.tex
Update ms.tex

@@
 
-We calculated the average of $g^{estimated}-g^{true}$ of 10,000 data
-sets as described in section 4.1 .Each data set has 64 patches and 8$\times$64 galaxies,and
+We calculated the value of $\hat{g}-g^{true}$ of 10,000 data. Each data set has 64 patches and 8$\times$64 galaxies,and
 the true P($\epsilon$) is Beta(2.8,2.8).The step function model is used with the prior prefator $\xi=3$.

### 2013-04-05 docs/ms.tex
Update ms.tex

@@
 of shpape distribution parameters and shears in different sky patches.With
-a classical Gibbs MCMC sampler we are able to sample their posteior
-distriibution.After marginalizing the shape parameters, we can obtain
+a classical Gibbs MCMC sampler we are able to sample their posterior
+distribution.After marginalizing the shape parameters, we can obtain
 the posterior distribution of shear,which we are interested in. This

### 2013-04-05 docs/ms.tex
Update ms.tex

@@
 Several  model fitting galaxy shape measurent method have been proposed in recent years.
-Unlike the average method which merely request a point estimator of galaxy ellipcity,our hierachical bayesian
-utilizes the whole likelihood of the galaxy ellipticity.
+Unlike the average method which merely request a point estimator of galaxy ellipcity,our 
+hierachical bayesian approach utilizes the whole likelihood of the galaxy ellipticity.
 \begin{itemize}

### 2013-04-05 docs/ms.tex
Update ms.tex

@@
 shear map,and then infers the mean mass profile of galaxy or galaxy
-cluster. However with HB method we can avoid this brute averaging
+cluster. However with Hierarchical Bayesian method we can avoid this brute averaging
 , instead we can get the posterior distribution of mass profile for

### 2013-04-05 docs/ms.tex
Update ms.tex

@@
 variance of sample mean and compare with that of the simple average
-method.In Section 4 we discussed
+method.In Section 4 we discussed the systematical bias ,mean square error
+and effects of prefactor $\xi$ and galaxy shape measurement error.
 

### 2013-04-06 docs/ms.tex
Update ms.tex

@@
 \begin{equation}
-p(\epsilon_{\ell}|\vec{g},\alpha)=p(\epsilon_{0}(\vec{g})|\alpha)*|\frac{\partial\epsilon_{0}}{\,}{\partial\epsilon_{\ell}}|
+p(\epsilon_{\ell}|\vec{g},\alpha)=p(\epsilon_{0}(\vec{g})|\alpha)\,|\frac{\partial\epsilon_{0}}{\partial\epsilon_{\ell}}|
 \end{equation}
@@
 Here the prior distribtuion we use for $\vec{g}$ is a 2D flat distribution
-in the region $|g|<1$.Therefore $p(\vec{g)}=\begin{cases}
-1 & |\vec{g}|<1\\
-0 & |\vec{g}|>1
-\end{cases}$
+in the region $|\vec{g}|<1$.Therefore $p(\vec{g)}=1$ if $|\vec{g}|<1$
+and $p(\vec{g})=0$ if $|\vec{g}|>1$.
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%  SECTION X: DISCUSSION
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section{Discussion}
-
-\label{sec:discuss}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 %%  SECTION X: CONCLUSIONS

### 2013-04-06 docs/ms.tex
Update ms.tex
update me.tex

@@
 
-While making the posterior samples $p(g,\alpha|Data)$ we choose to
+While making the posterior samples $p(\vec{g},\alpha|Data)$ we choose to
 use the classical Gibbs sampler.
@@
 
-While the conditional distribution of one variable given all others
-is just proportional to the joint distribution
+The conditional probability distribution of one variable given all the other variables are proportional to their joint probability distribution
 
 \begin{equation}
-p(x_{j}|x_{1},....,x_{j-1},x_{j+1}...,x_{n})\varpropto p(x_{1},.....,x_{n})
+p(x_{j}|x_{1},....,x_{j-1},x_{j+1}...,x_{n})\propto p(x_{1},.....,x_{n})
 \end{equation}

### 2013-04-07 docs/ms.tex
Update ms.tex

@@
 
-Weak gravitational lensing has become the most potential tool to explore
-the dark universe. One application of Weak gravitational lensing is
+Weak gravitational lensing has the potential to be the most powerful
+tool to explore the dark universe. One application of weak gravitational lensing is
 that it can be used to measure the mass profile of single galaxy,galaxy
-groups and clusters or large scales. Cosmic shear is the mild distortion
+groups , clusters  the large scales. Cosmic shear is the mild distortion
 of distant galaxy images due to the bending of light by intervening
@@
 2006). While in galaxy--galaxy weaklensing, tangential shear distortions
-of background galaxies around foreground galaxies, allows direct measurement
-of the galaxy-DM correlation
+of background galaxies around foreground galaxies allows direct measurement
+of the galaxy-DM correlation.
 
-The distortion in Weak lensing is typically ~ 0.01,or ~0.001 for
-galaxy-galaxy lensing. It's usually more than 10 times smaller than
-the intrinsic shape noise, it's also smaller than the distortion caused
-be PSF effect which is usually around ~0.05 level. For shear measurement
-the main source of uncertainty comes from the intrinsic shape noise
-.Since the unlensed galaxy shape can not be observed directly the information
-we have about the intrinsic ellipticity is scarce,other than  the assumption that 
-the orientational angle should be isotropic. With
-this assumption,an estimator can be made by simply averaging galaxies' complex
-ellipticity.However by doing this we will not be able to utilize the
-information about how the ellipticity are distributed. Simple average
-point estimator can't use the other reasonable assumption about intrinsic
-shape distribution --galaxies in different sky patches should have
-the same shape distibution--which is the natural result of the homogeneous Universe.
+The distortion of galaxy image caused by weak lensing effect is typically only a few percent.
+It's usually more than 10 times smaller than galaxies' intrinsic ellipticity. It's also smaller than the distortion caused
+be PSF effect which is usually around 0.05 level. The main source of uncertainty of shear measurements comes from the intrinsic shape noise
+. Since the unlensed galaxy shape can not be observed directly the information
+we have about the intrinsic ellipticity is scarce. One natural assumption about the intrinsic shape distribution is that 
+it should be isotropic. With this assumption,an estimator can be made by simply averaging galaxies' complex
+ellipticity.However by doing this we are not be able to utilize the
+information about how the ellipticity are distributed. The mean ellipticity
+point estimator can't use another reasonable assumption about the intrinsic shape distribution --galaxies in different sky patches should have
+the same shape distibution--which is a natural result of the homogeneous Universe.
 
-A typical procedure of weak lensing analysis  includes ellipticity
-measurement,shear inference and mass profile reconstruction. The measurement
-of galaxy shapes is the first step of weak gravitational lensing analysis,since
-it's the direct observable that relates with tangential shear. However
+A typical procedure of weak lensing analysis  includes galaxy shape measurements from images
+,shear inference and mass profile reconstruction. The galaxy shape measurement is usually the
+first step of weak lensing analysis,since it's the direct observable related with shear effect. However
 in this paper we only concern about how to infer shear from galaxy
-ellipticity in a hierarchical way. Therefore in our simulation we merely
-set up a simple toy model in which we have the observed ellipticity as
-data,and the only measurement error we consider is a Gaussian noise
-added on the lensed galaxy ellipticity.We also suppose there is a uniform shear
-acting on one all the galaxies in sky patch.
+ellipticity in a novel hierarchical way. Therefore we set up a simple toy model in which we have the observed ellipticity as
+data,and the only shape measurement error we consider is a Gaussian noise
+added on the lensed galaxy ellipticity. We also suppose there is a uniform shear
+acting on one all the galaxies in one sky patch.
 
@@
 shape distribution, and assumes all the galaxies in different patches
-abeys such a distribution. Then we can calculate the joint likelihood
-of shpape distribution parameters and shears in different sky patches.With
-a classical Gibbs MCMC sampler we are able to sample their posterior
-distribution.After marginalizing the shape parameters, we can obtain
-the posterior distribution of shear,which we are interested in. This
-approach allows us use the information maximumly without introducing
+abey such a distribution. Then we can calculate the joint likelihood
+of shpape distribution parameters and shear in different sky patches.With
+a classical Gibbs MCMC sampler we are able to sample the joint posterior distribution
+in an efficient way. After marginalizing the shape parameters, we can obtain
+the posterior distribution of shear, which we are interested in. This
+approach allows us to use the information maximumly without introducing
 in any wrong assumption on intrinsic shape distribution.
 
-In galaxy--galaxy lensing ,since the distortion is so weak,what people
-usually do is stack many lensing signals together and get the mean
-shear map,and then infers the mean mass profile of galaxy or galaxy
-cluster. However with Hierarchical Bayesian method we can avoid this brute averaging
-, instead we can get the posterior distribution of mass profile for
+In galaxy--galaxy lensing, since the distortion is so weak, what people
+usually do is to stack many lensing signals together. Then they can obtain the mean
+shear map and infer the mean mass profile of single galaxy or galaxy
+cluster. However with the Hierarchical Bayesian method we can avoid this brute averaging
+. Insteadly, we can get the posterior distribution of mass profile for
 each lensing system  - even though it may have very large uncertainty- we
@@
 This paper is orgnized as following: In section 2 we introduce the
-weak lensing formulas and the likelihood function .Then we describe
-two flexible models for the intrinsic shape distribution. In section
-3 we show the result of the MCMC sampling ,and check the bias and
-variance of sample mean and compare with that of the simple average
-method.In Section 4 we discussed the systematical bias ,mean square error
-and effects of prefactor $\xi$ and galaxy shape measurement error.
+weak lensing formulas and the likelihood functions. Then we describe
+two flexible models for the intrinsic shape distribution.Section 3 details
+the results of simulations including tests for biases and accuracy.In Section 4, we
+derive some general conclusions and outline suggestions for future
+development.
 
@@
 \begin{equation}
-p(\epsilon_{ob}|\vec{g},\alpha)=\int f(\epsilon_{ob}|\epsilon_{\ell})\, p(\epsilon_{\ell}|\vec{g},\alpha)
+p(\epsilon_{ob}|\vec{g},\alpha)=\int f(\epsilon_{ob}|\epsilon_{\ell})\, p(\epsilon_{\ell}|\vec{g},\alpha)\,d\epsilon_{\ell}
 \end{equation}
@@
 \begin{equation}
-p(\epsilon_{\ell}|\vec{g})=\int p(\epsilon_{\ell}|\vec{g},\alpha)p(\alpha|\vec{g})d\alpha
+p(\epsilon_{\ell}|\vec{g})=\int p(\epsilon_{\ell}|\vec{g},\vec{\alpha})\,p(\vec{\alpha}|\vec{g})\,d\vec{\alpha}
 \end{equation}
@@
 \begin{equation}
-p(\epsilon_{\ell}|\vec{g})=\int p(\epsilon_{\ell}|\vec{g},\alpha)\, p(\vec{\alpha}|\xi)d\alpha
+p(\epsilon_{\ell}|\vec{g})=\int p(\epsilon_{\ell}|\vec{g},\vec{\alpha})\, p(\vec{\alpha}|\xi)\,d\vec{\alpha}
 \end{equation}
@@
 
-\subsection{Model for Prior($\epsilon_{0}$)}
+\subsection{Model for Intrinsic Shape distribution
 
@@
 
-Several  model fitting galaxy shape measurent method have been proposed in recent years.
+Several  model fitting  shape measurent methods have been proposed in recent years.
 Unlike the average method which merely request a point estimator of galaxy ellipcity,our 

### 2013-04-07 docs/ms.tex
Update ms.tex

@@
 abey such a distribution. Then we can calculate the joint likelihood
-of shpape distribution parameters and shear in different sky patches.With
+of shpape distribution parameters and shear in different sky patches. With
 a classical Gibbs MCMC sampler we are able to sample the joint posterior distribution
@@
 approach allows us to use the information maximumly without introducing
-in any wrong assumption on intrinsic shape distribution.
+in any wrong assumption on the intrinsic shape distribution.
 

### 2013-04-07 docs/ms.tex
Update ms.tex

@@
 of distant galaxy images due to the bending of light by intervening
-matter.It provides one of the most promising methods for constraining
+matter. It provides one of the most promising methods for constraining
 the nature of dark energy (Albrecht et al. 2006; Peacock\&Schneider
@@
 ,shear inference and mass profile reconstruction. The galaxy shape measurement is usually the
-first step of weak lensing analysis,since it's the direct observable related with shear effect. However
+first step of weak lensing analysis, since it's the direct observable related with shear effect. However
 in this paper we only concern about how to infer shear from galaxy
 ellipticity in a novel hierarchical way. Therefore we set up a simple toy model in which we have the observed ellipticity as
-data,and the only shape measurement error we consider is a Gaussian noise
+data, and the only shape measurement error we consider is a Gaussian noise
 added on the lensed galaxy ellipticity. We also suppose there is a uniform shear
@@
 weak lensing formulas and the likelihood functions. Then we describe
-two flexible models for the intrinsic shape distribution.Section 3 details
-the results of simulations including tests for biases and accuracy.In Section 4, we
+two flexible models for the intrinsic shape distribution. Section 3 details
+the results of simulations including tests for biases and accuracy. In Section 4, we
 derive some general conclusions and outline suggestions for future
@@
 Here the prior distribtuion we use for $\vec{g}$ is a 2D flat distribution
-in the region $|\vec{g}|<1$.Therefore $p(\vec{g)}=1$ if $|\vec{g}|<1$
+in the region $|\vec{g}|<1$. Therefore $p(\vec{g)}=1$ if $|\vec{g}|<1$
 and $p(\vec{g})=0$ if $|\vec{g}|>1$.
@@
 Since $p(\alpha)$ does not explicitly depends on $\vec{g}$ .$p(\alpha|\vec{g})$is
-just the pror distribution $p(\vec{\alpha}|\xi)$.Therefore, we have
+just the pror distribution $p(\vec{\alpha}|\xi)$. Therefore, we have
 marginalized likehood 
@@
 One thing to note is that the likelihood of g in patch i only depends
-on the shape parameters but not dependent to g in other patch.Therefore,the
+on the shape parameters but not dependent to g in other patch. Therefore, the
 marginalized likelihood of shape parameters has an equation like:
@@
 
-Here $\xi$ is a prefactor need to be tuned .
+Here $\xi$ is a prefactor need to be tuned.
 
@@
 is a Beta distribution, and thus $\alpha$ is the 2-D parameter (p,q)
-of the Beta distribution.We will show the posterior samples using
+of the Beta distribution. We will show the posterior samples using
 both of these two methods in next section. Note that for either model
@@
 Therefore sampling reduced shear g from conditional distribution can
-be reduced to 2D sampling problem,which can be done very quickly.
+be reduced to 2D sampling problem, which can be done very quickly.
 
@@
 
-The procedure of our simulation is that ,first we generated N{*}NP
+The procedure of our simulation is that, first we generated N{*}NP
 unlensed galaxies' elliprticity from the ``true'' $P(\epsilon_{0})$,and
-asign these galaxies into NP patches equally.So each patch has N galaxies.Second
-we generate NP true reduced shears ,and asign them to each patch,and
+asign these galaxies into NP patches equally. So each patch has N galaxies.Second
+we generate NP true reduced shears, and asign them to each patch,and
 then shear the unlensed galaxies using formula (4) .
@@
 We also shows the histogram of g1 in a single sky patch. Not surprisingly it is close to a Gaussian distribution.
-If the probability distribution of parameters are perfect Gaussian,their most probable estimates and uncertainty 
-is just the mean and standard deviation of the Gaussian distribution.However,in pratical,we find that the distribution 
-of reduced shear $\vec{g}$ will be getting closer to Gaussian,with larger number of galaxies used.When we have more than
-8 galaxies in each sky patch,we found it's eligible to make such an approximation that to use sample mean and standard 
+If the probability distribution of parameters are perfect Gaussian, the most probable estimates and uncertainty 
+is just the mean and standard deviation of the Gaussian distribution. However,in pratical,we find that the distribution 
+of reduced shear $\vec{g}$ will be getting closer to Gaussian,with larger number of galaxies used. When we have more than
+8 galaxies in each sky patch, we found it's eligible to make such an approximation that to use sample mean and standard 
 deviation as most probable estimates and uncertainty. We will justify this approximation with a bias test in the following
@@
 the hierchical Bayesian inference method would have no bias, if propagate the whole likelihood function.
-However,in practical, the bias may be introduced by the model we use for the intrinsic shape distribution,
+However, in practical, the bias may be introduced by the model we use for the intrinsic shape distribution,
 and the prior regularizer of the prefactor $\xi$ as well as the Gaussian approximation we did for the likelihood
@@
 distribution were known. We show how the mean square error varies
-with number of galaxies ,number of patches and so on.
+with number of galaxies, number of patches and so on.
 
@@
 affect the variance and bias of this Hierarchical Bayesian method.
-In principle,if the likelihood of true lensed ellipticity $p(\epsilon_{ob}|\epsilon_{\ell})$
+In principle, if the likelihood of true lensed ellipticity $p(\epsilon_{ob}|\epsilon_{\ell})$
 is known the likelihood $p(\epsilon_{ob}|g,\alpha)$ can be calculated using the convolution as equation ().

### 2013-04-07 docs/ms.tex
Update ms.tex

@@
 
+\begin{figure}
+\end{figure}
+\begin{figure}
+\includegraphics[scale=0.2]{fig/test10}
+
+\caption{The figure shows the posterior samples of reduced shear g
+in all the 64 patches . The two blues lines indicate the poisition of
+true(input) $g_{1}$ and $g_{2}$. The Blue '+' shows the position
+of sample mean, while the red '+' shows the result of mean ellipticity
+estimator.}
+\end{figure}
+
 \subsection{Bias Test}
@@
 relatively large uncertainty, it is only an rough estimate of bias level.
+\begin{figure}
+\includegraphics[scale=0.5]{fig/g1bias}
+
+\caption{The figure shows the estimated $g_{1}$ values minus the true (input)
+$g_{1}^{true}$ . The distribution range of $g_{1}^{true}$ is from
+-0.1 to 0.1. Originally there are 640,000 true $g_{1}$. We bin the
+plot for presentation purpose. The data point and error bars are the weighted
+ average and  variance of $\delta g_{1}$ in each bin.The blue
+line is the result of weighted linear fit of the original 640,000 data points
+with sample standard deviation as error bar.}
+\end{figure}
 
@@
 with number of galaxies, number of patches and so on.
+\begin{figure}
+\includegraphics[scale=0.5]{fig/Np_step}
+
+\includegraphics[scale=0.5]{fig/N16NP_vary}
+
+\caption{The upper panel shows how the mean square error of g estimates varies
+with the number of patches used with 8 galaxies in each patch. The
+lowwer panel shows the same thing with 16 galaxies in each patch. }
+\end{figure}
 

### 2013-04-10 docs/ms.tex
update ms.tex
Update ms.tex

@@
 added on the lensed galaxy ellipticity. We also suppose there is a uniform shear
-acting on one all the galaxies in one sky patch.
+acting on all the galaxies in one sky patch.
 
@@
 
-\subsection{Model for Intrinsic Shape distribution
+\subsection{Model for Intrinsic Shape distribution}
 
@@
 \begin{figure}
-\includegraphics[scale=0.2]{fig/test10}
+\includegraphics[scale=0.15]{fig/test10}
 
@@
 \begin{figure}
-\includegraphics[scale=0.5]{fig/Np_step}
+\includegraphics[scale=0.48]{fig/Np_step}
 
-\includegraphics[scale=0.5]{fig/N16NP_vary}
+\includegraphics[scale=0.48]{fig/N16NP_vary}
 
@@
 with the number of patches used with 8 galaxies in each patch. The
-lowwer panel shows the same thing with 16 galaxies in each patch. }
+lowwer panel shows the same thing with 16 galaxies in each patch.
+The green line in both graphics shows the mean square error of mean ellipticity estimator,while the red line is the mean square error of g estimates from the likelihood built with the true intrinsic shape distribution.
+They are both independ from the number of patches.
+}
 \end{figure}

### 2013-04-10 docs/ms.tex
Update ms.tex

@@
 Since $p(\alpha)$ does not explicitly depends on $\vec{g}$ .$p(\alpha|\vec{g})$is
-just the pror distribution $p(\vec{\alpha}|\xi)$. Therefore, we have
+just the prior distribution $p(\vec{\alpha}|\xi)$. Therefore, we have
 marginalized likehood 
@@
 One thing to note is that the likelihood of g in patch i only depends
-on the shape parameters but not dependent to g in other patch. Therefore, the
-marginalized likelihood of shape parameters has an equation like:
+on the shape parameters but not dependent to shear in other patches. Therefore, the
+marginalized likelihood of shape parameters is :
 
@@
 $\ell_{i}(\alpha|data_{i})$ is the marginalized likelihood function
-calculated with data in the ith patch.From this formula we can see
+calculated with data in the ith patch. From this formula we can see
 how better estimation of $\alpha$ will be obtained if we infer more
@@
 of human's knowledge we are not able to give an analytical form of
-$P(\epsilon_{0}|\alpha)$.Therefore we proposed an exceedingly flexible
+$P(\epsilon_{0}|\alpha)$. Therefore we proposed an exceedingly flexible
 model for $P(\epsilon_{0}|\alpha)$, which does not requires further
@@
 
-We divide the 2-D space r$\in$(0,1) into N bins .The probability
+We divide the 2-D space r $\in$(0,1) into N bins. The probability
 of each bin is $p_{i}=e^{\alpha_{i}}$. $\overrightarrow{\alpha}$
@@
 
-Meanwhile,in order to show the correctness of our method, we also
+Meanwhile, in order to show the correctness of our method, we also
 set up a simulation in which we know the true $P(|\epsilon_{0}||\alpha)$
@@
 patch only explicitly depends on $\alpha$, but not g in other patches. Therefore
-with $\alpha$ fixed ,the posterior distribution of reduced shear
+with $\alpha$ fixed, the posterior distribution of reduced shear
 in ith patch are independent from each other. 
@@
 The procedure of our simulation is that, first we generated N{*}NP
-unlensed galaxies' elliprticity from the ``true'' $P(\epsilon_{0})$,and
-asign these galaxies into NP patches equally. So each patch has N galaxies.Second
-we generate NP true reduced shears, and asign them to each patch,and
+unlensed galaxies' elliprticity from the ``true'' $P(\epsilon_{0})$, and
+asign these galaxies into NP patches equally. So each patch has N galaxies. Second
+we generate NP true reduced shears, and asign them to each patch, and
 then shear the unlensed galaxies using formula (4) .
@@
 
-Use Gibbs sampler and $P(\epsilon_{0}|\alpha)$ mentioned previously,we
+Use Gibbs sampler and $P(\epsilon_{0}|\alpha)$ mentioned previously, we
 are to sample the posterior distribution of g and $\alpha$ simultaneously
@@
 
-We show the posterior samples of both g and $\alpha$ ,for both beta
+We show the posterior samples of both g and $\alpha$, for both beta
 function and step function model.
@@
 $\vec{g}$ of 64 sky patches in Fig. .8 galaxy shape profiles in each patch is used as the data.
-The number density of samples is proportional to the probability density.The figure shows that the two parameters of $\vec{g}$
+The number density of samples is proportional to the probability density. The figure shows that the two parameters of $\vec{g}$
 do not have strong correlation,since the shape of smaples is close to a circle.
@@
 If the probability distribution of parameters are perfect Gaussian, the most probable estimates and uncertainty 
-is just the mean and standard deviation of the Gaussian distribution. However,in pratical,we find that the distribution 
-of reduced shear $\vec{g}$ will be getting closer to Gaussian,with larger number of galaxies used. When we have more than
-8 galaxies in each sky patch, we found it's eligible to make such an approximation that to use sample mean and standard 
-deviation as most probable estimates and uncertainty. We will justify this approximation with a bias test in the following
+is just the mean and standard deviation of the Gaussian distribution. However, in pratical, we find that the distribution 
+of reduced shear $\vec{g}$ will  get closer to Gaussia, with larger number of galaxies used. When the number of galaxies in 
+one patch is equal or more than 8, we found it's eligible to make such an approximation that to use sample mean and standard 
+deviation as the most probable estimates and uncertainty. We will justify this approximation with a bias test in the following
 sub section.
@@
 \subsection{Bias Test}
-In this section,we measured the levels of possible systemmatical
-bias of this Hierarchical inference method.In principle given the correct model and prior ,
+In this section, we measured the levels of possible systemmatical
+bias of this Hierarchical inference method. In principle given the correct model and prior,
 the hierchical Bayesian inference method would have no bias, if propagate the whole likelihood function.
@@
 
-To isolate out the source of the bias in this section,we assume we have perfect measurement on galaxy shape.
-We will discuss more on the influence of measurement error section 4.4 .
+To isolate out the source of the bias in this section, we assume we have perfect measurement on galaxy shape.
+We will discuss more on the influence of measurement error section 3.4 .
 
-We calculated the value of $\hat{g}-g^{true}$ of 10,000 data. Each data set has 64 patches and 8$\times$64 galaxies,and
-the true P($\epsilon$) is Beta(2.8,2.8).The step function model is used with the prior prefator $\xi=3$.
+We calculated the value of $\hat{g}-g^{true}$ of 10,000 data. Each data set has 64 patches and 8$\times$64 galaxies, and
+the true P($\epsilon$) is Beta(2.8,2.8). The step function model is used with the prior prefator $\xi=3$.
 The input true values of $\vec{g}_{1}$ and $\vec{g}_{2}$ of the 64$\times$10,000 sky patches are generated randomly from a uniform distribution from -0.1 to 0.1 .
@@
 As described in the previous subsection we use the sample mean as the most probable $g_{i}$ and 
-the standard deviation as the uncertainty. A standard weighted minimum $\chi^{2}$ linear fit is performed to get the
+the standard deviation as the uncertainty. A weighted minimum $\chi^{2}$ linear fit is performed to get the
 most-likely value and uncertainty of m and c.
 
-Due to the limitation of galaxy number we are not able to get an exact value for m and c.However in our result 
+Due to the limitation of galaxy number we are not able to get an exact value for m and c. However in our result 
 both the most-like and uncertainty of m are around $10^{-3}$ and for c they are around $10^{-4}$ . Due to the
@@
 \caption{The figure shows the estimated $g_{1}$ values minus the true (input)
-$g_{1}^{true}$ . The distribution range of $g_{1}^{true}$ is from
+$g_{1}^{true}$. The distribution range of $g_{1}^{true}$ is from
 -0.1 to 0.1. Originally there are 640,000 true $g_{1}$. We bin the
 plot for presentation purpose. The data point and error bars are the weighted
- average and  variance of $\delta g_{1}$ in each bin.The blue
+ average and  variance of $\delta g_{1}$ in each bin. The blue
 line is the result of weighted linear fit of the original 640,000 data points
@@
 Gaussian with mean equals $\epsilon_{\ell}$ and $\sigma$ equals 0.05 .
-The result of bias test and mean square error test is shown in...
+The result of bias test and mean square error test is shown in
 
@@
 
-\label{sec:XXX} In weak lensing survey,one way to obtain high S/N
-ratio is to stack large number of lensing signal together,and calculate
-the mean shear map of all these lensing systems.However simply to
+\label{sec:XXX} In weak lensing survey, one way to obtain high S/N
+ratio is to stack large number of lensing signal together, and calculate
+the mean shear map of all these lensing systems. However simply to
 stack all the lensing signals would not be the optimal way because
@@
 can be very different. The Bayesian inference approach we proposed
-allows a natural way to optimally include all the data.In stead of
+allows a natural way to optimally include all the data. Instead of
 stacking what we need to do is to propogate the likelihood of the
@@
 approach for weak lensing shear estimation, with carefully calculated 
-uncertainty estimates.This method is intrinsically cope with high noise
+uncertainty estimates. This method is intrinsically cope with high noise
 levels on the input data and naturally allows bad fit to be identified 
@@
 for intrinsic shape distribution allows us to obtain the correct posterior 
-distributions, while avoiding making any unsupported assumptions.The Gibbs
+distributions, while avoiding making any unsupported assumptions. The Gibbs
 sampler allows us to sample the posterior distribution of shear in large number of
@@
 Unlike the average method which merely request a point estimator of galaxy ellipcity,our 
-hierachical bayesian approach utilizes the whole likelihood of the galaxy ellipticity.
+hierachical bayesian approach utilizes the whole likelihood of the galaxy ellipticity in a Bayesian probability analysis framework.
 \begin{itemize}

### 2013-04-10 docs/ms.tex
Update ms.tex

@@
 
-In Gibbs sampling ,samples of variable $x_{j}$ is made from the conditional
-probability distribution:$p(x_{j}^{(i)}|x_{1}^{(i)},....,x_{j-1}^{(i)},x_{j+1}^{(i-1)}...,x_{n}^{(i-1)})$
+In Gibbs sampling, samples of variable $x_{j}$ is made from the conditional
+probability distribution: $p(x_{j}^{(i)}|x_{1}^{(i)},....,x_{j-1}^{(i)},x_{j+1}^{(i-1)}...,x_{n}^{(i-1)})$
 
@@
 patch only explicitly depends on $\alpha$, but not g in other patches. Therefore
-with $\alpha$ fixed, the posterior distribution of reduced shear
-in ith patch are independent from each other. 
+with $\alpha$ fixed, the posterior distributions of reduced shear in different patches are independent from each other. 
 \begin{equation}
@@
 \end{equation}
-Therefore sampling reduced shear g from conditional distribution can
-be reduced to 2D sampling problem, which can be done very quickly.
+Therefore sampling reduced shear g from conditional distribution can be reduced to 2D sampling problem, which can be done very quickly.
 
@@
 we generate NP true reduced shears, and asign them to each patch, and
-then shear the unlensed galaxies using formula (4) .
+then shear the unlensed galaxies using formula (4).
 
@@
 is just the mean and standard deviation of the Gaussian distribution. However, in pratical, we find that the distribution 
-of reduced shear $\vec{g}$ will  get closer to Gaussia, with larger number of galaxies used. When the number of galaxies in 
+of reduced shear $\vec{g}$ will  get closer to Gaussian, when larger number of galaxies in one patch  is used. When the number of galaxies in 
 one patch is equal or more than 8, we found it's eligible to make such an approximation that to use sample mean and standard 
-deviation as the most probable estimates and uncertainty. We will justify this approximation with a bias test in the following
+deviation as the most probable estimates and uncertainty. We'll justify this approximation with a bias test in the following
 sub section.

### 2013-04-10 docs/ms.tex
Update ms.tex

@@
 Suppose we know the ellipticity distribution of unlensed galaxies
-based on some parasmeters $\alpha$, then we can write the likelihood
+based on some parasmeters $\alpha$, then we can write down the likelihood
 of reduced shear and $\alpha$:

### 2013-04-10 docs/ms.tex
Update ms.tex

@@
 ,shear inference and mass profile reconstruction. The galaxy shape measurement is usually the
-first step of weak lensing analysis, since it's the direct observable related with shear effect. However
+first step of weak lensing analysis, since it's a direct observable related with shear effect. However
 in this paper we only concern about how to infer shear from galaxy
@@
 cluster. However with the Hierarchical Bayesian method we can avoid this brute averaging
-. Insteadly, we can get the posterior distribution of mass profile for
+. Instead, we can get the posterior distribution of mass profile for
 each lensing system  - even though it may have very large uncertainty- we
@@
 
-If there is measurement error on $\epsilon_{ob}$,we will have 
+If there is measurement error on $\epsilon_{ob}$, we will have 
 \begin{equation}
@@
 
-Since $p(\alpha)$ does not explicitly depends on $\vec{g}$ .$p(\alpha|\vec{g})$is
+Since $p(\alpha)$ does not explicitly depends on $\vec{g}$. $p(\alpha|\vec{g})$is
 just the prior distribution $p(\vec{\alpha}|\xi)$. Therefore, we have
@@
 The number density of samples is proportional to the probability density. The figure shows that the two parameters of $\vec{g}$
-do not have strong correlation,since the shape of smaples is close to a circle.
+do not have strong correlation, since the shape of smaples is close to a circle.
 We also shows the histogram of g1 in a single sky patch. Not surprisingly it is close to a Gaussian distribution.

### 2013-04-10 docs/ms.tex
Update ms.tex

@@
 we have about the intrinsic ellipticity is scarce. One natural assumption about the intrinsic shape distribution is that 
-it should be isotropic. With this assumption,an estimator can be made by simply averaging galaxies' complex
+it should be isotropic. With this assumption, an estimator can be made by simply averaging galaxies' complex
 ellipticity.However by doing this we are not be able to utilize the

### 2013-04-10 docs/ms.tex
Update ms.tex

@@
 ,shear inference and mass profile reconstruction. The galaxy shape measurement is usually the
-first step of weak lensing analysis, since it's a direct observable related with shear effect. However
+first step of weak lensing analysis, since it's a direct observable of shear effect. However
 in this paper we only concern about how to infer shear from galaxy
@@
 we expect $\phi$ has a uniform distribution
-from 0 to $\pi$.Then we can expect 
+from 0 to $\pi$. Then we can expect 
 \begin{equation}

### 2013-04-10 docs/ms.tex
Update ms.tex

@@
 of reduced shear $\vec{g}$ will  get closer to Gaussian, when larger number of galaxies in one patch  is used. When the number of galaxies in 
-one patch is equal or more than 8, we found it's eligible to make such an approximation that to use sample mean and standard 
+one patch is equal to or more than 8, we found it's eligible to make such an approximation that to use sample mean and standard 
 deviation as the most probable estimates and uncertainty. We'll justify this approximation with a bias test in the following

### 2013-04-10 docs/ms.tex
Update ms.tex

@@
 the data at hand, but in practice we find that we further more need some
-prior regularizer on $\xi$ to obtain correct inference.Therefore in this paper 
+prior regularizer on $\xi$ to obtain correct inference. Therefore in this paper 
 we just tuned $\xi$ empirically .From various trials, We find

### 2013-04-10 docs/ms.tex
Update ms.tex

@@
 shear map of each lensing system. The statistical property of all
-the lensing systems like the galaxy-mass ,shear-shar correlation function
-,in principle can be calculated from these likelihood functions.
+the lensing systems like the galaxy-mass, shear-shar correlation function
+, in principle can be calculated from these likelihood functions.
 

### 2013-04-10 docs/ms.tex
Update ms.tex

@@
 tool to explore the dark universe. One application of weak gravitational lensing is
-that it can be used to measure the mass profile of single galaxy,galaxy
+that it can be used to measure the mass profile of single galaxy, galaxy
 groups , clusters  the large scales. Cosmic shear is the mild distortion
@@
 
-Since $p(\alpha)$ does not explicitly depends on $\vec{g}$. $p(\alpha|\vec{g})$is
+Since $p(\alpha)$ does not explicitly depends on $\vec{g}$. $p(\alpha|\vec{g})$ is
 just the prior distribution $p(\vec{\alpha}|\xi)$. Therefore, we have

### 2013-04-10 docs/ms.tex
Update ms.tex

@@
 . Instead, we can get the posterior distribution of mass profile for
-each lensing system  - even though it may have very large uncertainty- we
-can calculate their statistical property like galaxy-mass correlation
+each lensing system, even though it may have very large uncertainty. Then we
+can calculate their statistical properties like galaxy-mass correlation
 function via this posterior distribution.

### 2013-04-10 docs/ms.tex
Update ms.tex

@@
 that it can be used to measure the mass profile of single galaxy, galaxy
-groups , clusters  the large scales. Cosmic shear is the mild distortion
+groups, clusters  the large scales. Cosmic shear is the mild distortion
 of distant galaxy images due to the bending of light by intervening

### 2013-04-10 docs/ms.tex
Update ms.tex

@@
 
-The total time needed to sample $g$ and $\alpha$ of 64 sky patches
-with 8 galaxies in each patch will only be approximitly 25s on a 2
-GHz CPU.
+The total time needed to sample $g$ and $\alpha$ of 64 sky patches with 8 galaxies in each patch will only be 
+approximitly 25s on a 2 GHz CPU.
 
@@
 \caption{The figure shows the posterior samples of reduced shear g
-in all the 64 patches . The two blues lines indicate the poisition of
+in all the 64 patches. The two blues lines indicate the poisition of
 true(input) $g_{1}$ and $g_{2}$. The Blue '+' shows the position
@@
 We calculated the value of $\hat{g}-g^{true}$ of 10,000 data. Each data set has 64 patches and 8$\times$64 galaxies, and
-the true P($\epsilon$) is Beta(2.8,2.8). The step function model is used with the prior prefator $\xi=3$.
+the true(input) P($\epsilon_{0}$) is Beta(2.8,2.8). The step function model is used with the prior prefator $\xi=3$.
 The input true values of $\vec{g}_{1}$ and $\vec{g}_{2}$ of the 64$\times$10,000 sky patches are generated randomly from a uniform distribution from -0.1 to 0.1 .
@@
 prior regularizer on $\xi$ to obtain correct inference. Therefore in this paper 
-we just tuned $\xi$ empirically .From various trials, We find
+we just tuned $\xi$ empirically. From various trials, We find
 that $\xi$ should be proportional to the mean data number density and can
@@
 Here $<\rho|\epsilon|>=\int\rho(|\epsilon|)^{2}d(|\epsilon|)$ corresponds
-to the average of data number density,and Nbin is the number of bins used 
+to the average of data number density, and Nbin is the number of bins used 
 in step function model.

### 2013-04-10 docs/ms.tex
Update ms.tex

@@
 It's usually more than 10 times smaller than galaxies' intrinsic ellipticity. It's also smaller than the distortion caused
-be PSF effect which is usually around 0.05 level. The main source of uncertainty of shear measurements comes from the intrinsic shape noise
-. Since the unlensed galaxy shape can not be observed directly the information
+be PSF effect which is usually around 0.05 level. The main source of uncertainty of shear measurements is the intrinsic shape noise
+. Since the unlensed galaxy shape can not be observed directly, the information
 we have about the intrinsic ellipticity is scarce. One natural assumption about the intrinsic shape distribution is that 
 it should be isotropic. With this assumption, an estimator can be made by simply averaging galaxies' complex
-ellipticity.However by doing this we are not be able to utilize the
+ellipticity. However by doing this we are not be able to utilize the
 information about how the ellipticity are distributed. The mean ellipticity
@@
 In galaxy--galaxy lensing, since the distortion is so weak, what people
-usually do is to stack many lensing signals together. Then they can obtain the mean
+usually do is to stack many lensing signals together. Then they can the mean
 shear map and infer the mean mass profile of single galaxy or galaxy
 cluster. However with the Hierarchical Bayesian method we can avoid this brute averaging
-. Instead, we can get the posterior distribution of mass profile for
+of lensing signal. Instead, we can get the posterior distribution of mass profile for
 each lensing system, even though it may have very large uncertainty. Then we

### 2013-04-10 docs/ms.tex
Update ms.tex

@@
 intrinsic ellipticity distribution. When we use the step function
-model for P($\epsilon_{0}$), which we'll describe latter.We find that
+model for P($\epsilon_{0}$), which we'll describe latter. We find that
 we need to use a prior on $\alpha$. 
@@
 
-One thing to note is that the conditional probability of g in ith
-patch only explicitly depends on $\alpha$, but not g in other patches. Therefore
+One thing to note is that the conditional probability of g in one patch only explicitly depends on $\alpha$, but not g in other patches. Therefore
 with $\alpha$ fixed, the posterior distributions of reduced shear in different patches are independent from each other. 

### 2013-04-10 docs/ms.tex
Update ms.tex

@@
 
-Note that both $\epsilon_{0}$ and $\epsilon_{\ell}$are complex numbers.So
+Note that both $\epsilon_{0}$ and $\epsilon_{\ell}$ are complex numbers. So
 $|\frac{\partial\epsilon_{0}}{\partial\epsilon_{\ell}}|$ is the Jacobian

### 2013-04-10 docs/ms.tex
Update ms.tex

@@
 A typical procedure of weak lensing analysis  includes galaxy shape measurements from images
-,shear inference and mass profile reconstruction. The galaxy shape measurement is usually the
+, shear inference and mass profile reconstruction. The galaxy shape measurement is usually the
 first step of weak lensing analysis, since it's a direct observable of shear effect. However
@@
 In galaxy--galaxy lensing, since the distortion is so weak, what people
-usually do is to stack many lensing signals together. Then they can the mean
+usually do is to stack many lensing signals together. Then they can obain the mean
 shear map and infer the mean mass profile of single galaxy or galaxy

### 2013-04-10 docs/ms.tex
Update ms.tex

@@
 is known the likelihood $p(\epsilon_{ob}|g,\alpha)$ can be calculated using the convolution as equation ().
-However,due to the limitation of computational time we avoid to do this convolution but use $\epsilon_{ob}$
+However, due to the limitation of computational time we avoid to do this convolution but use $\epsilon_{ob}$
 as an estimator of $\epsilon_{\ell}$.
@@
 Several  model fitting  shape measurent methods have been proposed in recent years.
-Unlike the average method which merely request a point estimator of galaxy ellipcity,our 
+Unlike the average method which merely request a point estimator of galaxy ellipcity, our 
 hierachical bayesian approach utilizes the whole likelihood of the galaxy ellipticity in a Bayesian probability analysis framework.

### 2013-04-11 docs/ms.tex
Update ms.tex

@@
 In galaxy--galaxy lensing, since the distortion is so weak, what people
-usually do is to stack many lensing signals together. Then they can obain the mean
+usually do is to stack many lensing signals together. Then they can obtain the mean
 shear map and infer the mean mass profile of single galaxy or galaxy
@@
 $|\frac{\partial\epsilon_{0}}{\partial\epsilon_{\ell}}|$ is the Jacobian
-determinant term,which can be calculated numerically from formula
+determinant term, which is calculated numerically from formula
 (5).
@@
 intrinsic ellipticity distribution. When we use the step function
-model for P($\epsilon_{0}$), which we'll describe latter. We find that
-we need to use a prior on $\alpha$. 
+model for P($\epsilon_{0}$), which we'll describe latter, we find that
+we need to use a prior regulazier on $\alpha$. 
 \begin{equation}
@@
 
-Given the likehood functions and priors we can also calculated the
-marginalized likelihood function. 
+Given the likehood functions and priors we can also calculated the marginalized likelihood function. 
 \begin{equation}
@@
 \end{equation}
-Given that marginalized likelihood function, in principle we could
-optimize it and gives out a max-likelihood estimator for $\vec{g}$
+Given that marginalized likelihood function, in principle we could optimize it and gives out a max-likelihood estimator for $\vec{g}$
 in different patches simultaneously.
 
-One thing to note is that the likelihood of g in patch i only depends
+One thing to note is that the likelihood of g in one patch only explicitly depends
 on the shape parameters but not dependent to shear in other patches. Therefore, the
@@
 Here $\xi$ is a prefactor need to be tuned.
-
 Meanwhile, in order to show the correctness of our method, we also

### 2013-04-11 docs/ms.tex
Update ms.tex

@@
 
+\begin{figure}
+
+\caption{\protect\includegraphics{averagebias}\protect\includegraphics{bayesianbias}}
+
+The upper panel shows the systematic bias of the mean ellipticity
+estimator. m=$7.9\times10^{-4}\pm0.0029$ , c=$3.63\times10^{-4}\pm1.637\times10^{-4}$.The
+lowwer panel shows the systembatic bias of the sample mean. m=$-0.06\pm0.00253$,
+c=$3\times10^{-4}\pm1.55\times10^{-4}$ . For both cases the m,c values
+are obtained from unweighted linear fit using 640,000 data points. We bin the plot into ten bins for presentation
+purpose. The black square denotes the mean of $\Delta g$ in that
+bin.
+\end{figure}
+
 \subsection{Accuracy Test}

### 2013-04-11 docs/ms.tex
Update ms.tex
update mx.tex

@@
 \end{figure}
+Suppose we have perfect measurements on galaxy shape, the measures
+ellipticity is equall to the true lensed ellipticity. The mean ellipticity
+estimator has following expression :
+\begin{equation}
+<\epsilon_{\ell}>=g^{t}+<\epsilon_{0}>+<(\epsilon_{0}+g^{t})[-g^{t*}\epsilon_{0}+O(g^{t*}\epsilon_{0})]>
+\end{equation}
+When the unlensd ellipticity is purely isotropic ,we have $<\epsilon_{\ell}>=g^{t}$ . In this case, the mean ellipticity estimator is 
+unbiased.
+Meanwhile we find that simply using the posterior mean as the estimator of g will lead to a significant bias. 
+Figure 3 shows the result of bias test for both mean ellipticity and posterior mean estimator.
 
@@
 
-\caption{\protect\includegraphics{averagebias}\protect\includegraphics{bayesianbias}}
+\includegraphics[scale=0.48]{fig/averagebias}
 
-The upper panel shows the systematic bias of the mean ellipticity
+\includegraphics[scale=0.48]{fig/bayesianbias}
+
+\caption{The upper panel shows the systematic bias of the mean ellipticity
 estimator. m=$7.9\times10^{-4}\pm0.0029$ , c=$3.63\times10^{-4}\pm1.637\times10^{-4}$.The
@@
 purpose. The black square denotes the mean of $\Delta g$ in that
-bin.
+bin.}
 \end{figure}

### 2013-04-11 docs/ms.tex
modify abstract

@@
 unlensed ellipticity distribution simultaneously with the shear map.  The best
-shear-field estimators (point estimates), in this context, become
-maximum-\emph{marginalized}-likelihood estimates, in which uncertainty about the
+shear-field estimates, in this context, become the \emph{marginalized}-likelihood functions, in which uncertainty about the
 inferred unlensed distribution has been marginalized out.  We show that our proposed
-estimators perform better than simple mean-ellipticity estimators both in terms of
-bias and variance.  We also show that as the number of observed galaxies becomes
+estimates do not give a significant bias when averaged by statistical weight and perform better than simple mean-ellipticity estimators both in terms of variance.
+We also show that as the number of observed galaxies becomes
 large, the performance of our proposed estimators approaches the performance of a

### 2013-04-12 docs/ms.tex
Update ms.tex

@@
 One thing to note is that the conditional probability of g in one patch only explicitly depends on $\alpha$, but not g in other patches. Therefore
-with $\alpha$ fixed, the posterior distributions of reduced shear in different patches are independent from each other. 
+With $\alpha$ fixed, the posterior distributions of reduced shear in different patches are independent from each other. 
 \begin{equation}
@@
 \end{equation}
-Therefore sampling reduced shear g from conditional distribution can be reduced to 2D sampling problem, which can be done very quickly.
+Therefore sampling reduced shear g from the conditional probability distribution can be reduced to a 2D sampling problem, which can be done very quickly.
 
@@
 
-Finally we can put on some noise on $\epsilon_{\ell}$ to get the
+Finally we can add noise on $\epsilon_{\ell}$ to get the
 observed ellipticity $\epsilon_{ob}$. For simplicity we've only considered

### 2013-04-12 docs/ms.tex
Update ms.tex

@@
 However in our hierarchical Bayesian approach we are able to obtain
-the posterior distribution of g, based on the assumption $\phi$ has
+the posterior distribution of reduced shear, based on the assumption that $\phi$ has
 a uniform distribution and galaxies in different sky patches have
@@
 
-Suppose we know the ellipticity distribution of unlensed galaxies
-based on some parasmeters $\alpha$, then we can write down the likelihood
+Suppose we know the intrnsic ellipticity distribution P($\epslion_{0}$)
+based on some parasmeters $\alpha$. Then we can write down the likelihood
 of reduced shear and $\alpha$:

### 2013-04-12 docs/ms.tex
Update ms.tex

@@
 of reduced shear $\vec{g}$ will  get closer to Gaussian, when larger number of galaxies in one patch  is used. When the number of galaxies in 
-one patch is equal to or more than 8, we found it's eligible to make such an approximation that to use sample mean and standard 
+one patch is equal to or larger than 8, we found it's eligible to make such an approximation that to use sample mean and standard 
 deviation as the most probable estimates and uncertainty. We'll justify this approximation with a bias test in the following
@@
 \end{figure}
-Suppose we have perfect measurements on galaxy shape, the measures
-ellipticity is equall to the true lensed ellipticity. The mean ellipticity
+Suppose we have perfect measurements on galaxy shape. The measured ellipticity then equals to the true lensed ellipticity. The mean ellipticity
 estimator has following expression :

### 2013-04-12 docs/ms.tex
Update ms.tex

@@
 \subsection{Bias Test}
-In this section, we measured the levels of possible systemmatical
-bias of this Hierarchical inference method. In principle given the correct model and prior,
+In principle given the correct model and prior,
 the hierchical Bayesian inference method would have no bias, if propagate the whole likelihood function.

### 2013-04-12 docs/ms.tex
Update ms.tex

@@
 function of $\vec{g}$. Therefore a bias test is necessary to identify how much bias there is. 
-Following Heymans et al. (2006), we quantify the systematic bias in
+Following Heymans et al. (2006), we quantify the systematic bias 
 in terms of the multiplicative error m and additive error c on the
@@
 \end{figure}
-Suppose we have perfect measurements on galaxy shape. The measured ellipticity then equals to the true lensed ellipticity. The mean ellipticity
+Suppose we have perfect measurements on galaxy shape. The measured ellipticity then equals to the true lensed ellipticity. With equation (1) the mean ellipticity
 estimator has following expression :

### 2013-04-12 docs/ms.tex
grammar correction

@@
 
-Suppose we know the intrnsic ellipticity distribution P($\epslion_{0}$)
+Suppose we know the intrnsic ellipticity distribution P($\epsilon_{0}$)
 based on some parasmeters $\alpha$. Then we can write down the likelihood
@@
 ratio is to stack large number of lensing signal together, and calculate
-the mean shear map of all these lensing systems. However simply to
-stack all the lensing signals would not be the optimal way because
-of the amount of information we can obtain from each lensing system
+the mean shear map of all these lensing systems. However simply 
+stacking all the lensing signals would not be the optimal way because
+the amount of information we can obtain from each lensing system
 can be very different. The Bayesian inference approach we proposed

### 2013-04-12 docs/ms.tex
Update ms.tex

@@
 
-In Gibbs sampling, samples of variable $x_{j}$ is made from the conditional
+In Gibbs sampling, variables $x_{j}$ are sampled from the conditional
 probability distribution: $p(x_{j}^{(i)}|x_{1}^{(i)},....,x_{j-1}^{(i)},x_{j+1}^{(i-1)}...,x_{n}^{(i-1)})$
@@
 \end{equation}
-When the unlensd ellipticity is purely isotropic ,we have $<\epsilon_{\ell}>=g^{t}$ . In this case, the mean ellipticity estimator is 
+When the unlensd ellipticity is isotropic ,we have $<\epsilon_{\ell}>=g^{t}$ . In this case, the mean ellipticity estimator is 
 unbiased.

### 2013-04-12 docs/ms.tex
Update ms.tex

@@
 Meanwhile, in order to show the correctness of our method, we also
-set up a simulation in which we know the true $P(|\epsilon_{0}||\alpha)$
+set up a simulation in which we know that the true $P(|\epsilon_{0}||\alpha)$
 is a Beta distribution, and thus $\alpha$ is the 2-D parameter (p,q)

### 2013-04-12 docs/ms.tex
Update ms.tex

@@
 It's usually more than 10 times smaller than galaxies' intrinsic ellipticity. It's also smaller than the distortion caused
-be PSF effect which is usually around 0.05 level. The main source of uncertainty of shear measurements is the intrinsic shape noise
+by the PSF effect which is usually around 0.05 level. The main source of uncertainty of shear measurements is the intrinsic shape noise
 . Since the unlensed galaxy shape can not be observed directly, the information
@@
 \end{equation}
-Due to the isotropicity of Universe, for the unlensed ellipticity $\epsilon_{0}$ 
+Due to the isotropicity of the Universe, for the unlensed ellipticity $\epsilon_{0}$ 
 we expect $\phi$ has a uniform distribution

### 2013-04-12 docs/ms.tex
Update ms.tex

@@
 information about how the ellipticity are distributed. The mean ellipticity
-point estimator can't use another reasonable assumption about the intrinsic shape distribution --galaxies in different sky patches should have
-the same shape distibution--which is a natural result of the homogeneous Universe.
+point estimator can't use another reasonable assumption about the intrinsic shape distribution - galaxies in different sky patches should have
+the same shape distibution - which is a natural result of the homogeneous Universe.
 

### 2013-04-13 docs/ms.tex
add fig

@@
 position. An example in the x, y plane is shown for the posterior distribution of
-$\vec{g}$ of 64 sky patches in Fig. .8 galaxy shape profiles in each patch is used as the data.
+$\vec{g}$ of 64 sky patches in Fig 1. There are 8 galaxies in each patch in the simulation.
 The number density of samples is proportional to the probability density. The figure shows that the two parameters of $\vec{g}$
@@
 deviation as the most probable estimates and uncertainty. We'll justify this approximation with a bias test in the following
-sub section.
+sub section. We also show a histgram of g1 in a random patch in fig 2.
 
@@
 estimator.}
+\end{figure}
+
+\begin{figure}
+\end{figure}
+
+\begin{figure}
+\includegraphics[scale=0.48]{fig/g1hist}
+
+\caption{The figure shows the histogram of posterior samples of g1 in a random patch. The vertical line denotes the value of true(input) g1. }
 \end{figure}

### 2013-04-13 docs/ms.tex
Update ms.tex

@@
 that it can be used to measure the mass profile of single galaxy, galaxy
-groups, clusters  the large scales. Cosmic shear is the mild distortion
+groups, clusters and the large scales. Cosmic shear is the mild distortion
 of distant galaxy images due to the bending of light by intervening
@@
 abey such a distribution. Then we can calculate the joint likelihood
-of shpape distribution parameters and shear in different sky patches. With
-a classical Gibbs MCMC sampler we are able to sample the joint posterior distribution
+of shape distribution parameters and shear in different sky patches. Using
+ Gibbs MCMC sampler we are able to sample the joint posterior distribution
 in an efficient way. After marginalizing the shape parameters, we can obtain

### 2013-04-13 docs/ms.tex
Update ms.tex
update ms.tex

@@
 In galaxy--galaxy lensing, since the distortion is so weak, what people
-usually do is to stack many lensing signals together. Then they can obtain the mean
-shear map and infer the mean mass profile of single galaxy or galaxy
-cluster. However with the Hierarchical Bayesian method we can avoid this brute averaging
+usually do is to stack many lensing signals together. Then the mean
+shear map and mean mass profile of single galaxy or galaxy
+cluster can be inferred from this stacked lensing signal. However with the Hierarchical Bayesian method we can avoid this brute averaging
 of lensing signal. Instead, we can get the posterior distribution of mass profile for
@@
 
-\section{method}
+\section{Method}
 
@@
 from Schramm \& Kayser (1995), Seitz \& Schneider (1997), where $\epsilon$
-is represented as a complex variable and g, $g^{*}$ are the reduced
-shear and its complex conjugate, respectively. In weak lensing region we have 
+is represented as a complex variable. It is defined in terms of the major and minor axes and orientation a, b, $\phi$,
+respectively, as
+\begin{equation}
+\epsilon=\frac{a-b}{a+b}e^{2i\phi}
+\end{equation}
+$g$, $g^{*}$ are the reduced shear and its complex conjugate, respectively. In weak lensing region we have 
 \begin{equation}
@@
 $\gamma$ is the shear. This is the assumption we use through out
-the paper.$\epsilon$ is defined in terms of the major and minor axes and orientation a, b, $\phi$,
-respectively, as
-\begin{equation}
-\epsilon=\frac{a-b}{a+b}e^{2i\phi}
-\end{equation}
+the paper.
 Due to the isotropicity of the Universe, for the unlensed ellipticity $\epsilon_{0}$ 
@@
 
-Suppose we know the intrnsic ellipticity distribution P($\epsilon_{0}$)
-based on some parasmeters $\alpha$. Then we can write down the likelihood
-of reduced shear and $\alpha$:
+Suppose we know the intrnsic ellipticity distribution $P(\epsilon_{0}|\vec{\alpha})$
+based on some parasmeters $\vec{\alpha}$. Then we can write down the joint likelihood
+of reduced shear $g$ and shape parameters $\vec{\alpha}$:
 
@@
 
-If there is measurement error on $\epsilon_{ob}$, we will have 
+For a realistic unperfect galaxy shape measurement, there will be measurement errors on $\epsilon_{ob}$. Then we will have 
 \begin{equation}
@@
 
-One thing to note is that the likelihood of g in one patch only explicitly depends
-on the shape parameters but not dependent to shear in other patches. Therefore, the
+One thing to note is that the likelihood of $g$ in one patch only explicitly depends
+on the shape parameters but not dependent to reduced shear in other patches. Therefore, the
 marginalized likelihood of shape parameters is :
@@
 calculated with data in the ith patch. From this formula we can see
-how better estimation of $\alpha$ will be obtained if we infer more
-sky patches simultaneously. With better knowledge on $\alpha$ we
-can in turn have better estimates on reduced shear g.
+how better inference of $\vec{\alpha}$ will be obtained if we infer numerous
+sky patches simultaneously. With better knowledge on $\vec{\alpha}$ we
+will in turn have better estimates on the reduced shear $g$.
 
-\subsection{Model for Intrinsic Shape distribution}
+\subsection{Model for Intrinsic Shape Distribution}
 
@@
 ellipticity distribution P($\epsilon_{0}|\alpha$). Due to the limitation
-of human's knowledge we are not able to give an analytical form of
+of human's knowledge we will not be able to give an analytical form for
 $P(\epsilon_{0}|\alpha)$. Therefore we proposed an exceedingly flexible
@@
 of each bin is $p_{i}=e^{\alpha_{i}}$. $\overrightarrow{\alpha}$
-is a N-D parameter vector to be infered, simultaneously with g.
+is a N dimension parameter to be infered, simultaneously with $g$.
 
-From practice we find that a prior smooth regularzation on $\alpha$
-is needed to obtain a good estimation on shear g.
+From practice we find that a prior smooth regularizer on $\vec{\alpha}$
+is needed to obtain a good estimation on $g$ and $\vec{\alpha}$.
 
-The prior distribution we used on $\alpha$ is : 
+The prior distribution we used on $\vec{\alpha}$ is : 
 \begin{equation}
@@
 
-\subsection{Posterior samples}
+\subsection{Posterior Samples}
 
@@
 position. An example in the x, y plane is shown for the posterior distribution of
-$\vec{g}$ of 64 sky patches in Fig 1. There are 8 galaxies in each patch in the simulation.
+$\vec{g}$ of 64 sky patches in Figure 1. There are 8 galaxies in each patch in the simulation.
 The number density of samples is proportional to the probability density. The figure shows that the two parameters of $\vec{g}$
 do not have strong correlation, since the shape of smaples is close to a circle.
-We also shows the histogram of g1 in a single sky patch. Not surprisingly it is close to a Gaussian distribution.
+We also shows the histogram of g1 in a single sky patch in Figure 2. Not surprisingly it is close to a Gaussian distribution.
 If the probability distribution of parameters are perfect Gaussian, the most probable estimates and uncertainty 
@@
 deviation as the most probable estimates and uncertainty. We'll justify this approximation with a bias test in the following
-sub section. We also show a histgram of g1 in a random patch in fig 2.
+sub section.
 
@@
 We calculated the value of $\hat{g}-g^{true}$ of 10,000 data. Each data set has 64 patches and 8$\times$64 galaxies, and
-the true(input) P($\epsilon_{0}$) is Beta(2.8,2.8). The step function model is used with the prior prefator $\xi=3$.
+the true(input) P($\epsilon_{0}$) is Beta(2.8,2.8) distribution. The step function model is used with the prior prefator $\xi=3$.
 The input true values of $\vec{g}_{1}$ and $\vec{g}_{2}$ of the 64$\times$10,000 sky patches are generated randomly from a uniform distribution from -0.1 to 0.1 .
@@
 \subsection{Measurement Error}
-In this section we  discuss how the shape measurement error will
+In this section we  discuss how the shape measurement error 
 affect the variance and bias of this Hierarchical Bayesian method.
@@
 
-\subsection{prefactor $\xi$}
+\subsection{Prefactor $\xi$}
 

### 2013-04-13 docs/ms.tex
update ms.tex

@@
 One thing to note is that the conditional probability of g in one patch only explicitly depends on $\alpha$, but not g in other patches. Therefore
-With $\alpha$ fixed, the posterior distributions of reduced shear in different patches are independent from each other. 
+with $\vec{\alpha}$ fixed, the posterior distributions of reduced shear in different patches are independent from each other. 
 \begin{equation}
-p(\vec{g}_{1}....\vec{g}_{n}|\alpha,Data)=p(\vec{g}_{1}|\alpha,Data_{1})....p(\vec{g}_{n}|\alpha,Data_{n})
+p(\vec{g}_{1}....\vec{g}_{n}|\vec{\alpha},Data)=p(\vec{g}_{1}|\vec{\alpha},Data_{1})....p(\vec{g}_{n}|\vec{\alpha},Data_{n})
 \end{equation}
 Therefore sampling reduced shear g from the conditional probability distribution can be reduced to a 2D sampling problem, which can be done very quickly.
-
+In the Gibbs sampler, first we make a sample of $p(\vec{\alpha}|\vec{g},Data)$ with Metropolis-Hasting sampler. The we make samples of $g$ in different patches
+independently according to formula (14).
 The total time needed to sample $g$ and $\alpha$ of 64 sky patches with 8 galaxies in each patch will only be 

### 2013-04-13 docs/ms.tex
update ms.tex

@@
 
-The procedure of our simulation is that, first we generated N{*}NP
+The procedure of our simulation is as following. First we generated N$\times$NP
 unlensed galaxies' elliprticity from the ``true'' $P(\epsilon_{0})$, and
-asign these galaxies into NP patches equally. So each patch has N galaxies. Second
+asign these galaxies into NP patches equally. So each patch has N galaxies. Then
 we generate NP true reduced shears, and asign them to each patch, and

### 2013-04-13 docs/ms.tex
Update ms.tex

@@
 
-Given the likehood functions and priors we can also calculated the marginalized likelihood function. 
+Given the likehood functions and priors we can also calculate the marginalized likelihood function. 
 \begin{equation}
@@
 
-Since $p(\alpha)$ does not explicitly depends on $\vec{g}$. $p(\alpha|\vec{g})$ is
+Since $p(\alpha)$ does not explicitly depend on $\vec{g}$. $p(\alpha|\vec{g})$ is
 just the prior distribution $p(\vec{\alpha}|\xi)$. Therefore, we have
@@
 
-The procedure of our simulation is as following. First we generated N$\times$NP
+The procedure of our simulation is as following. First we generate N$\times$NP
 unlensed galaxies' elliprticity from the ``true'' $P(\epsilon_{0})$, and
-asign these galaxies into NP patches equally. So each patch has N galaxies. Then
+asign them into NP patches evenly. So each patch has N galaxies. Then
 we generate NP true reduced shears, and asign them to each patch, and

### 2013-04-13 docs/ms.tex
Update ms.tex

@@
 \subsection{Bias Test}
-In principle given the correct model and prior,
-the hierchical Bayesian inference method would have no bias, if propagate the whole likelihood function.
+In principle given the correct intrinsic shape distribution, the Bayesian inference method would have no bias, if propagate the whole likelihood function.
 However, in practical, the bias may be introduced by the model we use for the intrinsic shape distribution,

### 2013-04-13 docs/ms.tex
Update ms.tex

@@
 observed ellipticity $\epsilon_{ob}$. For simplicity we've only considered
-the situation when P($\epsilon_{ob}|\epsilon_{\ell})$ is a 2D Gaussian.
+the situation where P($\epsilon_{ob}|\epsilon_{\ell})$ is a 2D Gaussian.
 
@@
 
-We show the posterior samples of both g and $\alpha$, for both beta
+We show the posterior samples of both $g$ and $\vec{\alpha}$, for both beta
 function and step function model.

### 2013-04-13 docs/ms.tex
Update ms.tex

@@
 \end{equation}
-Given that marginalized likelihood function, in principle we could optimize it and gives out a max-likelihood estimator for $\vec{g}$
+Given that marginalized likelihood function, in principle we could optimize it and give out a max-likelihood estimator for $g$
 in different patches simultaneously.
@@
 
-The correctness of posterior distribution of g depends on the intrinsic
+The correctness of posterior distribution of $g$ depends on the intrinsic
 ellipticity distribution P($\epsilon_{0}|\alpha$). Due to the limitation
 of human's knowledge we will not be able to give an analytical form for
-$P(\epsilon_{0}|\alpha)$. Therefore we proposed an exceedingly flexible
-model for $P(\epsilon_{0}|\alpha)$, which does not requires further
+$P(\epsilon_{0}|\alpha)$. Therefore we propose an exceedingly flexible
+model for $P(\epsilon_{0}|\alpha)$, which does not require further
 assumption on $P(\epsilon_{0}|\alpha)$.
@@
 of each bin is $p_{i}=e^{\alpha_{i}}$. $\overrightarrow{\alpha}$
-is a N dimension parameter to be infered, simultaneously with $g$.
+is a N dimension parameter to be inferred, simultaneously with $g$.
 
@@
 
-One thing to note is that the conditional probability of g in one patch only explicitly depends on $\alpha$, but not g in other patches. Therefore
+One thing to note is that the conditional probability of $g$ in one patch only explicitly depends on $\alpha$, but not g in other patches. Therefore
 with $\vec{\alpha}$ fixed, the posterior distributions of reduced shear in different patches are independent from each other. 
@@
 independently according to formula (14).
-The total time needed to sample $g$ and $\alpha$ of 64 sky patches with 8 galaxies in each patch will only be 
+The total time needed to sample $g$ and $\alpha$ of 64 sky patches with 8 galaxies in each patch is 
 approximitly 25s on a 2 GHz CPU.
@@
 position. An example in the x, y plane is shown for the posterior distribution of
-$\vec{g}$ of 64 sky patches in Figure 1. There are 8 galaxies in each patch in the simulation.
+$g$ in 64 sky patches in Figure 1. There are 8 galaxies in each patch in the simulation.
 The number density of samples is proportional to the probability density. The figure shows that the two parameters of $\vec{g}$
@@
 unbiased.
-Meanwhile we find that simply using the posterior mean as the estimator of g will lead to a significant bias. 
+Meanwhile we find that simply using the posterior mean as the estimator of $g$ will lead to a significant bias. 
 Figure 3 shows the result of bias test for both mean ellipticity and posterior mean estimator.
@@
 In this section we  discuss how the shape measurement error 
-affect the variance and bias of this Hierarchical Bayesian method.
+affects the variance and bias shear inference.
 In principle, if the likelihood of true lensed ellipticity $p(\epsilon_{ob}|\epsilon_{\ell})$

### 2013-04-13 docs/ms.tex
Update ms.tex
add fig

@@
 Gaussian with mean equals $\epsilon_{\ell}$ and $\sigma$ equals 0.05 .
-The result of bias test and mean square error test is shown in
+Figure 5 shows the mean square error of the sample mean estimates in comparison with mean ellipticity estimator.
+\begin{figure}
+\includegraphics[scale=0.48]{fig/errorN8}
+\caption{Figure 5 shows how the mean square error of sample mean estimate varies with the number of patches used, while shape measurement error is considered as described in Section 3.4 .
+The horizontal line denotes the mean square of mean ellipticity estiimator which does not depend on number of patches. }
+\end{figure}
 
@@
 
+Several  model fitting  shape measurent methods have been proposed in recent years.
+Unlike the average method which merely request a point estimator of galaxy ellipcity, our 
+hierachical bayesian approach utilizes the whole likelihood of the galaxy ellipticity in a Bayesian probability analysis framework.
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-Several  model fitting  shape measurent methods have been proposed in recent years.
-Unlike the average method which merely request a point estimator of galaxy ellipcity, our 
-hierachical bayesian approach utilizes the whole likelihood of the galaxy ellipticity in a Bayesian probability analysis framework.
 \begin{itemize}

### 2013-04-14 docs/ms.tex
update

@@
 
-We compare the mean square error of our estimator with average and
-the estimator that could be constructed if the true unlensed ellipticity
-distribution were known. We show how the mean square error varies
-with number of galaxies, number of patches and so on.
+In this section we calculate the mean square error of mean of posterior samples from the true(input) $g$.
+We show the mean of posterior samples has smaller mean square error than the mean ellipticity estimator but has higher mean square error than the direct Bayesian estimates which could be made if we knew the exact intrinsic shape distribution.
+In figure 5 we show how the mean square error changes with the number of galaxies and patches, and make a comparison with mean ellipticity estimator and direct Bayesian estimates.
+From the figure we can see that when the number of sky patches is small our hierarchical Bayesian method does not necessarily has lower mean square error than mean ellipticity estimator.
+However it becomes smaller and approach to the result of direct Bayesian estimate which is the best estimate we can possibly make.
+
 \begin{figure}

### 2013-04-14 docs/ms.tex
Update ms.tex
up date

@@
 In this section we calculate the mean square error of mean of posterior samples from the true(input) $g$.
-We show the mean of posterior samples has smaller mean square error than the mean ellipticity estimator but has higher mean square error than the direct Bayesian estimates which could be made if we knew the exact intrinsic shape distribution.
+We show that the mean of posterior samples has smaller mean square error than the mean ellipticity estimator but has higher mean square error than the direct Bayesian estimates which could be made if we knew the exact intrinsic shape distribution.
 In figure 5 we show how the mean square error changes with the number of galaxies and patches, and make a comparison with mean ellipticity estimator and direct Bayesian estimates.

### 2013-04-14 docs/ms.tex
up

@@
 In this section we  discuss how the shape measurement error 
-affects the variance and bias shear inference.
+affects the variance and bias of shear inference.
 In principle, if the likelihood of true lensed ellipticity $p(\epsilon_{ob}|\epsilon_{\ell})$
-is known the likelihood $p(\epsilon_{ob}|g,\alpha)$ can be calculated using the convolution as equation ().
+is known the likelihood $p(\epsilon_{ob}|g,\alpha)$ can be calculated using the convolution as equation (7).
 However, due to the limitation of computational time we avoid to do this convolution but use $\epsilon_{ob}$

### 2013-04-14 docs/ms.tex
Update ms.tex

@@
 \subsection{Posterior Samples}
-
-We show the posterior samples of both $g$ and $\vec{\alpha}$, for both beta
-function and step function model.
-
 The probability distribution can be visualised by plotting points at each sample

### 2013-04-14 docs/ms.tex
Update ms.tex

@@
 
-The prior distribution we used on $\vec{\alpha}$ is : 
+The prior regularizer we used on $\vec{\alpha}$ is : 
 \begin{equation}
@@
 
-As described in the previous subsection we use the sample mean as the most probable $g_{i}$ and 
-the standard deviation as the uncertainty. A weighted minimum $\chi^{2}$ linear fit is performed to get the
+As described in section 3.1, we use the mean of posterior samples as the most probable $g_{i}$ and 
+the standard deviation as uncertainty. A weighted minimum $\chi^{2}$ linear fit is performed to get the
 most-likely value and uncertainty of m and c.

### 2013-04-14 docs/ms.tex
Update ms.tex

@@
 \begin{keywords}
-  gravitational lensing
+  gravitational lensing ; hierarchical Bayesian inference
 \end{keywords}
@@
 the standard deviation as uncertainty. A weighted minimum $\chi^{2}$ linear fit is performed to get the
-most-likely value and uncertainty of m and c.
-
+most-likely value and uncertainty of m and c. for $g_{1}$ component we get $m=-6.09\times10^{-4}\pm2.39\times10^{-3}$
+and $c=(1.82\pm1.44)\times10^{-4}$, while for $g_{2}$ component
+we have $m=-3.48\times10^{-4}\pm2.14\times10^{-3}$ and $c=(2.01\pm1.29)\times10^{-4}$.
 Due to the limitation of galaxy number we are not able to get an exact value for m and c. However in our result 
@@
 \end{figure}
+We can see that our proposed method still works well under shape measurement error, even when we do not have the exact likelihood
+of true lensed ellipticity. It means that this hierarchical Bayesian method does not only naturally cope with model fitting shape measurement 
+method but is also compatible with ellipticity point estimators.
 

### 2013-04-14 docs/ms.tex
Update ms.tex

@@
 \begin{equation}
-p(\vec{g}_{1}....\vec{g}_{n}|\vec{\alpha},Data)=p(\vec{g}_{1}|\vec{\alpha},Data_{1})....p(\vec{g}_{n}|\vec{\alpha},Data_{n})
+p(g_{1}....g_{n}|\vec{\alpha},Data)=p(g_{1}|\vec{\alpha},Data_{1})....p(g_{n}|\vec{\alpha},Data_{n})
 \end{equation}
-Therefore sampling reduced shear g from the conditional probability distribution can be reduced to a 2D sampling problem, which can be done very quickly.
+Therefore sampling reduced shear $g$ from the conditional probability distribution can be reduced to a 2D sampling problem, which can be done very quickly.
 In the Gibbs sampler, first we make a sample of $p(\vec{\alpha}|\vec{g},Data)$ with Metropolis-Hasting sampler. The we make samples of $g$ in different patches
 independently according to formula (14).
-The total time needed to sample $g$ and $\alpha$ of 64 sky patches with 8 galaxies in each patch is 
+The total time needed to sample $g$ and $\vec{\alpha}$ of 64 sky patches with 8 galaxies in each patch is 
 approximitly 25s on a 2 GHz CPU.

### 2013-04-14 docs/ms.tex
Update ms.tex

@@
 \begin{equation}
-p(\epsilon_{\ell}|\vec{g},\alpha)=p(\epsilon_{0}(\vec{g})|\alpha)\,|\frac{\partial\epsilon_{0}}{\partial\epsilon_{\ell}}|
+p(\epsilon_{\ell}|\vec{g},\vec{\alpha})=p(\epsilon_{0}(\vec{g})|\vec{\alpha})\,|\frac{\partial\epsilon_{0}}{\partial\epsilon_{\ell}}|
 \end{equation}
@@
 In summary, we have presented a conceptually hierachical inference
-approach for weak lensing shear estimation, with carefully calculated 
-uncertainty estimates. This method is intrinsically cope with high noise
+approach for weak lensing shear inference, with carefully calculated 
+uncertainty estimates. This method intrinsically cope with high noise
 levels on the input data and naturally allows bad fit to be identified 

### 2013-04-15 docs/ms.tex
add fig

@@
 do not have strong correlation, since the shape of smaples is close to a circle.
-We also shows the histogram of g1 in a single sky patch in Figure 2. Not surprisingly it is close to a Gaussian distribution.
+We also shows the histogram of g1 in a single sky patch in Figure 3. Not surprisingly it is close to a Gaussian distribution.
 If the probability distribution of parameters are perfect Gaussian, the most probable estimates and uncertainty 
@@
 estimator.}
+\end{figure}
+
+\begin{figure}
+\end{figure}
+\begin{figure}
+\includegraphics[scale=0.3]{fig/alpha_beta}
+\includegraphics[scale=0.3]{fig/stp10}
+
+\caption{The upper panel show the MCMC samples of shape parameters of the Beta function model.
+The true(input) value is (2.8,2.8) as indicated by the two straight lines in the graphic.
+The lower panel shows the sample mean of the shape parameters of the step function model.
+The curve denotes the true shape distribution $P(|\epsilon_{0}|)$, which is Beta (2.8,2.8) in this case.}
 \end{figure}
@@
 the standard deviation as uncertainty. A weighted minimum $\chi^{2}$ linear fit is performed to get the
-most-likely value and uncertainty of m and c. for $g_{1}$ component we get $m=-6.09\times10^{-4}\pm2.39\times10^{-3}$
+most-likely value and uncertainty of m and c. For $g_{1}$ component we get $m=-6.09\times10^{-4}\pm2.39\times10^{-3}$
 and $c=(1.82\pm1.44)\times10^{-4}$, while for $g_{2}$ component
-we have $m=-3.48\times10^{-4}\pm2.14\times10^{-3}$ and $c=(2.01\pm1.29)\times10^{-4}$.
+we have $m=-3.48\times10^{-4}\pm2.14\times10^{-3}$ and $c=(2.01\pm1.29)\times10^{-4}$. Figure 3 shows the result of bais test for the $g_{1}$ component.
 Due to the limitation of galaxy number we are not able to get an exact value for m and c. However in our result 
@@
 Meanwhile we find that simply using the posterior mean as the estimator of $g$ will lead to a significant bias. 
-Figure 3 shows the result of bias test for both mean ellipticity and posterior mean estimator.
+Figure 5 shows the result of bias test for both mean ellipticity and posterior mean estimator.
 
@@
 We show that the mean of posterior samples has smaller mean square error than the mean ellipticity estimator but has higher mean square error than the direct Bayesian estimates which could be made if we knew the exact intrinsic shape distribution.
-In figure 5 we show how the mean square error changes with the number of galaxies and patches, and make a comparison with mean ellipticity estimator and direct Bayesian estimates.
+In figure 6 we show how the mean square error changes with the number of galaxies and patches, and make a comparison with mean ellipticity estimator and direct Bayesian estimates.
 From the figure we can see that when the number of sky patches is small our hierarchical Bayesian method does not necessarily has lower mean square error than mean ellipticity estimator.
@@
 Gaussian with mean equals $\epsilon_{\ell}$ and $\sigma$ equals 0.05 .
-Figure 5 shows the mean square error of the sample mean estimates in comparison with mean ellipticity estimator.
+Figure 7 shows the mean square error of the sample mean estimates in comparison with mean ellipticity estimator.
 \begin{figure}
